---
title: "Analyzing Combined NetVisLit Data"
author: "Angela Zoss"
date: "July 19, 2017"
output: github_document
---

Notes:

These command files should contain commands that open up your analysis data files, and then use those data to generate the output upon which your results are based.

Every command that generates any of your results should be preceded by a comment that states which result the command generates.  A few Hypothetical examples illustrate what these comments might look like:

* The following command generates the first column of Table 6.

The command files for your analysis phase should not contain any commands that generate new variables or process your data in any way.  All the procedures required to prepare your data for analysis should be executed by the command files you wrote for the processing phase.

It is often convenient to write all the commands for the analysis phase in a single command file. However, if the nature of your project or the structure of your data are such that you think it would make sense to divide the code that generates the results into two or more command files, you should feel free to do so.  No matter how you organize your analysis command files, your Read Me file will include an explanation of how to use them to reproduce your results.

Save the command files you write for the analysis phase in the Command Files folder.


## Clear environment

```{r}

rm(list=ls())

```

```{r}

# Detach previous packages

detachAllPackages <- function() {
  
  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")
  
  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]
  
  package.list <- setdiff(package.list,basic.packages)
  
  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)
  
}

detachAllPackages()

```

## Load packages

```{r}

require(tidyverse)
library(officer)
library(rvg)
library(devEMF)
library(nlme)
library(lme4)
library(car)
library(lmerTest)

```

## Environmental Variables

```{r}

originalDataDir <- "../../Original Data"
analysisDataDir <- "../../Analysis Data"

generatedDataDir <- file.path(originalDataDir, "Generated data")

figureDir <- "../../Documents/"

```

## Loading analysis data files

```{r, eval=FALSE}

#all_nodes <- read_csv(file.path(generatedDataDir, "all_nodes.csv"))

all_edges <- read_csv(file.path(generatedDataDir, "all_edges.csv"))

node_lookup <- read_csv(file.path(generatedDataDir, "node_lookup.csv"), col_types = cols(MaxValue = col_double(),NodeValue = col_double()))

graded_num_ans <- read_csv(file.path(analysisDataDir, "GradedNumAnswers.csv"))

graded_nodes <- read_csv(file.path(analysisDataDir, "GradedNodes.csv"))

stats_datasets_tall <- read_csv(file.path(analysisDataDir, "Stats_Datasets_Tall.csv"))

stats_demo <- read_csv(file.path(analysisDataDir, "Stats_Demo.csv"))

responses <- read_csv(file.path(analysisDataDir, "CombinedResponsesWithOrder.csv"))

num_ans_lookup <- read_csv(file.path(generatedDataDir, "numerical_answer_lookup.csv"))

#responses <- read_csv(file.path(analysisDataDir, "Pilot3ResponsesWithOrder.csv"))

exp_only <- read_csv(file.path(analysisDataDir, "ExpOnly.csv"))

all_exp <- read_csv(file.path(analysisDataDir, "AllExperimental.csv"))

graphics <- read_csv(file.path(analysisDataDir, "Graphics.csv"))

layoutfac <- read_csv(file.path(analysisDataDir, "LayoutFac.csv"))

```

```{r}

#all_nodes <- read_csv(file.path(generatedDataDir, "all_nodes.csv"))

all_edges <- read_csv(file.path(generatedDataDir, "all_edges.csv"))

node_lookup <- read_csv(file.path(generatedDataDir, "node_lookup.csv"), col_types = cols(MaxValue = col_double(),NodeValue = col_double()))

#graded_num_ans <- read_csv(file.path(analysisDataDir, "GradedNumAnswers.csv"))
graded_num_ans <- readRDS(file.path(analysisDataDir, "GradedNumAnswers.rds"))

#graded_nodes <- read_csv(file.path(analysisDataDir, "GradedNodes.csv"))
graded_nodes <- readRDS(file.path(analysisDataDir, "GradedNodes.rds"))

#stats_datasets_tall <- read_csv(file.path(analysisDataDir, "Stats_Datasets_Tall.csv"))
stats_datasets_tall <- readRDS(file.path(analysisDataDir, "Stats_Datasets_Tall.rds"))

#stats_demo <- read_csv(file.path(analysisDataDir, "Stats_Demo.csv"))
stats_demo <- readRDS(file.path(analysisDataDir, "Stats_Demo.rds"))

#responses <- read_csv(file.path(analysisDataDir, "CombinedResponsesWithOrder.csv"))
responses <- readRDS(file.path(analysisDataDir, "CombinedResponsesWithOrder.rds"))

num_ans_lookup <- read_csv(file.path(generatedDataDir, "numerical_answer_lookup.csv"))

#responses <- read_csv(file.path(analysisDataDir, "Pilot3ResponsesWithOrder.csv"))

#exp_only <- read_csv(file.path(analysisDataDir, "ExpOnly.csv"))
exp_only <- readRDS(file.path(analysisDataDir, "ExpOnly.rds"))

#all_exp <- read_csv(file.path(analysisDataDir, "AllExperimental.csv"))
all_exp <- readRDS(file.path(analysisDataDir, "AllExperimental.rds"))

#graphics <- read_csv(file.path(analysisDataDir, "Graphics.csv"))
graphics <- readRDS(file.path(analysisDataDir, "Graphics.rds"))

#layoutfac <- read_csv(file.path(analysisDataDir, "LayoutFac.csv"))
layoutfac <- readRDS(file.path(analysisDataDir, "Layouts.rds"))

```

## Slight processing for analysis

```{r}

graded_num_ans$ClustConf <- factor(graded_num_ans$ClustConf, levels = c("Very doubtful (0-25%)","Somewhat doubtful (26-50%)","Somewhat confident (51-75%)","Very confident (76-100%)"), ordered = TRUE)

graded_num_ans$Condition <- factor(graded_num_ans$Condition,
                                   levels=c("Ctrl","Phr","Siz","Col","Fru","Ord","Cir"))

graded_nodes$Condition <- factor(graded_nodes$Condition,
                                   levels=c("Ctrl","Phr","Siz","Col","Fru","Ord","Cir"))


stats_demo$`Stats-Group` <- factor(stats_demo$`Stats-Group`,
                                   levels=c("control", "phrasing", "size", "color", 
                                            "frucht", "openord", "circle"))

stats_demo$`Demo-educ` <- factor(stats_demo$`Demo-educ`, 
                                 levels=c("did not complete High School diploma",
                                          "High School diploma",
                                          "Bachelor’s degree",
                                          "Professional degree",
                                          "Master’s degree",
                                          "Doctorate degree",
                                          "Other"))

freq4 <- c("None", "A little", "Some", "A lot")

stats_demo$`Demo-expdataanal` <- factor(stats_demo$`Demo-expdataanal`, 
                                        levels = freq4, 
                                        ordered = TRUE)

stats_demo$`Demo-expdatavis` <- factor(stats_demo$`Demo-expdatavis`, 
                                        levels = freq4, 
                                        ordered = TRUE)

stats_demo$`Demo-expreadnetvis` <- factor(stats_demo$`Demo-expreadnetvis`, 
                                        levels = freq4, 
                                        ordered = TRUE)

stats_demo$`Demo-expcreatenetvis` <- factor(stats_demo$`Demo-expcreatenetvis`, 
                                        levels = freq4, 
                                        ordered = TRUE)

graphics$ClustConf <- factor(graphics$ClustConf,
                             levels = c("Very confident (76-100%)", 
                                        "Somewhat confident (51-75%)", 
                                        "Somewhat doubtful (26-50%)", 
                                        "Very doubtful (0-25%)"),
                             ordered = TRUE)

num_ans_lookup$Dataset <- factor(num_ans_lookup$Dataset, ordered = TRUE)

```

```{r}

graded_num_ans <- left_join(graded_num_ans, stats_demo)
graded_num_ans <- left_join(graded_num_ans, stats_datasets_tall)

graded_nodes <- left_join(graded_nodes, stats_demo)
graded_nodes <- left_join(graded_nodes, stats_datasets_tall)

```

## Summarize Stats and Demo data

```{r}

ggplot(stats_demo) +
  geom_density(aes(`Stats-Q_TotalDuration` / 60, color=filename)) +
#  geom_histogram(aes(`Stats-Q_TotalDuration` / 60)) +
#  geom_dotplot(aes(x = (`Stats-Q_TotalDuration` / 60)), binwidth = 3) +
  scale_x_continuous(limits = c(0,70), name = "Total Duration in Minutes") +
  #facet_grid(filename~.)
  facet_grid(NetVisExperience~.)
  


```
```{r}

ggplot(stats_demo) +
  geom_bin2d(aes(x = factor(`Stats-dataset_count`), y=filename))


```

```{r}

ggplot(stats_demo) +
#  geom_histogram(aes(`Stats-Q_TotalDuration`)) +
  geom_dotplot(aes(x = (`Stats-Q_TotalDuration` / `Stats-dataset_count` / 60)), binwidth = 1) +
  scale_x_continuous(limits = c(0,25), name = "Average duration in minutes per dataset (bins = 1 minute each)") +
  facet_grid(filename~.)


```

```{r}

ggplot(stats_demo) +
  geom_boxplot(aes(x = NetVisExperience, y = (`Stats-Q_TotalDuration` / `Stats-dataset_count` / 60), color=filename)) +
  labs(y="Avg. Duration per dataset in minutes\n(filtered to exclude averages over 50 min.)") +
  scale_y_continuous(limits = c(0,50))

```

```{r}

ggplot(stats_datasets_tall) +
  geom_boxplot(aes(x = NetVisExperience, y = (DatasetDuration / 60), color=factor(DatasetOrder))) + 
  scale_y_continuous(limits=c(0,125)) #+
  #facet_grid(NetVisExperience~.)


```

```{r}

three.block.duration <- stats_datasets_tall %>% filter(filename=="PilotStudents") %>% group_by(`Demo-ResponseID`) %>% summarise(totalDuration=sum(DatasetDuration)/60) %>% dplyr::select(`Demo-ResponseID`,totalDuration)

two.block.duration <- stats_datasets_tall %>% filter(filename=="PilotStudents") %>% filter(DatasetOrder < 3) %>% group_by(`Demo-ResponseID`) %>% summarise(totalDuration=sum(DatasetDuration)/60) %>% dplyr::select(`Demo-ResponseID`,totalDuration)
  
ggplot(two.block.duration) + geom_boxplot(aes(y=totalDuration,x="all"))
```

```{r}
median(two.block.duration$totalDuration)

median(three.block.duration$totalDuration)

median(stats_demo$`Stats-Q_TotalDuration`/60)

```


```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Stats-Group`)) +
  facet_grid(NetVisExperience~.)


```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Stats-BrowserName`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Stats-OperatingSystem`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Stats-ScreenResolution`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_dotplot(aes(`Demo-age`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-gender`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-lang`)) +
  facet_grid(filename~.)

```

```{r}

table(stats_demo$`Demo-lang_TEXT`, stats_demo$filename)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-educ`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-acfield`)) +
  coord_flip() +
  facet_grid(filename~.)

```

```{r}

table(stats_demo$`Demo-acfieldother`, stats_demo$filename)

```

```{r}

#stats_demo$`Demo-dailytech_Tablet` <- type.convert(sub(-99, 0, stats_demo$`Demo-dailytech_Tablet`))

ggplot(stats_demo) +
  geom_density(aes(`Demo-dailytech_Computer`), color = "blue") +
  geom_density(aes(`Demo-dailytech_Tablet`), color = "red") +
  geom_density(aes(`Demo-dailytech_SmartPhone`), color = "green") +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_dotplot(aes(`Demo-weeklygaming`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-expdataanal`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-expdatavis`)) +
  scale_x_discrete(drop=FALSE) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-expreadnetvis`)) +
  facet_grid(filename~.)

```

```{r}

ggplot(stats_demo) +
  geom_bar(aes(`Demo-expcreatenetvis`)) +
  facet_grid(filename~.)

```

```{r, eval=FALSE}

IDs <- stats_datasets_tall %>% group_by(`Demo-ResponseID`) %>% summarise(TotalDuration = sum(DatasetDuration)) %>% arrange(TotalDuration) %>% select(`Demo-ResponseID`) %>% unlist()

stats_datasets_tall$`Demo-ResponseID` <- factor(stats_datasets_tall$`Demo-ResponseID`, 
                                                levels = IDs) 

ggplot(stats_datasets_tall) +
  geom_col(aes(x = `Demo-ResponseID`, 
               y = `DatasetDuration`)) +
  facet_grid(filename~Dataset, scales="free_y", space="free_y") +
  coord_flip()

```

```{r}

ggplot(stats_datasets_tall) +
  geom_boxplot(aes(x = factor(Dataset), y = `DatasetDuration`)) +
  facet_grid(.~filename)

```

## Figures

```{r}

ggplot(graded_num_ans) +
  geom_density(aes(LogError)) + 
  scale_x_log10() +
  facet_grid(.~filename)

```


```{r}

ggplot(graded_num_ans) +
  geom_boxplot(aes(factor(Dataset), LogError)) +
  scale_y_log10() +
  facet_grid(.~filename)

```

```{r}

ggplot(graded_num_ans) +
  geom_boxplot(aes(Task, LogError)) +
  scale_y_log10() +
  facet_grid(.~filename)

```

```{r}

ggplot(graded_num_ans) +
  geom_point(aes(DatasetDuration, LogError)) +
  #scale_y_log10() + 
  facet_grid(Dataset~Task) +
  facet_grid(.~filename)

```

```{r}

ggplot(graded_num_ans) +
  geom_boxplot(aes(factor(Dataset), LogError)) +
  scale_y_log10() +
  facet_grid(Task~filename)

```

```{r}

ggplot(graded_num_ans) +
  geom_boxplot(aes(Task, LogError)) +
  scale_y_log10() +
  facet_grid(Dataset~filename)

```

```{r}

ggplot(graded_num_ans) +
  geom_boxplot(aes(Condition, LogError)) +
  facet_grid(Task~Dataset)

```

```{r clust_conf_bar}

ggplot(graded_num_ans %>% filter(!is.na(ClustConf))) +
  geom_bar(aes(x=ClustConf)) + 
  facet_grid(Dataset~.)

```

```{r}

ggplot(graded_num_ans %>% filter(!is.na(ClustConf)) %>% filter(Task == "NumClust")) +
  geom_boxplot(aes(ClustConf, LogError)) +
  scale_y_log10() +
  coord_flip() +
  facet_grid(Dataset~Condition)

```

```{r}

ggplot(graded_num_ans %>% filter(!is.na(ClustConf)) %>% filter(Task == "NumClust")) +
  geom_boxplot(aes(ClustConf, LogError)) +
  scale_y_log10() +
  #coord_flip() +
  facet_grid(.~Condition)

```

```{r}

ggplot(graded_num_ans %>% filter(!is.na(ClustConf)) %>% filter(Task == "NumClust")) +
  geom_boxplot(aes(Condition, LogError)) 


```

### Compare results to some of the demographics?


```{r, fig.width=12, fig.height=12}

ggplot() + 
  geom_point(data = node_lookup %>% filter(!(Dataset==6)),
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = graded_nodes %>% filter(Task == "BC"), 
             aes(x=Click_X,y=Click_Y), colour="red") + 
  facet_grid(Dataset~Condition) +
  theme_bw()

# TO DO: Factor node_lookup$Condition

# TO DO: remove dataset 6 from raw network data, since I never used it in surveys?


```

```{r, fig.width=12, fig.height=12}

ggplot() + 
  geom_point(data = node_lookup,
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = graded_nodes %>% filter(Task == "ClickHighDeg"), 
             aes(x=Click_X,y=Click_Y), colour="red") + 
  facet_grid(Dataset~Condition) +
  theme_bw()


```


```{r}

ggplot(graded_nodes %>% filter(Task == "BC")) +
  geom_point(aes(x=factor(Dataset), y=Percentage)) +
  facet_grid(filename~Condition)
  
```

```{r}

ggplot(graded_nodes %>% filter(Task == "ClickHighDeg")) +
  geom_point(aes(x=factor(Dataset), y=Percentage)) +
  facet_grid(filename~Condition)
  
```

```{r, eval=FALSE}

stats_datasets_tall %>% filter(NetVisExperience=="Low", !is.na(Dataset)) %>% group_by(`Stats-Group`,Dataset) %>% summarise(count=n_distinct(`Demo-ResponseID`)) %>% spread(Dataset,count) %>% View()

stats_datasets_tall %>% filter(NetVisExperience=="High", !is.na(Dataset)) %>% group_by(`Stats-Group`,Dataset) %>% summarise(count=n_distinct(`Demo-ResponseID`)) %>% spread(Dataset,count) %>% View()


stats_demo %>% group_by(NetVisExperience, `Stats-Group`) %>% summarise(count=n_distinct(`Demo-ResponseID`)) %>% spread(`Stats-Group`,count) %>% View()

```

## Research Questions

### Are some tasks harder?

```{r}

ggplot(graded_num_ans %>% filter(Task=="AvgDeg",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  #geom_boxplot(aes(factor(Dataset),Response), width=.1, alpha=.3) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="AvgDeg",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Average Degree",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumNodes",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumNodes",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Nodes",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumLinks",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumLinks",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Links",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumHighDegree",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumHighDegree",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Degree of Highest Degree Node",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumClust",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumClust",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Clusters",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="LargeClust1",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="LargeClust1",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_continuous(limits=c(0,100)) +
  labs(title="% Nodes in Largest Cluster",x="Dataset") +
  guides(fill="none")

```


```{r}

ggplot(graded_num_ans %>% filter(Task=="AvgDeg",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="Average Degree",x="Dataset") +
  guides(fill="none")


ggplot(graded_num_ans %>% filter(Task=="NumNodes",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="Number of Nodes",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumLinks",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="Number of Links",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumHighDegree",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="Degree of Highest Degree Node",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="NumClust",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="Number of Clusters",x="Dataset") +
  guides(fill="none")

ggplot(graded_num_ans %>% filter(Task=="LargeClust1",Dataset!=0)) +
  geom_violin(aes(factor(Dataset),LogError, fill=factor(Dataset))) + 
  labs(title="% Nodes in Largest Cluster",x="Dataset") +
  guides(fill="none")

```

```{r}

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Phr","Col","Siz"))) +
  geom_density(aes(LogError,color=factor(Condition,levels=c("Ctrl","Phr","Col","Siz")))) +
  labs(title="Error by Graphic Condition",x="Condition") +
  scale_color_discrete(name="Condition")

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Phr","Col","Siz"))) +
  geom_boxplot(aes(y=LogError,x=factor(Condition,levels=c("Ctrl","Phr","Col","Siz")),color=factor(Condition,levels=c("Ctrl","Phr","Col","Siz")))) +
  labs(title="Error by Graphic Condition",x="Condition") +
  scale_color_discrete(name="Condition")


```

```{r}

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord"))) +
  geom_density(aes(LogError,color=factor(Condition,levels=c("Ctrl","Cir","Fru","Ord")))) +
  labs(title="Error by Layout Condition",x="Condition") +
  scale_color_discrete(name="Condition")

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord"))) +
  geom_boxplot(aes(y=LogError,x=factor(Condition,levels=c("Ctrl","Cir","Fru","Ord")),color=factor(Condition,levels=c("Ctrl","Cir","Fru","Ord")))) +
  labs(title="Error by Layout Condition",x="Condition") +
  scale_color_discrete(name="Condition")


```

```{r}

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord"))) +
  geom_density(aes(LogError,color=NetVisExperience)) +
  labs(title="Error by Expertise",x="Expertise") +
  scale_color_discrete(name="Expertise")

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord"))) +
  geom_boxplot(aes(y=LogError,x=NetVisExperience,color=NetVisExperience)) +
  labs(title="Error by Expertise",x="Expertise") +
  scale_color_discrete(name="Expertise")


```

```{r}

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord")) %>% filter(Dataset!=0)) +
  geom_violin(aes(Task,LogError, fill=Task)) + 
  labs(title="Tasks by Layout Condition") +
  guides(fill="none") +
  facet_wrap(~Condition)

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord")) %>% filter(Dataset!=0)) +
  geom_boxplot(aes(factor(Condition, levels=c("Ctrl","Cir","Fru","Ord")),LogError, fill=Condition)) + 
  labs(title="Tasks by Layout Condition",x="Condition") +
  guides(fill="none") +
  facet_wrap(~Task)

ggplot(graded_num_ans %>% filter(Condition %in% c("Ctrl","Cir","Fru","Ord")) %>% filter(Dataset!=0)) +
  geom_density(aes(LogError, color=factor(Condition, levels=c("Ctrl","Cir","Fru","Ord")))) + 
  labs(title="Tasks by Layout Condition",x="Condition") +
  scale_color_discrete(name="Condition") +
  facet_wrap(~Task)

```

```{r}

ggplot(graded_num_ans) +
  geom_density(aes(LogError))

```

### dive in after JMP

```{r}

graphics %>% filter(Dataset %in% c(5,7), Task=="LargeClust1") %>% ggplot() + geom_boxplot(aes(x=factor(Dataset),y=LogError))

graphics %>% filter(Dataset %in% c(5,7), Task=="LargeClust1") %>% ggplot() + geom_boxplot(aes(x=factor(Dataset),y=Response))

median(graphics$Response[graphics$Dataset==7 & graphics$Task=="LargeClust1"])
```

```{r}

#ggplot(graphics %>% filter(Response>0)) +
ggplot(graphics) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(!(Dataset==6)), 
             aes(y=CorrectAnswer,x=factor(Dataset)))+
  #scale_y_continuous(limits=c(0,100)) +
  #labs(title="% Nodes in Largest Cluster",x="Dataset") +
  guides(fill="none") +
  facet_grid(Task~., scales="free_y")

ggplot(graphics) +
  geom_density(aes(x=Response)) + 
   #scale_y_continuous(limits=c(0,100)) +
  #labs(title="% Nodes in Largest Cluster",x="Dataset") +
  scale_x_log10() +
  facet_wrap(~Task, scales="free_x")

```

```{r}

# removing zeroes because of log transform on y-axis; better way? 

ggplot(graphics %>% filter(Task=="AvgDeg",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  #geom_boxplot(aes(factor(Dataset),Response), width=.1, alpha=.3) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="AvgDeg",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Average Degree",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="BC",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=node_lookup %>% filter(Task=="BC",correct==TRUE,!(Dataset %in% c(0,6))),aes(y=NodeValue,x=factor(Dataset)))+
#  scale_y_log10(limits=c(.1,10000)) +
  scale_y_log10() +
  labs(title="Node with Highest Betweenness Centrality",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="ClickHighDeg",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=node_lookup %>% filter(Task=="ClickHighDeg",correct==TRUE,!(Dataset %in% c(0,6))),aes(y=NodeValue,x=factor(Dataset)))+
  geom_text(data=node_lookup %>% filter(Task=="ClickHighDeg",correct==TRUE,!(Dataset %in% c(0,6))),aes(y=NodeValue+5,x=factor(Dataset),label=NodeValue))+
  #scale_y_log10(limits=c(.1,10000)) +
  #scale_y_log10() +
  labs(title="Node with Highest Degree",x="Dataset") +
  guides(fill="none")

high_deg_votes <- graded_nodes %>% filter(Task=="ClickHighDeg",Dataset!=0,NetVisExperience=="Low",Condition%in% c("Ctrl","Phr","Siz","Col")) %>% group_by(Dataset,NodeID) %>% summarise(votes=n(),distance=mean(Distance),rank=mean(NodeRank),NodeX=mean(NodeXAdjusted),NodeY=mean(NodeYAdjusted))

ggplot(high_deg_votes) +
  geom_col(aes(rank,votes)) +
  #coord_flip() +
  labs(title="Rank of Selected Node for Highest Degree Task by Dataset",
       x="Rank of selected node", y="Number of times selected") +
  facet_wrap(~Dataset, scales="free_x")


high_bc_votes <- graded_nodes %>% filter(Task=="BC",Dataset!=0,NetVisExperience=="Low",Condition%in% c("Ctrl","Phr","Siz","Col")) %>% group_by(Dataset,NodeID) %>% summarise(votes=n(),distance=mean(Distance),rank=mean(NodeRank),NodeX=mean(NodeXAdjusted),NodeY=mean(NodeYAdjusted))

ggplot(high_bc_votes) +
  geom_col(aes(rank,votes)) +
  #coord_flip() +
  labs(title="Rank of Selected Node for Betweenness Centrality Task by Dataset",
       x="Rank of selected node", y="Number of times selected") +
  facet_wrap(~Dataset, scales="free_x")

ggplot(graphics %>% filter(Task=="NumNodes",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumNodes",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Nodes",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="NumLinks",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumLinks",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Links",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="NumHighDegree",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumHighDegree",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  geom_text(data=num_ans_lookup %>% filter(Task=="NumHighDegree",!(Dataset %in% c(0,6))),aes(y=0.8*CorrectAnswer,x=factor(Dataset),label=CorrectAnswer))+
#  scale_y_log10(limits=c(.1,10000)) +
  scale_y_log10() +
  labs(title="Degree of Highest Degree Node",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="NumClust",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="NumClust",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_log10(limits=c(.1,10000)) +
  labs(title="Number of Clusters",x="Dataset") +
  guides(fill="none")

ggplot(graphics %>% filter(Task=="LargeClust1",Dataset!=0,Response>0)) +
  geom_violin(aes(factor(Dataset),Response, fill=factor(Dataset))) + 
  geom_point(data=num_ans_lookup %>% filter(Task=="LargeClust1",!(Dataset %in% c(0,6))),aes(y=CorrectAnswer,x=factor(Dataset)))+
  scale_y_continuous(limits=c(0,100)) +
  labs(title="% Nodes in Largest Cluster",x="Dataset") +
  guides(fill="none")

```

```{r}

ggplot() + 
  geom_point(data = node_lookup %>% filter(Dataset==7,Task=="BC",Condition=="Ctrl"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = high_bc_votes %>% filter(Dataset==7,rank==33), 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  #facet_grid(Dataset~Condition) +
  scale_y_reverse() +
  theme_bw()

ggplot() + 
  geom_point(data = node_lookup %>% filter(Dataset==3,Task=="BC",Condition=="Ctrl"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = high_bc_votes %>% filter(Dataset==3,rank==14), 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  #facet_grid(Dataset~Condition) +
  scale_y_reverse() +
  theme_bw()

```

```{r}

ggplot(graphics %>% filter(Task=="NumClust")) +
  geom_density(aes(Response)) +
  #coord_flip() +
  labs(title="Number of Clusters") +
  scale_x_log10() +
  facet_wrap(~Dataset, scales="free_x")

ggplot(graphics %>% filter(Task=="NumClust",!is.na(ClustConf))) +
  geom_density(aes(Response,color=ClustConf)) +
  #coord_flip() +
  labs(title="Number of Clusters by Confidence") +
  scale_x_log10() +
  scale_color_grey(name="Cluster Confidence",start=0.2,end=0.7) +
  #facet_wrap(~Dataset, scales="free_x") +
  facet_wrap(~Dataset) +
  theme_bw()

ggplot(graphics %>% filter(Task=="NumClust",!is.na(ClustConf))) +
  geom_boxplot(aes(x=ClustConf, y=Response, color=ClustConf)) +
  #coord_flip() +
  labs(title="Number of Clusters by Confidence") +
  scale_y_log10() +
  scale_x_discrete(limits = rev(levels(graphics$ClustConf))) +
  scale_color_grey(name="Cluster Confidence",start=0.2,end=0.7) +
  facet_wrap(~Dataset) +
  coord_flip() +
  theme_bw()

ggplot(graphics %>% filter(Task=="NumClust",!is.na(ClustConf))) +
  geom_boxplot(aes(x=ClustConf, y=Response, color=ClustConf)) +
  #coord_flip() +
  labs(title="Number of Clusters by Confidence") +
  scale_y_log10() +
  scale_x_discrete(limits = rev(levels(graphics$ClustConf))) +
  scale_color_grey(name="Cluster Confidence",start=0.2,end=0.7) +
  geom_hline(aes(yintercept=CorrectAnswer,group=Dataset),colour="red") +
  facet_wrap(~Dataset) +
  coord_flip() +
  guides(color="none") +
  theme_bw()

ggplot(graphics %>% 
         filter(Task=="NumClust", !is.na(ClustConf)) %>% 
         group_by(Dataset,ClustConf) %>% 
         summarise(var=var(Response), sd=sd(Response), avgLogError=mean(LogError))) +
  geom_col(aes(ClustConf,sd)) +
  scale_x_discrete(limits = rev(levels(graphics$ClustConf))) +
  coord_flip() +
  facet_wrap(~Dataset) +
  labs(title="Standard Deviation of the Response by Cluster Confidence",y="Standard deviation of the response",x="Cluster Confidence")

ggplot(graphics %>% filter(Task=="NumClust",!is.na(ClustConf)) %>% left_join(num_ans_lookup %>% filter(Task=="NumNodes") %>% rename(NumNodes=CorrectAnswer) %>% dplyr::select(Dataset,NumNodes))) +
  geom_point(aes(x=Response, y=NumNodes)) +
  #coord_flip() +
  labs(title="Estimated Number of Clusters by Number of Nodes in Network") +
  facet_grid(.~ClustConf, scales="free")

ggplot(graphics %>% 
         filter(Task=="NumClust", !is.na(ClustConf)) %>% 
         group_by(Dataset,ClustConf) %>% 
         summarise(var=var(Response), sd=sd(Response), avgLogError=mean(LogError))) +
  geom_point(aes(sd, avgLogError, color=ClustConf)) +
  facet_wrap(~Dataset)

```

```{r}

ggplot(graphics %>% filter(Dataset!=0)) +
  geom_boxplot(aes(factor(Dataset), LogError, fill=factor(Dataset))) + 
  labs(title="Tasks by Dataset Condition",x="Dataset") +
  guides(fill="none") +
  facet_wrap(~Task)

ggplot(graphics %>% filter(Dataset!=0)) +
  geom_boxplot(aes(factor(Dataset), Response, fill=factor(Dataset))) + 
  labs(title="Tasks by Dataset Condition",x="Dataset") +
  guides(fill="none") +
  scale_y_log10() +
  facet_wrap(~Task, scales="free")


```

```{r}

#over- or underestimating?

ggplot(graphics) +
  geom_histogram(aes(RawDifference,fill=RawDifference>0))+
  scale_y_continuous(limits=c(0,1))+
  facet_wrap(~Task, scales="free")

```

```{r}

layoutfac %>% filter(Dataset %in% c(1,7), Task=="LargeClust1") %>% ggplot() + geom_boxplot(aes(x=factor(Dataset),y=LogError))

layoutfac %>% filter(Dataset %in% c(1,7), Task=="LargeClust1") %>% ggplot() + geom_boxplot(aes(x=factor(Dataset),y=Response))

median(layoutfac$Response[layoutfac$Dataset==7 & layoutfac$Task=="LargeClust1"])
median(layoutfac$Response[layoutfac$Dataset==1 & layoutfac$Task=="LargeClust1"])
sd(layoutfac$Response[layoutfac$Dataset==7 & layoutfac$Task=="LargeClust1"])
sd(layoutfac$Response[layoutfac$Dataset==1 & layoutfac$Task=="LargeClust1"])
median(layoutfac$LogError[layoutfac$Dataset==7 & layoutfac$Task=="LargeClust1"])
median(layoutfac$LogError[layoutfac$Dataset==1 & layoutfac$Task=="LargeClust1"])

```

```{r}

ggplot(node_lookup %>% filter(Dataset %in% c(1,7,9), Task=="ClickHighDeg", Condition=="Ctrl")) +
  geom_histogram(aes(NodeValue)) +
  facet_grid(.~Dataset, scales="free")

high_deg_votes_lay <- graded_nodes %>% filter(Task=="ClickHighDeg",Dataset %in% c(1,7,9),Condition %in% c("Cir","Ctrl","Fru","Ord")) %>% group_by(Dataset,Condition,NodeID) %>% summarise(votes=n(),distance=mean(Distance),rank=mean(NodeRank),NodeX=mean(NodeXAdjusted),NodeY=mean(NodeYAdjusted),NodeValue=mean(NodeValue))

ggplot() + 
  geom_point(data = node_lookup %>% filter(Condition %in% c("Cir","Ctrl","Fru","Ord"), Dataset %in% c(1,7,9),Task=="ClickHighDeg"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted,size=NodeValue),colour="gray50") +
  geom_point(data = high_deg_votes_lay, 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  facet_grid(Dataset~Condition) +
  scale_y_reverse() +
  theme_bw()

ggplot() + 
  geom_point(data = high_deg_votes_lay, 
             aes(x=NodeValue,y=votes)) + 
  facet_grid(Dataset~Condition) +
  theme_bw()

edges_vis <- all_edges %>% 
  rowid_to_column("EdgeID") %>% 
  gather("end","NodeID",2:3) %>%
  separate(NodeID,c("Condition","Dataset","NodeXOriginal","NodeYOriginal"), 
           sep="[_]", remove=FALSE, convert=TRUE) %>%
  mutate(NodeXAdjusted = NodeXOriginal * 150 / 72, NodeYAdjusted = NodeYOriginal * 150 / 72)
  
ggplot() + 
  geom_line(data=edges_vis %>% filter(Condition %in% c("Cir","Ctrl","Fru","Ord"), Dataset %in% c(1,7,9)), 
            aes(x=NodeXAdjusted,y=NodeYAdjusted,group=EdgeID)) +
  geom_point(data = node_lookup %>% filter(Condition %in% c("Cir","Ctrl","Fru","Ord"), Dataset %in% c(1,7,9),Task=="ClickHighDeg"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted,size=NodeValue),colour="gray50") +
  geom_point(data = high_deg_votes_lay, 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  facet_grid(Dataset~Condition) +
  scale_y_reverse() +
  theme_bw()

```

```{r}

ggplot() + 
  geom_line(data=edges_vis %>% filter(Condition=="Fru", Dataset==9), 
            aes(x=NodeXAdjusted,y=NodeYAdjusted,group=EdgeID),color="gray80") +
  geom_point(data = node_lookup %>% filter(Dataset==9,Task=="ClickHighDeg",Condition=="Fru"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = high_deg_votes_lay %>% filter(Dataset==9,Condition=="Fru"), 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  #facet_grid(Dataset~Condition) +
  scale_y_reverse() +
  theme_classic()

ggplot() + 
  geom_line(data=edges_vis %>% filter(Condition=="Fru", Dataset %in% c(7,9)), 
            aes(x=NodeXAdjusted,y=NodeYAdjusted,group=EdgeID),color="gray80") +
  geom_point(data = node_lookup %>% filter(Dataset %in% c(7,9),Task=="ClickHighDeg",Condition=="Fru"),
             aes(x=NodeXAdjusted,y=NodeYAdjusted),colour="gray50") +
  geom_point(data = high_deg_votes_lay %>% filter(Dataset %in% c(7,9),Condition=="Fru"), 
             aes(x=NodeX,y=NodeY,size=votes), colour="red", alpha=.5) + 
  facet_grid(.~Dataset) +
  scale_y_reverse() +
  theme_classic()

```



## Output


```{r, eval=FALSE}

# add charts to Word Doc

# ggplot example
gg <- ggplot(mtcars, aes(x = mpg , y = wt, colour = qsec)) + geom_point() + theme_minimal()

# produce an emf file containing the ggplot (won't be editable in Word, but will be vector)
filename <- tempfile(fileext = ".emf")
emf(file = filename, width = 6, height = 7)
print(gg)
dev.off()

read_docx() %>% 
  body_add_img(src = filename, width = 6, height = 7) %>% 
  print(target = "~/Desktop/demo_emf.docx") %>% 
  invisible()

# add charts to PowerPoint (should be editable, though they won't be a chart per se)

read_pptx() %>% 
  add_slide(layout = "Title and Content", master = "Office Theme") %>% 
  ph_with_vg(code = print(gg), type = "body") %>% 
  print(target = "~/Desktop/demo_rvg.pptx") %>% 
  invisible()


```

