---
title: "Analysis for Degree of Highest Degree Node task, Graphics conditions"
author: "Angela Zoss"
date: "March 23, 2018"
output: github_document
---

```{r}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, message=FALSE}

source('GlobalSetup.R')

```

```{r}

# load full graphics dataset for summary graphics

graphics_numhighdeg <- readRDS(file.path(analysisDataDir, "GraphicsNumHD.rds"))


```


#### lme4

```{r, cache=TRUE, eval=FALSE}

# Condition

graph.numhd.lmer.cond <- lmer(LogError ~ Condition + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.cond) # Color and Phrasing very significant, Size not at all

anova(graph.numhd.lmer.cond)

# Condition is significant (p=2.557e-06); trying Ctrl_dummy

graph.numhd.lmer.ctrldummy <- lmer(LogError ~ Ctrl_dummy + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.ctrldummy)

anova(graph.numhd.lmer.ctrldummy)

# Ctrl_dummy is significant (p=0.000624)

graph.numhd.lmer.condphr <- lmer(LogError ~ ConditionPhrasing + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.condphr) 

anova(graph.numhd.lmer.condphr)

# ConditionPhrasing is significant (p=0.003696)

graph.numhd.lmer.condgr <- lmer(LogError ~ ConditionGraphics + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.condgr) 

anova(graph.numhd.lmer.condgr)

# ConditionGraphics is significant (p=0.001828)

graph.numhd.lmer.condcol <- lmer(LogError ~ ConditionColor + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.condcol) 

anova(graph.numhd.lmer.condcol)

# ConditionColor is significant (p=0.002186)


graph.numhd.lmer.dataset <- lmer(LogError ~ Dataset + (1|Demo.ResponseID), data = graphics_numhighdeg, REML = T)

lmsum <- summary(graph.numhd.lmer.dataset)
lmsum
#names(lmsum)

anova(graph.numhd.lmer.dataset)

# Dataset is significant (p < 1.3e-12); trying QuestionOrder

graph.numhd.lmer <- lmer(LogError ~ QuestionOrder + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# QuestionOrder is not significant; trying DatasetOrder

graph.numhd.lmer.dataord <- lmer(LogError ~ DatasetOrder + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.dataord)

anova(graph.numhd.lmer.dataord)

# DatasetOrder is significant (p=0.005725); trying DatasetDuration

graph.numhd.lmer <- lmer(LogError ~ DatasetDuration + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# DatasetDuration is barely not significant (p=0.05675); trying DatasetStartTime

graph.numhd.lmer <- lmer(LogError ~ DatasetStartTime + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# DatasetStartTime is not significant; trying TaskOrder

graph.numhd.lmer <- lmer(LogError ~ TaskOrder + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# TaskOrder is not significant; trying CorrectAnswer

graph.numhd.lmer <- lmer(LogError ~ CorrectAnswer + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# CorrectAnswer is barely not significant (p = 0.05447); trying Underestimated

graph.numhd.lmer.underest <- lmer(LogError ~ Underestimated + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.underest)

anova(graph.numhd.lmer.underest)

# Underestimated is highly significant (p = 6.661e-16); trying Overestimated

graph.numhd.lmer.overest <- lmer(LogError ~ Overestimated + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.overest)

anova(graph.numhd.lmer.overest)

# Overestimated is highly significant (p = 1.165e); trying Stats.Q_TotalDuration

graph.numhd.lmer <- lmer(LogError ~ Stats.Q_TotalDuration + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Stats.Q_TotalDuration is not significant; trying Stats.dataset_count

graph.numhd.lmer <- lmer(LogError ~ Stats.dataset_count + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Stats.dataset_count is not significant; trying Stats.OperatingSystem

graph.numhd.lmer <- lmer(LogError ~ Stats.OperatingSystem + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer) # nothing significant

anova(graph.numhd.lmer)

# Stats.OperatingSystem is not significant (skipping combinations); trying StatsNumPixels

graph.numhd.lmer.pixels <- lmer(LogError ~ StatsNumPixels + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.pixels)

anova(graph.numhd.lmer.pixels)

# StatsNumPixels is barely significant (p=0.02101); trying Demo.age

graph.numhd.lmer.age <- lmer(LogError ~ Demo.age + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.age))), REML = T)

summary(graph.numhd.lmer.age)

anova(graph.numhd.lmer.age)

# Demo.age is significant (p=0.0159); trying Demo.gender

graph.numhd.lmer <- lmer(LogError ~ Demo.gender + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.gender))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.gender is not significant; trying Demo.lang

graph.numhd.lmer <- lmer(LogError ~ Demo.lang + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.lang))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.lang is not significant; trying Demo.educ

graph.numhd.lmer <- lmer(LogError ~ Demo.educ + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.educ))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.educ is not significant; trying Demo.acfield

graph.numhd.lmer <- lmer(LogError ~ Demo.acfield + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.acfield))), REML = T)

summary(graph.numhd.lmer) # nothing significant

anova(graph.numhd.lmer)

# Demo.acfield is not significant (skipping groups); trying Demo.dailytech_Computer

graph.numhd.lmer <- lmer(LogError ~ Demo.dailytech_Computer + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.dailytech_Computer))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.dailytech_Computer is not significant; trying Demo.dailytech_Tablet

graph.numhd.lmer <- lmer(LogError ~ Demo.dailytech_Tablet + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.dailytech_Tablet))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.dailytech_Computer is not significant; trying Demo.dailytech_SmartPhone

graph.numhd.lmer <- lmer(LogError ~ Demo.dailytech_SmartPhone + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.dailytech_SmartPhone))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.dailytech_SmartPhone is not significant; trying Demo.weeklygaming

graph.numhd.lmer <- lmer(LogError ~ Demo.weeklygaming + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.weeklygaming))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.weeklygaming is not significant; trying Demo.expdataanal

graph.numhd.lmer <- lmer(LogError ~ Demo.expdataanal + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expdataanal))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.expdataanal is not significant; trying Demo.expdatavis

graph.numhd.lmer <- lmer(LogError ~ Demo.expdatavis + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expdatavis))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.expdatavis is not significant; trying Demo.expreadnetvis

graph.numhd.lmer <- lmer(LogError ~ Demo.expreadnetvis + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expreadnetvis))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.expreadnetvis is not significant; trying Demo.expreadnetvis.alot

graph.numhd.lmer <- lmer(LogError ~ Demo.expreadnetvis.alot + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expreadnetvis.alot))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.expreadnetvis.alot is not significant; trying Demo.expcreatenetvis

graph.numhd.lmer <- lmer(LogError ~ Demo.expcreatenetvis + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expcreatenetvis))), REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# Demo.expcreatenetvis is not significant; trying Demo.expcreatenetvis.alot

graph.numhd.lmer <- lmer(LogError ~ Demo.expcreatenetvis.alot + (1|Demo.ResponseID), data=graphics_numhighdeg %>% filter(!(is.na(Demo.expcreatenetvis.alot))), REML = T)

summary(graph.numhd.lmer) # doesn't reach significance

anova(graph.numhd.lmer)

# Demo.expcreatenetvis.alot is not significant; trying AvgDeg

graph.numhd.lmer.avgdeg <- lmer(LogError ~ AvgDeg + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.avgdeg)

anova(graph.numhd.lmer.avgdeg)

# AvgDeg is significant (p=6.871e-08); trying Density

graph.numhd.lmer.dens <- lmer(LogError ~ Density + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.dens)

anova(graph.numhd.lmer.dens)

# Density is significant (p=1.913e-07); trying LargeClust1

graph.numhd.lmer.lgclust <- lmer(LogError ~ LargeClust1 + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.lgclust)

anova(graph.numhd.lmer.lgclust)

# LargeClust1 is significant (p=5.644e-08); trying Modularity

graph.numhd.lmer.mod <- lmer(LogError ~ Modularity + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.mod)

anova(graph.numhd.lmer.mod)

# Modularity is significant (p=0.000103); trying NumClust

graph.numhd.lmer.numclust <- lmer(LogError ~ NumClust + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.numclust)

anova(graph.numhd.lmer.numclust)

# NumClust is significant (p=0.0008824); trying NumHighDegree

graph.numhd.lmer <- lmer(LogError ~ NumHighDegree + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# NumHighDegree is not quite significant (p=0.05447); trying NumLinks

graph.numhd.lmer <- lmer(LogError ~ NumLinks + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# NumLinks is not significant; trying NumNodes

graph.numhd.lmer.numnodes <- lmer(LogError ~ NumNodes + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer.numnodes)

anova(graph.numhd.lmer.numnodes)

# NumNodes is significant (p=0.0009184); trying NumNodesClust1

graph.numhd.lmer <- lmer(LogError ~ NumNodesClust1 + (1|Demo.ResponseID), data=graphics_numhighdeg, REML = T)

summary(graph.numhd.lmer)

anova(graph.numhd.lmer)

# NumNodesClust1 is not quite significant (p=0.05285); 


```

```{r}

temp <- graphics_numhighdeg %>% dplyr::select(
  Demo.ResponseID, LogError, Condition, Ctrl_dummy, ConditionPhrasing, ConditionGraphics, ConditionColor, Dataset, DatasetOrder, Underestimated, Overestimated, StatsNumPixels, Demo.age, AvgDeg, Density, LargeClust1, Modularity, NumClust, NumNodes) %>% drop_na()

temp <- temp %>% mutate(StatsNumPixels=scale(StatsNumPixels))

temp.numhd.gr <- temp %>% mutate(DatasetOrder=factor(DatasetOrder))

```

Run this one

```{r, eval=FALSE}

# combinations of individual predictors

graph.numhd.lmer.full <- lmer(LogError ~ Condition + 
                                Dataset +
                                DatasetOrder +
                                Overestimated +
                                StatsNumPixels +
                                (1|Demo.ResponseID), 
                              data=temp, REML = T)

summary(graph.numhd.lmer.full)

anova(graph.numhd.lmer.full)

```

Run this one

```{r, eval=FALSE}

# interactions

graph.numhd.lmer.full.int <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    DatasetOrder +
                                    Overestimated +
                                    StatsNumPixels +
                                    Condition:Dataset +
                                    (1|Demo.ResponseID), 
                                  data=temp, REML = T)

summary(graph.numhd.lmer.full.int)

anova(graph.numhd.lmer.full.int)

anova(graph.numhd.lmer.full.int,graph.numhd.lmer.full)

# definitely keep the interaction

graph.numhd.lmer.full.int.2 <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    DatasetOrder +
                                    Overestimated +
                                    StatsNumPixels +
                                    Condition:Dataset +
                                      Dataset:Overestimated +
                                    (1|Demo.ResponseID), 
                                  data=temp, REML = T)

summary(graph.numhd.lmer.full.int.2)

anova(graph.numhd.lmer.full.int.2)

anova(graph.numhd.lmer.full.int.2,graph.numhd.lmer.full.int)

graph.numhd.lmer.full.int.3 <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    DatasetOrder +
                                    Overestimated +
                                    StatsNumPixels +
                                    Condition:Dataset +
                                      Dataset:Overestimated +
                                      DatasetOrder:Overestimated +
                                    (1|Demo.ResponseID), 
                                  data=temp, REML = T)

summary(graph.numhd.lmer.full.int.3)

anova(graph.numhd.lmer.full.int.3)

anova(graph.numhd.lmer.full.int.3,graph.numhd.lmer.full.int.2)

# keeping graph.numhd.lmer.full.int.3

graph.numhd.lmer.full.int.4 <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    Condition:Dataset +
                                      Dataset:Overestimated +
                                      DatasetOrder:Overestimated +
                                    (1|Demo.ResponseID), 
                                  data=temp, REML = T)

summary(graph.numhd.lmer.full.int.4)

anova(graph.numhd.lmer.full.int.4)

anova(graph.numhd.lmer.full.int.4, graph.numhd.lmer.full.int.3)

# no significant difference and 4 is way simpler, so keeping 4

graph.numhd.lmer.full.int.5 <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    Condition:Dataset +
                                      Dataset:Overestimated +
                                      factor(DatasetOrder):Overestimated +
                                    (1|Demo.ResponseID), 
                                  data=temp, REML = T)

summary(graph.numhd.lmer.full.int.5)

anova(graph.numhd.lmer.full.int.5)

anova(graph.numhd.lmer.full.int.4)

anova(graph.numhd.lmer.full.int.4, graph.numhd.lmer.full.int.5)

# should keep 5, where datasetorder is treated as a factor; only a slight difference between 4 and 5

# redoing 5 with factor in the dataset

graph.numhd.lmer.full.int.6 <- lmer(LogError ~ Condition + 
                                    Dataset +
                                    Condition:Dataset +
                                      Dataset:Overestimated +
                                      DatasetOrder:Overestimated +
                                    (1|Demo.ResponseID), 
                                  data=temp.numhd.gr, REML = T)

summary(graph.numhd.lmer.full.int.6)

anova(graph.numhd.lmer.full.int.6)

```

Run this one

```{r, eval=FALSE}

#SAVE THE RESULTS
save(graph.numhd.lmer.full.int.6, 
     file = file.path(analysisDataDir,"fits/graph_numhd_lmer_int.RData"))

```

##### Load pre-built model

```{r}

load(file.path(analysisDataDir,"fits/graph_numhd_lmer_int.RData"))

```

```{r, cache=TRUE}

rand(graph.numhd.lmer.full.int.6)

# result shows that random effects of participant are *not* significant (p=1)

#ranef(graph.numhd.lmer.full.int.4)

# displays the random effects; not that useful

# unlike lme(), lmer() doesn't allow for heterogeneous error variance structures (the "weights")

(r2nsj = r2beta(graph.numhd.lmer.full.int.6, method = 'nsj', partial = TRUE))[1,'Rsq']

ggplot(graphics_numhighdeg) + geom_histogram(aes(LogError), binwidth=.005) + labs(title="Distribution of LogError values for Degree of Highest Degree Node task,\ngraphics conditions")



```

```{r}

plot(graph.numhd.lmer.full.int.6)

plot(graph.numhd.lmer.full.int.6, resid(., scaled=TRUE) ~ fitted(.), abline = 0)

plot(graph.numhd.lmer.full.int.6, resid(.) ~ fitted(.) | Condition, abline = 0)

plot(graph.numhd.lmer.full.int.6, resid(., scaled=TRUE) ~ fitted(.) | Condition, abline = 0)

plot(graph.numhd.lmer.full.int.6, LogError ~ fitted(.), abline = c(0,1))



```

```{r}

graph.numhd.lmer.full.int.6.f <- fortify(graph.numhd.lmer.full.int.6)

ggplot(graph.numhd.lmer.full.int.6.f, aes(.fitted,.resid)) + 
  geom_point() +
  #facet_grid(.~Sex) + 
  geom_hline(yintercept=0)

ggplot(graph.numhd.lmer.full.int.6.f, aes(.fitted,LogError)) + 
  geom_point() +
  geom_abline(aes(slope = 1, intercept = 0))

ggplot(graph.numhd.lmer.full.int.6.f, aes(LogError,.fitted)) +
geom_point() +
geom_abline(aes(slope = 1, intercept = 0)) +
#scale_y_continuous(limits=c(0,0.3)) +
labs(title="Real vs. Predicted LogError values for Degree of Highest Degree Node task,\ngraphics conditions")


```

```{r, eval=FALSE}

# TO DO: check out interpretation for these plots??

prof <-  profile(graph.numhd.lmer.full.int.4, optimizer="Nelder_Mead", which="beta_")

prof.CI <- confint(prof)

CI2 <- confint(graph.numhd.lmer.full.int.4, maxpts = 8)

xyplot(prof)

xyplot(prof, absVal = TRUE)

xyplot(prof, conf = c(0.95, 0.99), main = "95% and 99% profile() intervals")

# can also apply logProf() and varianceProf() to profile object

densityplot(prof)

splom(prof)

```

#### Least Squares Means

Do for each categorical predictor. 

Final model:
LogError ~ Condition + Dataset + Condition:Dataset + Dataset:Overestimated + DatasetOrder:Overestimated + (1|Demo.ResponseID)

##### Condition

###### lsmeans - older than, e.g., numnodes
```{r, eval=FALSE}

# trying lmerTest::lsmeansLT

# note = lmerTest::lsmeans will only report lsmeans for factor variables and is deprecated

graph.numhd.lsmlt.cond.2 <- lsmeansLT(graph.numhd.lmer.full.int.4, test.effs = "Condition")

plot(graph.numhd.lsmlt.cond.2) # not a completely terrible style, but not sorted properly

graph.numhd.lsmlt.cond.2.df <- dplyr::as_data_frame(graph.numhd.lsmlt.cond.2$lsmeans.table)

graph.numhd.lsmlt.cond.2.df

graph.numhd.lsmlt.cond.2.df$Condition <- factor(graph.numhd.lsmlt.cond.2.df$Condition, levels=graph.numhd.lsmlt.cond.2.df %>% arrange(desc(Estimate)) %>% dplyr::select(Condition) %>% unlist())

graph.numhd.lsmlt.cond.2.df %>% arrange(desc(Estimate))

graph.numhd.lsmlt.cond.2.df <- graph.numhd.lsmlt.cond.2.df %>% 
  mutate(sig.levels = factor(case_when(
    `p-value` < .0001 ~ sig.level.names[1],
    `p-value` < .001 ~ sig.level.names[2],
    `p-value` < .01 ~ sig.level.names[3],
    `p-value` < .05 ~ sig.level.names[4],
    TRUE ~ sig.level.names[5]
    )
  ,levels=sig.level.names,ordered=TRUE))

graph.numhd.lsmlt.cond.2.df

ggplot(graph.numhd.lsmlt.cond.2.df) +
  geom_errorbar(aes(x=Condition,ymax=`Upper CI`,ymin=`Lower CI`), width=.2) +
  geom_point(aes(x=Condition,y=Estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r, eval=FALSE}

# LSMeans Difference data

graph.numhd.difflsmlt.cond <- difflsmeans(graph.numhd.lmer.full.int.4, test.effs = "Condition")

plot(graph.numhd.difflsmlt.cond)

graph.numhd.difflsmlt.cond.df <- dplyr::as_data_frame(graph.numhd.difflsmlt.cond$diffs.lsmeans.table, rownames="Pair")

graph.numhd.difflsmlt.cond.df

graph.numhd.difflsmlt.cond.df <- graph.numhd.difflsmlt.cond.df %>% mutate(Pair=sub("Condition ","",Pair)) %>% separate(Pair, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

copy <- graph.numhd.difflsmlt.cond.df %>% rename(From=To,To=From)

graph.numhd.difflsmlt.cond.df <- bind_rows(graph.numhd.difflsmlt.cond.df,copy)

graph.numhd.difflsmlt.cond.df$Pair <- factor(graph.numhd.difflsmlt.cond.df$Pair, levels=graph.numhd.difflsmlt.cond.df %>% arrange(desc(Estimate)) %>% dplyr::select(Pair) %>% distinct() %>% unlist())

cond.lev <- c("Ctrl","Phr","Col","Siz")

graph.numhd.difflsmlt.cond.df$From <- factor(graph.numhd.difflsmlt.cond.df$From, levels=cond.lev)
graph.numhd.difflsmlt.cond.df$To <- factor(graph.numhd.difflsmlt.cond.df$To, levels=cond.lev)

graph.numhd.difflsmlt.cond.df %>% arrange(desc(Estimate))

graph.numhd.difflsmlt.cond.df <- graph.numhd.difflsmlt.cond.df %>% 
  mutate(sig.levels = factor(case_when(
    `p-value` < .0001 ~ sig.level.names[1],
    `p-value` < .001 ~ sig.level.names[2],
    `p-value` < .01 ~ sig.level.names[3],
    `p-value` < .05 ~ sig.level.names[4],
    TRUE ~ sig.level.names[5]
    )
  ,levels=sig.level.names,ordered=TRUE))

ggplot(graph.numhd.difflsmlt.cond.df) +
  geom_errorbar(aes(x=Pair,ymax=`Upper CI`,ymin=`Lower CI`), width=.5) +
  geom_point(aes(x=Pair,y=Estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(graph.numhd.difflsmlt.cond.df) +
  geom_errorbar(aes(x=Pair,ymax=`Upper CI`,ymin=`Lower CI`), width=.5) +
  geom_point(aes(x=Pair,y=Estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(graph.numhd.difflsmlt.cond.df) +
  geom_tile(aes(x=To,y=ordered(From,levels=rev(cond.lev)),fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.difflsmlt.cond.df) +
  geom_count(aes(x=To,y=ordered(From,levels=rev(cond.lev)),size=abs(Estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")
  
```

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(graph.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(graphics_numhighdeg, table(Dataset,Overestimated))
# ref_grid(graph.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

graph.numhd.emm.cond <- emmeans(graph.numhd.lmer.full.int.6, "Condition", nesting = NULL)
#graph.numhd.emm.condition <- emmeans(graph.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

graph.numhd.emm.cond

graph.numhd.emm.cond.df <- dplyr::as_data_frame(graph.numhd.emm.cond)

graph.numhd.emm.cond.df

graph.numhd.emm.cond.cld <- cld(graph.numhd.emm.cond,
                                   details=TRUE,
                                   #alpha=0.01,
                                   #by="Dataset",
                                   #Letters="|||||||||||||||||||",
                                   sort=TRUE
)

graph.numhd.emm.cond.cld.df <- graph.numhd.emm.cond.cld$emmeans

graph.numhd.emm.cond.cld.df %>% dplyr::select(Condition,.group)

graph.numhd.emm.cond.cld.df

graph.numhd.emm.cond.cld.df$Condition <- factor(graph.numhd.emm.cond.cld.df$Condition, levels=graph.numhd.emm.cond.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())


#emmip(graph.numhd.lmer.full.int.4, ~Condition, CIs = TRUE)
emmip(graph.numhd.emm.cond, ~Condition, CIs = TRUE)
plot(graph.numhd.emm.cond)
#plot(graph.numhd.emm.cond, comparisons = TRUE)

graph.numhd.emm.cond.cld.df %>% arrange(desc(emmean))

ggplot(graph.numhd.emm.cond.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Condition,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip() +
labs(title="Estimated Marginal Means for Condition for Degree of\nHighest Degree Node task, graphics conditions")

#plot(ref_grid(graph.numhd.lmer.full.int.4), by="Condition") 
# try to figure this out? maybe only works on the interaction?

```

```{r}

graph.numhd.emm.cond.pairs <- dplyr::as_data_frame(pairs(graph.numhd.emm.cond)) 
graph.numhd.emm.cond.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(graph.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

cond.pairs.CI <- confint(pairs(graph.numhd.emm.cond))

graph.numhd.emm.cond.pairs <- full_join(graph.numhd.emm.cond.pairs, cond.pairs.CI)

#graph.numhd.diffemm.condition <- emmeans(graph.numhd.lmer.full.int.4, pairwise ~ Condition)
#graph.numhd.diffemm.condition$contrasts
#contrast(graph.numhd.emm.condition)
#confint(graph.numhd.emm.condition)
#pairs(graph.numhd.emm.condition, details=TRUE)
#confint(contrast(graph.numhd.emm.condition))
#confint(pairs(graph.numhd.emm.condition))
#coef(pairs(graph.numhd.emm.condition))


plot(pairs(graph.numhd.emm.cond))
plot(pairs(graph.numhd.emm.cond), comparisons = TRUE)


graph.numhd.emm.cond.pairs$sig.levels <- 
  case_when(graph.numhd.emm.cond.pairs$p.value < .0001 ~ sig.level.names[1],
            graph.numhd.emm.cond.pairs$p.value < .001 ~ sig.level.names[2],
            graph.numhd.emm.cond.pairs$p.value < .01 ~ sig.level.names[3],
            graph.numhd.emm.cond.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

graph.numhd.emm.cond.pairs$sig.levels <- factor(graph.numhd.emm.cond.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

graph.numhd.emm.cond.pairs$contrast <- factor(graph.numhd.emm.cond.pairs$contrast, levels=graph.numhd.emm.cond.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

graph.numhd.emm.cond.pairs <- graph.numhd.emm.cond.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

ggplot(graph.numhd.emm.cond.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(graph.numhd.emm.cond.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

cond.copy <- graph.numhd.emm.cond.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

graph.numhd.emm.cond.pairs.compl <- bind_rows(graph.numhd.emm.cond.pairs, cond.copy)


cond.lev <- c("Ctrl","Phr","Col","Siz")

graph.numhd.emm.cond.pairs.compl$From <- factor(graph.numhd.emm.cond.pairs.compl$From, levels=cond.lev)
graph.numhd.emm.cond.pairs.compl$To <- factor(graph.numhd.emm.cond.pairs.compl$To, levels=cond.lev)

#graph.numlinks.emm.cond.pairs.compl %>% arrange(desc(estimate))
graph.numhd.emm.cond.pairs.compl %>% arrange(estimate)

ggplot(graph.numhd.emm.cond.pairs.compl) +
  geom_tile(aes(x=To,y=ordered(From,levels=rev(cond.lev)),fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.cond.pairs.compl) +
  geom_count(aes(x=To,y=ordered(From,levels=rev(cond.lev)),size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.cond.pairs.compl) +
  geom_tile(aes(x=To,y=ordered(From,levels=rev(cond.lev)),fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.cond.pairs.compl) +
  geom_count(aes(x=To,y=ordered(From,levels=rev(cond.lev)),size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

```

###### networks

```{r, eval=FALSE}

# try a network of the pairwise significance values?  bleh...
# using igraph

graph <- graph_from_data_frame(graph.numhd.emm.cond.pairs %>% dplyr::select(-contrast), directed=TRUE)

E(graph)$width <- abs(E(graph)$estimate)*50
E(graph)$edge.color <- sig.colors[E(graph)$sig.levels]

graph

plot(graph, 
     edge.arrow.size=.5,
     vertex.frame.color="#555555")

```

```{r}

# using ggraph and tidygraph

graph <- graph_from_data_frame(graph.numhd.emm.cond.pairs %>% dplyr::select(-contrast), directed=TRUE)

# plot using ggraph
ggraph(graph, layout = 'kk') +
  geom_edge_link(aes(start_cap = label_rect(node1.name),
                       end_cap = label_rect(node2.name),
                     color=factor(sig.level.names[sig.levels]),
                     edge_width=.5/sig.levels
                     ), 
                   arrow = arrow(length = unit(4, 'mm')))+
  geom_node_text(label = vertex_attr(graph,"name")) +
  scale_edge_color_manual("Significance Levels", values=sig.colors) +
  scale_edge_width_continuous(labels=rev(sig.level.names)) +
  theme_graph()

```

##### Dataset

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(graph.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(graphics_numhighdeg, table(Dataset,Overestimated))
# ref_grid(graph.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

graph.numhd.emm.data <- emmeans(graph.numhd.lmer.full.int.6, "Dataset", nesting = NULL)
#graph.numhd.emm.condition <- emmeans(graph.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

graph.numhd.emm.data

graph.numhd.emm.data.df <- dplyr::as_data_frame(graph.numhd.emm.data)

graph.numhd.emm.data.df


# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the graph

#xtable::xtable(graph.numhd.emm.condition)

graph.numhd.emm.data.cld <- cld(graph.numhd.emm.data,
                details=TRUE,
                #alpha=0.01,
                #by="Dataset",
                #Letters="|||||||||||||||||||",
                sort=TRUE
)

graph.numhd.emm.data.cld.df <- graph.numhd.emm.data.cld$emmeans

graph.numhd.emm.data.cld.df %>% dplyr::select(Dataset,.group)

graph.numhd.emm.data.cld.df

graph.numhd.emm.data.cld.df$Dataset <- factor(graph.numhd.emm.data.cld.df$Dataset, levels=graph.numhd.emm.data.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Dataset) %>% unlist())


#emmip(graph.numlinks.lmer.full.int, ~Condition, CIs = TRUE)
emmip(graph.numhd.emm.data, ~Dataset, CIs = TRUE)
plot(graph.numhd.emm.data)
#plot(graph.numlinks.emm.cond, comparisons = TRUE)

graph.numhd.emm.data.cld.df %>% arrange(desc(emmean))

ggplot(graph.numhd.emm.data.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Dataset,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip() +
  labs(title="Estimated Marginal Means for Dataset for Degree of\nHighest Degree Node task, graphics conditions")



#plot(ref_grid(graph.numnodes.lmer.int.3), by="Condition") 
# try to figure this out? maybe only works on the interaction?
```

```{r}

graph.numhd.emm.data.pairs <- dplyr::as_data_frame(pairs(graph.numhd.emm.data)) 
graph.numhd.emm.data.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(graph.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

pairs.CI <- confint(pairs(graph.numhd.emm.data))

graph.numhd.emm.data.pairs <- full_join(graph.numhd.emm.data.pairs, pairs.CI)

#graph.numhd.diffemm.condition <- emmeans(graph.numhd.lmer.full.int.4, pairwise ~ Condition)
#graph.numhd.diffemm.condition$contrasts
#contrast(graph.numhd.emm.condition)
#confint(graph.numhd.emm.condition)
#pairs(graph.numhd.emm.condition, details=TRUE)
#confint(contrast(graph.numhd.emm.condition))
#confint(pairs(graph.numhd.emm.condition))
#coef(pairs(graph.numhd.emm.condition))


plot(pairs(graph.numhd.emm.data))
plot(pairs(graph.numhd.emm.data), comparisons = TRUE)

graph.numhd.emm.data.pairs$sig.levels <- 
  case_when(graph.numhd.emm.data.pairs$p.value < .0001 ~ sig.level.names[1],
            graph.numhd.emm.data.pairs$p.value < .001 ~ sig.level.names[2],
            graph.numhd.emm.data.pairs$p.value < .01 ~ sig.level.names[3],
            graph.numhd.emm.data.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

graph.numhd.emm.data.pairs$sig.levels <- factor(graph.numhd.emm.data.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)


graph.numhd.emm.data.pairs$contrast <- factor(graph.numhd.emm.data.pairs$contrast, levels=graph.numhd.emm.data.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

graph.numhd.emm.data.pairs <- graph.numhd.emm.data.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

graph.numhd.emm.data.pairs %>% arrange(estimate)

ggplot(graph.numhd.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(graph.numhd.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

data.copy <- graph.numhd.emm.data.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

graph.numhd.emm.data.pairs.compl <- bind_rows(graph.numhd.emm.data.pairs, data.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#graph.numlinks.emm.data.pairs.compl$From <- factor(graph.numlinks.emm.data.pairs.compl$From, levels=cond.lev)
#graph.numlinks.emm.data.pairs.compl$To <- factor(graph.numlinks.emm.data.pairs.compl$To, levels=cond.lev)

graph.numhd.emm.data.pairs.compl$From <- factor(graph.numhd.emm.data.pairs.compl$From, levels=rev(unique(graph.numhd.emm.data.pairs.compl$From)))

#graph.numhd.emm.data.pairs.compl %>% arrange(desc(estimate))
graph.numhd.emm.data.pairs.compl %>% arrange(estimate)

ggplot(graph.numhd.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
    scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(graph.numhd.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")


```

###### networks

```{r, eval=FALSE}

# try a network of the pairwise significance values?  bleh...
# using igraph

graph <- graph_from_data_frame(graph.numhd.emm.data.pairs %>% dplyr::select(-contrast), directed=TRUE)

E(graph)$width <- abs(E(graph)$estimate)*50
E(graph)$edge.color <- sig.colors[E(graph)$sig.levels]

graph

plot(graph, 
     edge.arrow.size=.5,
     vertex.frame.color="#555555")

```

```{r}

# using ggraph and tidygraph

graph <- graph_from_data_frame(graph.numhd.emm.data.pairs %>% dplyr::select(-contrast), directed=TRUE)

# plot using ggraph
ggraph(graph, layout = 'kk') +
  geom_edge_link(aes(start_cap = label_rect(node1.name),
                       end_cap = label_rect(node2.name),
                     color=factor(sig.level.names[sig.levels]),
                     edge_width=.5/sig.levels
                     ), 
                   arrow = arrow(length = unit(4, 'mm')))+
  geom_node_text(label = vertex_attr(graph,"name")) +
  scale_edge_color_manual("Significance Levels", values=sig.colors) +
  scale_edge_width_continuous(labels=rev(sig.level.names)) +
  theme_graph()

```

##### Condition:Dataset

###### emmeans

```{r}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(graph.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(graphics_numnodes, table(Dataset,Underestimated))
# ref_grid(graph.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#graph.numnodes.emm.cond <- emmeans(graph.numnodes.lmer.int.3, "Condition", nesting = NULL)
graph.numhd.emm.conddata <- emmeans(graph.numhd.lmer.full.int.6, ~ Dataset | Condition, nesting = NULL)
graph.numhd.emm.conddata.2 <- emmeans(graph.numhd.lmer.full.int.6, ~ Condition | Dataset, nesting = NULL)

graph.numhd.emm.conddata

#graph.numnodes.diffemm.conddata <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#graph.numnodes.diffemm.conddata

graph.numhd.emm.conddata.df <- dplyr::as_data_frame(graph.numhd.emm.conddata)

graph.numhd.emm.conddata.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the graph

#xtable::xtable(graph.numhd.emm.condition)

graph.numhd.emm.conddata.cld <- cld(graph.numhd.emm.conddata,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

graph.numhd.emm.conddata.cld[["emmeans"]]


graph.numhd.emm.conddata.cld.df <- graph.numhd.emm.conddata.cld[["emmeans"]]

graph.numhd.emm.conddata.cld.df %>% dplyr::select(Dataset,Condition,.group) %>% print()

cld(graph.numhd.emm.conddata.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(Dataset,Condition,.group) %>% print()

# TO DO : get this to print as single table

#graph.numnodes.emm.conddata.cld.df$Condition <- factor(graph.numnodes.emm.conddata.cld.df$Condition, levels=graph.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(graph.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(graph.numhd.emm.conddata, ~Condition|Dataset, CIs = TRUE)
plot(graph.numhd.emm.conddata)
#plot(graph.numnodes.emm.conddata, comparisons = TRUE)

graph.numhd.emm.conddata.cld.df %>% arrange(desc(emmean))

ggplot(graph.numhd.emm.conddata.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=Condition,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Dataset) + 
  coord_flip()

ggplot(graph.numhd.emm.conddata.cld.df) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL, color=Condition), width=.2, position=position_dodge(width=0.2)) +
  geom_point(aes(x=Dataset,y=emmean, color=Condition), position=position_dodge(width=0.2)) +
  geom_line(aes(x=Dataset,y=emmean, color=Condition, group=Condition), position=position_dodge(width=0.2)) +
  #scale_color_manual(labels=c("Blue","Black"),values=c("steelblue","black"), name="Node Color") +
  scale_color_discrete(labels=c("Control","Color","Phrasing","Size")) +
  labs(title="Estimated Marginal Means for Condition vs. Dataset for\nDegree of Highest Degree Node task, graphics conditions")

```

```{r}

graph.numhd.emm.conddata.pairs <- dplyr::as_data_frame(pairs(graph.numhd.emm.conddata)) 
graph.numhd.emm.conddata.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(graph.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

conddata.pairs.CI <- confint(pairs(graph.numhd.emm.conddata))

graph.numhd.emm.conddata.pairs <- full_join(graph.numhd.emm.conddata.pairs, conddata.pairs.CI)

#graph.numnodes.diffemm.cond <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Condition)
#graph.numnodes.diffemm.cond$contrasts
#contrast(graph.numnodes.emm.cond)
#confint(graph.numnodes.emm.cond)
#pairs(graph.numnodes.emm.cond, details=TRUE)
#confint(contrast(graph.numnodes.emm.cond))
#confint(pairs(graph.numnodes.emm.cond))
#coef(pairs(graph.numnodes.emm.cond))

plot(pairs(graph.numhd.emm.conddata))
plot(pairs(graph.numhd.emm.conddata), comparisons = TRUE)

graph.numhd.emm.conddata.pairs$sig.levels <- 
  case_when(graph.numhd.emm.conddata.pairs$p.value < .0001 ~ sig.level.names[1],
            graph.numhd.emm.conddata.pairs$p.value < .001 ~ sig.level.names[2],
            graph.numhd.emm.conddata.pairs$p.value < .01 ~ sig.level.names[3],
            graph.numhd.emm.conddata.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

graph.numhd.emm.conddata.pairs$sig.levels <- factor(graph.numhd.emm.conddata.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

graph.numhd.emm.conddata.pairs$contrast.cond <- paste0(graph.numhd.emm.conddata.pairs$contrast,graph.numhd.emm.conddata.pairs$Condition)

graph.numhd.emm.conddata.pairs$contrast.cond <- factor(graph.numhd.emm.conddata.pairs$contrast.cond, levels=graph.numhd.emm.conddata.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.cond) %>% distinct() %>% unlist())

#graph.numhd.emm.conddata.pairs %>% View()

graph.numhd.emm.conddata.pairs$contrast <- 
  factor(as.character(graph.numhd.emm.conddata.pairs$contrast), 
         levels=graph.numhd.emm.conddata.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


graph.numhd.emm.conddata.pairs <- graph.numhd.emm.conddata.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

graph.numhd.emm.conddata.pairs %>% arrange(estimate)
#graph.numlinks.emm.conddata.pairs %>% View()

ggplot(graph.numhd.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast.cond,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast.cond,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()


ggplot(graph.numhd.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

```

```{r}

conddata.copy <- graph.numhd.emm.conddata.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

graph.numhd.emm.conddata.pairs.compl <- bind_rows(graph.numhd.emm.conddata.pairs, conddata.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#graph.numnodes.emm.conddata.pairs.compl$From <- factor(graph.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#graph.numnodes.emm.conddata.pairs.compl$To <- factor(graph.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

graph.numhd.emm.conddata.pairs.compl$From <- factor(graph.numhd.emm.conddata.pairs.compl$From, levels=c(9,8,7,5,3,1))


#graph.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
graph.numhd.emm.conddata.pairs.compl %>% arrange(estimate)

ggplot(graph.numhd.emm.conddata.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(graph.numhd.emm.conddata.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(graph.numhd.emm.conddata.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(graph.numhd.emm.conddata.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)


```

##### Dataset:Overestimated

###### emmeans


```{r}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(graph.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(graphics_numnodes, table(Dataset,Underestimated))
# ref_grid(graph.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#graph.numnodes.emm.cond <- emmeans(graph.numnodes.lmer.int.3, "Condition", nesting = NULL)
graph.numhd.emm.dataover <- emmeans(graph.numhd.lmer.full.int.6, ~ Dataset | Overestimated, nesting = NULL)
graph.numhd.emm.dataover.2 <- emmeans(graph.numhd.lmer.full.int.6, ~ Overestimated | Dataset, nesting = NULL)

graph.numhd.emm.dataover

#graph.numnodes.diffemm.conddata <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#graph.numnodes.diffemm.conddata

graph.numhd.emm.dataover.df <- dplyr::as_data_frame(graph.numhd.emm.dataover)

graph.numhd.emm.dataover.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the graph

#xtable::xtable(graph.numhd.emm.condition)

graph.numhd.emm.dataover.cld <- cld(graph.numhd.emm.dataover,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

graph.numhd.emm.dataover.cld[["emmeans"]]


graph.numhd.emm.dataover.cld.df <- graph.numhd.emm.dataover.cld[["emmeans"]]

graph.numhd.emm.dataover.cld.df %>% dplyr::select(Dataset,Overestimated,.group) %>% print()
cld(graph.numhd.emm.dataover.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(Dataset,Overestimated,.group) %>% print()

# TO DO : get this to print as single table

#graph.numnodes.emm.conddata.cld.df$Condition <- factor(graph.numnodes.emm.conddata.cld.df$Condition, levels=graph.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(graph.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(graph.numhd.emm.dataover, ~Dataset|Overestimated, CIs = TRUE)
plot(graph.numhd.emm.dataover)
#plot(graph.numnodes.emm.conddata, comparisons = TRUE)

graph.numhd.emm.dataover.cld.df %>% arrange(desc(emmean))

ggplot(graph.numhd.emm.dataover.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=Dataset,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated) + 
  coord_flip()

ggplot(graph.numhd.emm.dataover.cld.df) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL, color=Overestimated), width=.2, position=position_dodge(width=0.2)) +
  geom_point(aes(x=Dataset,y=emmean, color=Overestimated), position=position_dodge(width=0.2)) +
  geom_line(aes(x=Dataset,y=emmean, color=Overestimated, group=Overestimated), position=position_dodge(width=0.2)) +
  #scale_color_manual(labels=c("Blue","Black"),values=c("steelblue","black"), name="Node Color") +
  scale_color_discrete(labels=c("Overestimated","Correct or\nUnderestimated")) +
  labs(title="Estimated Marginal Means for Dataset vs. Overestimated for\nDegree of Highest Degree Node task, graphics conditions")



```

```{r}

graph.numhd.emm.dataover.pairs <- dplyr::as_data_frame(pairs(graph.numhd.emm.dataover)) 
graph.numhd.emm.dataover.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(graph.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

dataover.pairs.CI <- confint(pairs(graph.numhd.emm.dataover))

graph.numhd.emm.dataover.pairs <- full_join(graph.numhd.emm.dataover.pairs, dataover.pairs.CI)

#graph.numnodes.diffemm.cond <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Condition)
#graph.numnodes.diffemm.cond$contrasts
#contrast(graph.numnodes.emm.cond)
#confint(graph.numnodes.emm.cond)
#pairs(graph.numnodes.emm.cond, details=TRUE)
#confint(contrast(graph.numnodes.emm.cond))
#confint(pairs(graph.numnodes.emm.cond))
#coef(pairs(graph.numnodes.emm.cond))

plot(pairs(graph.numhd.emm.dataover))
plot(pairs(graph.numhd.emm.dataover), comparisons = TRUE)

graph.numhd.emm.dataover.pairs$sig.levels <- 
  case_when(graph.numhd.emm.dataover.pairs$p.value < .0001 ~ sig.level.names[1],
            graph.numhd.emm.dataover.pairs$p.value < .001 ~ sig.level.names[2],
            graph.numhd.emm.dataover.pairs$p.value < .01 ~ sig.level.names[3],
            graph.numhd.emm.dataover.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

graph.numhd.emm.dataover.pairs$sig.levels <- factor(graph.numhd.emm.dataover.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

graph.numhd.emm.dataover.pairs$contrast.all <- paste0(graph.numhd.emm.dataover.pairs$contrast,graph.numhd.emm.dataover.pairs$Overestimated)

graph.numhd.emm.dataover.pairs$contrast.all <- factor(graph.numhd.emm.dataover.pairs$contrast.all, levels=graph.numhd.emm.dataover.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.all) %>% distinct() %>% unlist())

#graph.numhd.emm.conddata.pairs %>% View()

graph.numhd.emm.dataover.pairs$contrast <- 
  factor(as.character(graph.numhd.emm.dataover.pairs$contrast), 
         levels=graph.numhd.emm.dataover.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


graph.numhd.emm.dataover.pairs <- graph.numhd.emm.dataover.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

graph.numhd.emm.dataover.pairs %>% arrange(estimate)
#graph.numlinks.emm.conddata.pairs %>% View()

ggplot(graph.numhd.emm.dataover.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.dataover.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()


ggplot(graph.numhd.emm.dataover.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.dataover.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

```

```{r}

dataover.copy <- graph.numhd.emm.dataover.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

graph.numhd.emm.dataover.pairs.compl <- bind_rows(graph.numhd.emm.dataover.pairs, dataover.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#graph.numnodes.emm.conddata.pairs.compl$From <- factor(graph.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#graph.numnodes.emm.conddata.pairs.compl$To <- factor(graph.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

graph.numhd.emm.dataover.pairs.compl$From <- factor(graph.numhd.emm.dataover.pairs.compl$From, levels=c(9,8,7,5,3,1))


#graph.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
graph.numhd.emm.dataover.pairs.compl %>% arrange(estimate)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)


```


##### DatasetOrder:Overestimated

TO DO : add factor to DatasetOrder at beginning

###### emmeans

```{r}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(graph.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(graphics_numnodes, table(Dataset,Underestimated))
# ref_grid(graph.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#graph.numnodes.emm.cond <- emmeans(graph.numnodes.lmer.int.3, "Condition", nesting = NULL)
graph.numhd.emm.dorderover <- emmeans(graph.numhd.lmer.full.int.6, ~ DatasetOrder | Overestimated, nesting = NULL)
graph.numhd.emm.dorderover.2 <- emmeans(graph.numhd.lmer.full.int.6, ~ Overestimated | DatasetOrder, nesting = NULL)

graph.numhd.emm.dorderover

#graph.numnodes.diffemm.conddata <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#graph.numnodes.diffemm.conddata

graph.numhd.emm.dorderover.df <- dplyr::as_data_frame(graph.numhd.emm.dorderover)

graph.numhd.emm.dorderover.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the graph

#xtable::xtable(graph.numhd.emm.condition)

graph.numhd.emm.dorderover.cld <- cld(graph.numhd.emm.dorderover,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

graph.numhd.emm.dorderover.cld[["emmeans"]]


graph.numhd.emm.dorderover.cld.df <- graph.numhd.emm.dorderover.cld[["emmeans"]]

graph.numhd.emm.dorderover.cld.df %>% dplyr::select(DatasetOrder,Overestimated,.group) %>% print()
cld(graph.numhd.emm.dorderover.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(DatasetOrder,Overestimated,.group) %>% print()


# TO DO : get this to print as single table

#graph.numnodes.emm.conddata.cld.df$Condition <- factor(graph.numnodes.emm.conddata.cld.df$Condition, levels=graph.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(graph.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(graph.numhd.emm.dorderover, ~DatasetOrder|Overestimated, CIs = TRUE)
plot(graph.numhd.emm.dorderover)
#plot(graph.numnodes.emm.conddata, comparisons = TRUE)

graph.numhd.emm.dorderover.cld.df %>% arrange(desc(emmean))

ggplot(graph.numhd.emm.dorderover.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=DatasetOrder,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=DatasetOrder,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated) + 
  coord_flip()

ggplot(graph.numhd.emm.dorderover.cld.df) +
  geom_errorbar(aes(x=DatasetOrder,ymax=upper.CL,ymin=lower.CL, color=Overestimated), width=.2, position=position_dodge(width=0.2)) +
  geom_point(aes(x=DatasetOrder,y=emmean, color=Overestimated), position=position_dodge(width=0.2)) +
  geom_line(aes(x=DatasetOrder,y=emmean, color=Overestimated, group=Overestimated), position=position_dodge(width=0.2)) +
  #scale_color_manual(labels=c("Blue","Black"),values=c("steelblue","black"), name="Node Color") +
  scale_color_discrete(labels=c("Overestimated","Correct or\nUnderestimated")) +
  labs(title="Estimated Marginal Means for Dataset Order vs. Overestimated for\nDegree of Highest Degree Node task, graphics conditions", x="Dataset Order")


```

```{r, eval=FALSE}

graph.numhd.emm.dorderover.pairs <- dplyr::as_data_frame(pairs(graph.numhd.emm.dorderover)) 
graph.numhd.emm.dorderover.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(graph.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

dorderover.pairs.CI <- confint(pairs(graph.numhd.emm.dorderover))

graph.numhd.emm.dorderover.pairs <- full_join(graph.numhd.emm.dorderover.pairs, dorderover.pairs.CI)

#graph.numnodes.diffemm.cond <- emmeans(graph.numnodes.lmer.int.3, pairwise ~ Condition)
#graph.numnodes.diffemm.cond$contrasts
#contrast(graph.numnodes.emm.cond)
#confint(graph.numnodes.emm.cond)
#pairs(graph.numnodes.emm.cond, details=TRUE)
#confint(contrast(graph.numnodes.emm.cond))
#confint(pairs(graph.numnodes.emm.cond))
#coef(pairs(graph.numnodes.emm.cond))

plot(pairs(graph.numhd.emm.dorderover))
plot(pairs(graph.numhd.emm.dorderover), comparisons = TRUE)

graph.numhd.emm.dorderover.pairs$sig.levels <- 
  case_when(graph.numhd.emm.dorderover.pairs$p.value < .0001 ~ sig.level.names[1],
            graph.numhd.emm.dorderover.pairs$p.value < .001 ~ sig.level.names[2],
            graph.numhd.emm.dorderover.pairs$p.value < .01 ~ sig.level.names[3],
            graph.numhd.emm.dorderover.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

graph.numhd.emm.dorderover.pairs$sig.levels <- factor(graph.numhd.emm.dorderover.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

graph.numhd.emm.dorderover.pairs$contrast.all <- paste0(graph.numhd.emm.dorderover.pairs$contrast,graph.numhd.emm.dorderover.pairs$Overestimated)

graph.numhd.emm.dorderover.pairs$contrast.all <- factor(graph.numhd.emm.dorderover.pairs$contrast.all, levels=graph.numhd.emm.dorderover.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.all) %>% distinct() %>% unlist())

#graph.numhd.emm.conddata.pairs %>% View()

graph.numhd.emm.dorderover.pairs$contrast <- 
  factor(as.character(graph.numhd.emm.dorderover.pairs$contrast), 
         levels=graph.numhd.emm.dorderover.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


graph.numhd.emm.dorderover.pairs <- graph.numhd.emm.dorderover.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

graph.numhd.emm.dorderover.pairs %>% arrange(estimate)
#graph.numlinks.emm.conddata.pairs %>% View()

ggplot(graph.numhd.emm.dorderover.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.dorderover.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()


ggplot(graph.numhd.emm.dorderover.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

ggplot(graph.numhd.emm.dorderover.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Overestimated, scales="free_y") +
  coord_flip()

```

```{r, eval=FALSE}

dataover.copy <- graph.numhd.emm.dataover.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

graph.numhd.emm.dataover.pairs.compl <- bind_rows(graph.numhd.emm.dataover.pairs, dataover.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#graph.numnodes.emm.conddata.pairs.compl$From <- factor(graph.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#graph.numnodes.emm.conddata.pairs.compl$To <- factor(graph.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

graph.numhd.emm.dataover.pairs.compl$From <- factor(graph.numhd.emm.dataover.pairs.compl$From, levels=c(9,8,7,5,3,1))


#graph.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
graph.numhd.emm.dataover.pairs.compl %>% arrange(estimate)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)

ggplot(graph.numhd.emm.dataover.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Overestimated)


```


