---
title: "Analysis for Percentage of Nodes in Largest Cluster task, Layout conditions"
author: "Angela Zoss"
date: "March 25, 2018"
output: github_document
---

```{r layout-setup-lgclust}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r layout-load-environment-lgclust, message=FALSE}

source('LayoutSetup.R')

```

#### Beta regression for percentage


See also: http://rcompanion.org/handbook/J_02.html

```{r, eval=FALSE}


#layouts_lgclust.2 <- layouts_lgclust %>% mutate(ResponsePct = (Response-.001)/100)
layouts_lgclust.2 <- layouts_lgclust %>% mutate(ResponseInfl = Response/100,
                                                  ResponsePct = (Response+0.00000001)/100.01)
# should give a min of .00001 and a max of .99999
```


```{r}

temp.lgclust.nodemo <- layouts_lgclust %>% 
  mutate(ResponsePct = Response/100, 
         StatsNumPixels=scale(StatsNumPixels)) %>%
  dplyr::select(-Demo.educ_TEXT,-starts_with("Demo"),-Attempt,-NodeRank,-MaxNodeRank,-Stats.CompensationCondition, -ClustConf,Demo.ResponseID) %>%
  drop_na()

```

##### brms/tidybayes

```{r, eval=FALSE}

#library(rstan)

theme_set(theme_grey())

#fit <- brm(ResponseInfl~Dataset, data = layouts_lgclust.2, family = zero_one_inflated_beta())
#fit <- brm(bf(ResponseInfl ~ Dataset + UnderestDummy + Demo.gender + 
#    Demo.lang + Demo.expreadnetvis + Stats.OperatingSystemWindows + 
#    Dataset:UnderestDummy + Demo.gender:Stats.OperatingSystemWindows + 
#    UnderestDummy:Demo.gender + UnderestDummy:Stats.OperatingSystemWindows, 
#    sigma ~ Dataset + UnderestDummy), data = layouts_lgclust.2, family = zero_one_inflated_beta())

#compose_data(layouts_lgclust.2)

# THIS WAS RUN
#fit <- brm(bf(ResponseInfl ~ Dataset + UnderestDummy + Demo.gender + 
#    Demo.lang + Demo.expreadnetvis + Stats.OperatingSystemWindows + 
#    Dataset:UnderestDummy + Demo.gender:Stats.OperatingSystemWindows + 
#    UnderestDummy:Demo.gender + UnderestDummy:Stats.OperatingSystemWindows), 
#    data = layouts_lgclust.2, family = zero_one_inflated_beta())

#fit2 <- update(fit, formula = . ~ . + (1 | Demo.ResponseID), newdata=layouts_lgclust.2)

LOO(fit, fit2)

# fit2 has lower LOOIC (1646.85 < 1620.62), which is good

fit2$formula

#fixed_form <- brms:::extract_effects(fit$formula)$fixed
#mm <- brms:::get_model_matrix(fixed_form, data = fit$data) 

coef(fit2)
fixef(fit2)
fixef(fit2, robust=TRUE)
fitted(fit2)
tidy(fit2)


fit2 %<>% recover_types(layouts_lgclust.2)

#print(fit2, pars = c("b_Intercept"))

#str(extract(fit2))

summary(fit2, waic = TRUE) 

```

```{r, eval=FALSE}

#plot(fit, ask=FALSE) 
#plot(marginal_effects(fit, probs = c(0.05, 0.95)),points=TRUE, ask=FALSE)
#plot(marginal_effects(fit, probs = c(0.05, 0.95)),ask=FALSE)
plot(marginal_effects(fit, effects="Dataset", probs = c(0.05, 0.95)),ask=FALSE)

```

```{r, eval=FALSE}
#fit.df <- tidy(fit2)

# diff between each dataset and dataset 1
hyp.vs.1 <- c("Dataset.L = 0", 
         "Dataset.Q = 0",
         "Dataset.C = 0",
         "DatasetE4 = 0",
         "DatasetE5 = 0")

hyp.vs.1.res <- hypothesis(fit2, hyp.vs.1)

# 1 = Intercept
# 3 = Dataset.L + Intercept
# 5 = Dataset.Q + Intercept
# 7 = Dataset.C + Intercept
# 8 = DatasetE4 + Intercept
# 9 = DatasetE5 + Intercept

# diff between each dataset and dataset 3
hyp.vs.3 <- c("Dataset.Q > Dataset.L", # 5 vs. 3
         "Dataset.C > Dataset.L",
         "DatasetE4 > Dataset.L",
         "DatasetE5 > Dataset.L")

hyp.vs.3.res <- hypothesis(fit2, hyp.vs.3)

# diff between each dataset and dataset 5
hyp.vs.5 <- c("Dataset.C > Dataset.Q", # 7 vs. 5
         "DatasetE4 > Dataset.Q",
         "DatasetE5 > Dataset.Q")

hyp.vs.5.res <- hypothesis(fit2, hyp.vs.5)

# diff between each dataset and dataset 7
hyp.vs.7 <- c("DatasetE4 > Dataset.C", # 8 vs. 7
         "DatasetE5 > Dataset.C")

hyp.vs.7.res <- hypothesis(fit2, hyp.vs.7)

# diff between each dataset and dataset 8
hyp.vs.8 <- c("DatasetE5 > DatasetE4" # 9 vs. 8
         )

hyp.vs.8.res <- hypothesis(fit2, hyp.vs.8)

# sequential differences
hyp.seq <- c("Dataset.L = 0",
             "Dataset.L + Dataset.Q > Dataset.L",
             "Dataset.Q + Dataset.C > Dataset.Q",
             "Dataset.C + DatasetE4 > Dataset.C",
             "DatasetE4 + DatasetE5 > DatasetE4")

(hyp.seq.res <- hypothesis(fit2, hyp.seq))

```

```{r, eval=FALSE}

# all pairs

hyp.pairs <- c("Dataset.L = 0", # 3 vs. 1
         "Dataset.Q = 0",
         "Dataset.C = 0",
         "DatasetE4 = 0",
         "DatasetE5 = 0",
         "Dataset.Q > Dataset.L", # 5 vs. 3
         "Dataset.C > Dataset.L",
         "DatasetE4 > Dataset.L",
         "DatasetE5 > Dataset.L",
         "Dataset.C > Dataset.Q", # 7 vs. 5
         "DatasetE4 > Dataset.Q",
         "DatasetE5 > Dataset.Q",
         "DatasetE4 > Dataset.C", # 8 vs. 7
         "DatasetE5 > Dataset.C",
         "DatasetE5 > DatasetE4")

# above syntax converts to Dataset.Q - Dataset.L > 0, which then calculates evidence ratio, which often makes upper CI infinite; correct syntax is Dataset.Q - Dataset.L = 0

hyp.pairs.2 <- c("Dataset.L = 0", # 3 vs. 1
         "Dataset.Q = 0",
         "Dataset.C = 0",
         "DatasetE4 = 0",
         "DatasetE5 = 0",
         "Dataset.Q - Dataset.L = 0", # 5 vs. 3
         "Dataset.C - Dataset.L = 0",
         "DatasetE4 - Dataset.L = 0",
         "DatasetE5 - Dataset.L = 0",
         "Dataset.C - Dataset.Q = 0", # 7 vs. 5
         "DatasetE4 - Dataset.Q = 0",
         "DatasetE5 - Dataset.Q = 0",
         "DatasetE4 - Dataset.C = 0", # 8 vs. 7
         "DatasetE5 - Dataset.C = 0",
         "DatasetE5 - DatasetE4 = 0")


(hyp.pairs.2.res <- hypothesis(fit2, hyp.pairs.2))

#plot(hyp.pairs.2.res, chars = NULL, ask=FALSE)

hyp.pairs.2.res.df <- hyp.pairs.2.res$hypothesis

hyp.pairs.2.res.df$contrast <- c("3-1","5-1","7-1","8-1","9-1","5-3","7-3","8-3","9-3","7-5","8-5","9-5","8-7","9-7","9-8")

hyp.pairs.2.res.df$contrast <- factor(hyp.pairs.2.res.df$contrast,
                                    levels=hyp.pairs.2.res.df %>% arrange(desc(Estimate)) %>%
                                      dplyr::select(contrast) %>% unlist())

ggplot(hyp.pairs.2.res.df, aes(contrast,Estimate)) + 
  geom_errorbar(aes(ymin=`l-95% CI`,ymax=`u-95% CI`)) +
  geom_point(aes(fill=Star=="*"), size=7, shape=21) +
  geom_hline(yintercept = 0) +
  scale_fill_manual(values=star.colors,name="Outside 95% CI") +
  coord_flip()

```

```{r, eval=FALSE}

hyp.pairs.2.res.df <- hyp.pairs.2.res.df %>% separate(contrast, c("From", "To"), sep="[-]", remove=FALSE)

copy <- hyp.pairs.2.res.df %>% rename(From=To,To=From) %>% 
  mutate(Estimate=-Estimate,
         `l-95% CI`=-`l-95% CI`,
         `u-95% CI`=-`u-95% CI`)

pairs.compl <- bind_rows(hyp.pairs.2.res.df, copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#layout.numnodes.emm.conddata.pairs.compl$From <- factor(layout.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#layout.numnodes.emm.conddata.pairs.compl$To <- factor(layout.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

pairs.compl$From <- factor(pairs.compl$From, levels=c(9,8,7,5,3,1))
pairs.compl$To <- factor(pairs.compl$To, levels=c(1,3,5,7,8,9))

#layout.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
pairs.compl %>% arrange(Estimate)

# can't get color to go the right direction
ggplot(pairs.compl %>% filter(Estimate >= 0)) +
  geom_tile(aes(x=To,y=From,fill=Estimate), color="black") +
  scale_fill_distiller(palette="Greys", direction=1) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(Estimate),fill=Star=="*"),shape=21, color="black") +
  scale_fill_manual(values=star.colors, name="Outside 95% CI") +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=Estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(Estimate),fill=Estimate, color=Star=="*"), shape=21,stroke=1) +
  scale_fill_distiller(type="div", palette=4, limits=c(-max(abs(pairs.compl$Estimate)),max(abs(pairs.compl$Estimate)))) +
  scale_color_manual(values=c("grey90","black"), name="Outside 95% CI") +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

hyp.pairs.2.res.df$From <- factor(hyp.pairs.2.res.df$From, levels=c(9,8,7,5,3,1))
hyp.pairs.2.res.df$To <- factor(hyp.pairs.2.res.df$To, levels=c(1,3,5,7,8,9))


ggplot(hyp.pairs.2.res.df) +
  geom_count(aes(x=To,y=From,size=abs(Estimate),fill=Estimate, color=Star=="*"), shape=21,stroke=1) +
  scale_fill_distiller(type="div", palette=4, limits=c(-max(abs(pairs.compl$Estimate)),max(abs(pairs.compl$Estimate)))) +
  scale_color_manual(values=c("grey90","black"), name="Outside 95% CI") +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")




```


##### mgcv

```{r, eval=FALSE}

#mgcv

library(mgcv)

layout.lgclust.beta.data <- gam(ResponsePct~Dataset,family=mgcv::betar(),data=layouts_lgclust.2)
layout.lgclust.beta.data.infl <- gam(ResponseInfl~Dataset,family=mgcv::betar(),data=layouts_lgclust.2)

gam.check(layout.lgclust.beta.data.infl)

bGAM <- coef(layout.lgclust.beta.data.infl)[2:6]
seGAM <- diag(vcov(layout.lgclust.beta.data.infl))[2:6]

    df <- data.frame(term     = nms <- names(bGAM),
                     estimate = bGAM)
    df <- transform(df,
                    upper = estimate + sqrt(seGAM),
                    lower = estimate - sqrt(seGAM))
    df
    
    p1 <- ggplot(df, aes(y = estimate, x = term, ymax = upper, ymin = lower)) +
    geom_pointrange() +
    labs(y = NULL,
         x = "Regression estimate",
         caption = "Bars are ±1 SE")

p1


```

##### glmmTMB

```{r, eval=FALSE}

#package glmmTMB:

(layout.lgclust.beta.cond <- glmmTMB(ResponsePct ~ Condition + (1|Demo.ResponseID), layouts_lgclust.2, family=list(family="beta",link="logit")))

summary(layout.lgclust.beta.cond) # no pseudo R^2, unlike betareg

#(layout.lgclust.beta.cond.ZI <- glmmTMB(Response ~ Condition + (1|Demo.ResponseID), layouts_lgclust.2, family=list(family="beta",link="logit"),ziformula =~1))
#Error in nlminb(start = par, objective = fn, gradient = gr, control = control$optCtrl) : gradient function must return a numeric vector of length 7

#ranef(layout.lgclust.beta.cond)

#fixef(layout.lgclust.beta.cond)

#confint(layout.lgclust.beta.cond)

#getME(layout.lgclust.beta.cond, name=c("X"))

hist(residuals(layout.lgclust.beta.cond))

lrtest(layout.lgclust.beta.cond)

```

##### betareg

```{r, eval=FALSE}


# betareg package

layout.lgclust.beta.cond <- betareg(ResponsePct~Condition, data=layouts_lgclust.2, type="ML") 
# specify random effects?
# no zero inflation?

summary(layout.lgclust.beta.cond)

lrtest(layout.lgclust.beta.cond)

# from car library

Anova(layout.lgclust.beta.cond, type="II")

```

##### broom

```{r, cache=TRUE, eval=FALSE}

# depends on gamlss, later

mod7$call

mod7.tidy.df <- tidy(mod7)
mod7.tidy.df.mu <- mod7.tidy.df %>% filter(parameter == "mu")

mod7.ci.df <- confint_tidy(mod7)
mod7.ci.df.nona <- mod7.ci.df %>% drop_na()

mod7.tidyci.df <- bind_cols(mod7.tidy.df.mu, mod7.ci.df.nona)

mod7.aug.df <- augment(mod7,temp) # augment isn't supposed to work but seems to
#mod7.summ.df <- glance(mod7) #glance doesn't work

mod7.tidyci.df$term <- factor(mod7.tidyci.df$term,
                                          levels=mod7.tidyci.df %>% arrange(estimate) %>%
                                            dplyr::select(term) %>% unlist())

ggplot(mod7.aug.df) + geom_point(aes(ResponsePct,.fitted))

#ggplot(mod7.tidyci.df, aes(term, estimate)) + 
#  geom_point() + 
#  coord_flip()

#ggplot(mod7.aug.df %>% group_by(Dataset) %>% summarize(est=mean(.fitted))) +
#  geom_point(aes(Dataset,est)) +
#  #scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
#  coord_flip()

#plot(emmeans(layout.clickhd.nb.full, "Dataset"))

#ggplot(mod7.aug.df) +
#  geom_violin(aes(Dataset,.fitted)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% summarize(est=median(ResponsePct)),aes(Dataset,est)) +
#  #scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
#  coord_flip()

# could be okay, but not sure of calculation
#ggplot(data = mod7.aug.df) + 
#  geom_errorbar(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(.fitted), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est, ymin=ymin, ymax=ymax, width=.2)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(.fitted), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est))

# no good
#ggplot(data = mod7.aug.df) + 
#  geom_errorbar(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(ResponsePct), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est, ymin=ymin, ymax=ymax, width=.2)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(ResponsePct), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est))
  

```

```{r, eval=FALSE}



set.seed(2014)

# doesn't work
bootnls <- mod7.aug.df %>% bootstrap(100) %>% do(tidy(
      gamlss(formula = ResponsePct ~ Dataset + UnderestDummy + Demo.gender + 
    Demo.lang + Demo.expreadnetvis + Stats.OperatingSystemWindows + 
    Dataset:UnderestDummy + Demo.gender:Stats.OperatingSystemWindows + 
    UnderestDummy:Demo.gender + UnderestDummy:Stats.OperatingSystemWindows, 
    sigma.formula = ~Dataset + UnderestDummy, family = BEINF, 
    ., trace = FALSE)
    ))
alpha = .05
bootnls %>% group_by(term) %>% summarize(low=quantile(estimate, alpha / 2),
                                         high=quantile(estimate, 1 - alpha / 2))
ggplot(bootnls, aes(estimate)) + geom_histogram(binwidth=2) + facet_wrap(~ term, scales="free")

bootnls_aug <- mtcars %>% bootstrap(100) %>%
    do(augment(nls(mpg ~ k / wt + b, ., start=list(k=1, b=0)), .))

ggplot(bootnls_aug, aes(wt, mpg)) + geom_point() +
    geom_line(aes(y=.fitted, group=replicate), alpha=.2)

smoothspline_aug <- mtcars %>% bootstrap(100) %>%
    do(augment(smooth.spline(.$wt, .$mpg, df=4), .))

ggplot(smoothspline_aug, aes(wt, mpg)) + geom_point() +
    geom_line(aes(y=.fitted, group=replicate), alpha=.2)

```


```{r, eval=FALSE}

layout.lgclust.broom.tidy <- tidy(mod7)
layout.lgclust.broom.aug <- augment(layout.lgclust.nb.full, temp)
layout.lgclust.broom.ci <- confint_tidy(layout.lgclust.nb.full)
layout.lgclust.broom.tidyci <- bind_cols(layout.lgclust.broom.tidy %>% arrange(group), layout.lgclust.broom.ci)

layout.clickhd.broom.tidyci$term <- factor(layout.clickhd.broom.tidyci$term,
                                          levels=layout.clickhd.broom.tidyci %>% arrange(estimate) %>%
                                            select(term) %>% unlist())

ggplot(layout.clickhd.broom.tidyci, aes(term, estimate)) + 
  geom_point() + 
  coord_flip()

ggplot(layout.clickhd.broom.aug %>% group_by(Dataset) %>% summarize(est=mean(.fitted))) +
  geom_point(aes(Dataset,est)) +
  scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
  coord_flip()

plot(emmeans(layout.clickhd.nb.full, "Dataset"))

ggplot(layout.clickhd.broom.aug) +
  geom_violin(aes(Dataset,.fitted)) +
  scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
  coord_flip()

```

##### gamlss

```{r, eval=FALSE}

# gamlss
# also from http://rcompanion.org/handbook/J_02.html
# https://stats.stackexchange.com/questions/48028/beta-regression-of-proportion-data-including-1-and-0
# http://www.de.ufpe.br/~raydonal/Talks/talk-10-12-2008.pdf
# https://stats.stackexchange.com/questions/253738/what-is-mu-in-zero-one-beta-inflated-models-gamlss-beinf
# http://www.de.ufpe.br/~raydonal/Talks/Gamlss-Theory.pdf
# http://www.de.ufpe.br/~raydonal/Talks/Gamlss-Applications.pdf
# https://www.researchgate.net/publication/228429663_Instructions_on_how_to_use_the_gamlss_package_in_R_Second_Edition

# For subsets use data=subset(mydata, subset_of_mydata),
# for na.action use data=na.omit(mydata)
# The function refit() can be used if the converged component of the gamlss fitted object is FALSE
# Warning: The random(), ra() and rc() additive functions do not have a predict option implemented.

#temp <- layouts_lgclust %>% mutate(Response=Response/100) %>% dplyr::select(Demo.ResponseID, Response, Condition, Dataset, DatasetOrder) %>% drop_na()

```

```{r, eval=FALSE}
#===== Fit model (all covariates) =====
mod.0 <- gamlss(ResponsePct~. + re(random=~1|Demo.ResponseID, opt = 'optim'), nu.formula=~., family=BEINF, data=temp.lgclust.nodemo)

#==== model selection for alpha using AIC ====
mod.1 <- stepGAIC(mod.0, what="nu")

#==== model selection for mu using AIC ====
mod.2 <- stepGAIC(mod.1)

#==== final fit model ====
fit <- gamlss(formula = ResponsePct ~ Dataset + (re(random = ~1 | Demo.ResponseID, opt = "optim")) , nu.formula = ~1, family = BEINF, data = temp.lgclust.nodemo, trace = FALSE)

summary(fit)
mean.fit <- meanBEINF(fit)

# https://stats.stackexchange.com/questions/309047/zero-inflated-beta-regression-using-gamlss-for-vegetation-cover-data

#means_m1 <- lpred(fit, type='response', what='mu', se.fit=T)
# can't do prediction with random effects?


```

```{r, eval=FALSE}
layout.lgclust.beta.cond <- gamlss(Response~Condition+random(factor(Demo.ResponseID)), data=temp, family=BEINF) 

layout.lgclust.beta.cond.2 <- gamlss(Response~Condition+re(random=~1|Demo.ResponseID, opt = 'optim'), data=temp, family=BEINF) 

layout.lgclust.beta.cond.3 <- gamlss(Response~re(fixed=~Condition, random=~1|Demo.ResponseID, opt = 'optim'), data=temp, family=BEINF) 


car::Anova(layout.lgclust.beta.cond.2)
# Error: $ operator is invalid for atomic vectors

AIC(layout.lgclust.beta.cond,layout.lgclust.beta.cond.2,layout.lgclust.beta.cond.3)

lrtest(layout.lgclust.beta.cond.2)

print(layout.lgclust.beta.cond.2)

summary(layout.lgclust.beta.cond.2)

#names(layout.lgclust.beta.cond.2)

#deviance(layout.lgclust.beta.cond.2, "G")
#deviance(layout.lgclust.beta.cond.2, "P")


#plot(fitted(layout.lgclust.beta.cond), fitted(layout.lgclust.beta.cond.2))

plot(fitted(layout.lgclust.beta.cond.2), residuals(layout.lgclust.beta.cond.2))

plot(layout.lgclust.beta.cond.2)

#term.plot(layout.lgclust.beta.cond.2)
wp(layout.lgclust.beta.cond.2)
wp(layout.lgclust.beta.cond.2,ylim.all=2)

#summary results
summary(layout.lgclust.beta.cond)
# fit values
mean.fit <- meanBEINF(layout.lgclust.beta.cond)
#meanBEINF(layout.lgclust.beta.cond)[1]

#source("ExtraBIc.R")
#source("residualsBIc.R")
# can't find these files

#==== residuals =====
#a <- residuals.BIc(layout.lgclust.beta.cond) #standardized residual
#b <- residuals.BIc(layout.lgclust.beta.cond, type="experimental") #weighted residual
#c <- residuals.BIc(layout.lgclust.beta.cond, type="quantil") #quantal residual

#==== normal probability plots ====
#envelope.BIc(layout.lgclust.beta.cond, main="standardized residual" )
#envelope.BIc(layout.lgclust.beta.cond, type="experimental", main="weighted residual" )
#envelope.BIc(layout.lgclust.beta.cond, type="quantil", main="quantal residual")


```

```{r, eval=FALSE}

# from https://pdfs.semanticscholar.org/ed3d/f96aa477d6454d5737403a5aab751ccd9315.pdf

#gamlss(Response~Condition+random(factor(Demo.ResponseID)), data=temp, family=BEINF) 
#gamlss(Response~Condition+re(random=~1|Demo.ResponseID, opt = 'optim'), data=temp, family=BEINF) 
#gamlss(Response~re(fixed=~Condition, random=~1|Demo.ResponseID, opt = 'optim'), data=temp, family=BEINF)

mod01.0 <- gamlss(ResponsePct ~ 1, data = temp.lgclust.nodemo, family = BEINF)
mod01.r <- gamlss(ResponsePct ~ 1 + random(factor(Demo.ResponseID)), data = temp.lgclust.nodemo, family = BEINF) # lowest deviance, highest AIC, highest df
mod01.r1 <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID), data = temp.lgclust.nodemo, family = BEINF)
mod01.r2 <- gamlss(ResponsePct ~ re(fixed=~1, random=~1|Demo.ResponseID), data = temp.lgclust.nodemo, family = BEINF)
mod01.r3 <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), data = temp.lgclust.nodemo, family = BEINF) # change in optimizer decreases df a small fraction, much faster 
mod01.r4 <- gamlss(ResponsePct ~ re(fixed=~1, random=~1|Demo.ResponseID, opt = 'optim'), data = temp.lgclust.nodemo, family = BEINF)
AIC(mod01.0,mod01.r,mod01.r1,mod01.r2,mod01.r3,mod01.r4) # keep .r3 syntax

mod01 <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), data = temp.lgclust.nodemo, family = BEINF)

mod02.0 <- gamlss(ResponsePct ~ Condition, data = temp, family = BEINF)
mod02.r <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), data = temp, family = BEINF)
mod02.0.s <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, data = temp, family = BEINF)
mod02.0.n <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), nu.fo = ~Condition, data = temp, family = BEINF)
mod02.0.t <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), tau.fo = ~Condition, data = temp, family = BEINF)
mod02.0.s.n <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, nu.fo = ~Condition, data = temp, family = BEINF)
mod02.0.s.t <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, tau.fo = ~Condition, data = temp, family = BEINF)
mod02.0.n.t <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), tau.fo = ~Condition, nu.fo = ~Condition, data = temp, family = BEINF)
mod02.0.s.n.t <- gamlss(ResponsePct ~ 1 + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, nu.fo = ~Condition, tau.fo = ~Condition, data = temp, family = BEINF)
mod02.r.s <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, data = temp, family = BEINF)
mod02.r.n <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), nu.fo = ~Condition, data = temp, family = BEINF)
mod02.r.t <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), tau.fo = ~Condition, data = temp, family = BEINF)
mod02.r.s.n <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, nu.fo = ~Condition, data = temp, family = BEINF)
mod02.r.s.t <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, tau.fo = ~Condition, data = temp, family = BEINF)
mod02.r.n.t <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), tau.fo = ~Condition, nu.fo = ~Condition, data = temp, family = BEINF)
mod02.r.s.n.t <- gamlss(ResponsePct ~ Condition + re(random=~1|Demo.ResponseID, opt = 'optim'), sigma.fo = ~Condition, nu.fo = ~Condition, tau.fo = ~Condition, data = temp, family = BEINF)

#summary(mod02.r.s.n.t)

AIC(mod01, mod02.0, mod02.r, mod02.0.s, mod02.0.n, mod02.0.t, mod02.0.s.n, mod02.0.s.t, mod02.0.n.t, mod02.0.s.n.t, mod02.r.s, mod02.r.n, mod02.r.t, mod02.r.s.n, mod02.r.s.t, mod02.r.n.t, mod02.r.s.n.t) 
# best is mod01

AIC(mod01, mod02.0, mod02.r, mod02.0.s, mod02.0.n, mod02.0.t, mod02.0.s.n, mod02.0.s.t, mod02.0.n.t, mod02.0.s.n.t, mod02.r.s, mod02.r.n, mod02.r.t, mod02.r.s.n, mod02.r.s.t, mod02.r.n.t, mod02.r.s.n.t, k=3.8) 
# best is mod01

AIC(mod01, mod02.0, mod02.r, mod02.0.s, mod02.0.n, mod02.0.t, mod02.0.s.n, mod02.0.s.t, mod02.0.n.t, mod02.0.s.n.t, mod02.r.s, mod02.r.n, mod02.r.t, mod02.r.s.n, mod02.r.s.t, mod02.r.n.t, mod02.r.s.n.t, k=7.96) 
# best is mod01

# adding condition does not improve model 

plot(mod01)
term.plot(mod01, se=T)

#op <- par(mfrow = c(4, 2))
#lev <- c(1, 2, 3, 4, 5, 6, 7)
#ind <- c(3, 2, 9, 12, 1, 7, 4)
#j <- 0
#for (i in ind) {
#  j = 1 + j
#  xlab <- paste("treatment = ", eval(substitute(lev[j])))
#  ylab <- paste("p(y)")
#  plotBEINF(mu = fitted(mod22)[i],
#  sigma = fitted(mod22, "sigma")[i],
#  nu = fitted(mod22, "nu")[i],
#  tau = fitted(mod22, "tau")[i],
#  from = 0, to = 1, n = 101, xlab = xlab, ylab = ylab)
#  }
#term.plot(mod22, se = T)
#par(op)

plotBEINF(mu=fitted(mod01)[1],
          sigma=fitted(mod01, "sigma")[1],
          nu=fitted(mod01, "nu")[1],
          tau=fitted(mod01, "tau")[1],
          from = 0, to = 1, n=101)

```

```{r, cache=TRUE}



#data(usair)
#mod1 <- gamlss(ResponsePct ~ ., data = temp.lgclust.nodemo, family = BEINF)

#mod1 <- gamlss(ResponsePct ~ Condition +
#Dataset + DatasetOrder +
#DatasetStartTime + TaskOrder + CorrectAnswer + Underestimated +
#Stats.Q_TotalDuration + Stats.OperatingSystem + Demo.age +
#Demo.gender + Demo.lang + Demo.educ + Demo.acfield +
#Demo.dailytech_Computer + Demo.dailytech_Tablet + Demo.dailytech_SmartPhone +
#Demo.weeklygaming + Demo.expdataanal + Demo.expdatavis + Demo.expreadnetvis +
#Demo.expcreatenetvis + StatsNumPixels + AvgDeg + Density + LargeClust1 +
#Modularity + NumClust + NumHighDegree + NumLinks + NumNodes + NumNodesClust1 +
#ConditionPhrasing + Conditionlayouts + ConditionColor + Ctrl_dummy +
#Demo.expreadnetvis.alot + Demo.expcreatenetvis.alot + Stats.OperatingSystemCombined +
#Stats.OperatingSystemCombined2 + Stats.OperatingSystemCombined3 +
#Stats.OperatingSystemCombined4 + Stats.OperatingSystemCombined5 +
#Stats.OperatingSystemWindows + Stats.OperatingSystemMacintosh +
#Stats.OperatingSystemAndroid + Stats.OperatingSystemiPhone +
#Stats.OperatingSystemNumClust + Demo.acfieldGrouped + Demo.acfieldGrouped2 +
#Demo.acfieldGrouped3 + Overestimated + UnderestDummy +
#DatasetDuration,
#data = temp, family = BEINF)

mod1 <- gamlss(ResponsePct ~ 
Dataset + DatasetOrder + 
#Demo.age +
#Demo.gender + Demo.lang + Demo.educ + Demo.acfield +
#Demo.dailytech_Computer + Demo.dailytech_Tablet + Demo.dailytech_SmartPhone +
#Demo.weeklygaming + Demo.expdataanal + Demo.expdatavis + Demo.expreadnetvis +
#Demo.expcreatenetvis + 
UnderestDummy,
data = temp.lgclust.nodemo, family = BEINF)

#library(MASS)
#dropterm(mod1, test = "Chisq")

dropterm(mod1, test = "Chisq")

#To demonstrate the function addterm consider adding a two way interaction term into the model mod1. Note that the scope argument has to be defined explicitly here.
#addterm(mod1, scope = ~(x1 + x2 + x3 + x4 + x5 + x6)^2, test = "Chisq")

addterm(mod1, scope = ~(Dataset + DatasetOrder + UnderestDummy)^2, test = "Chisq")

mod2 <- gamlss(ResponsePct ~ Dataset + DatasetOrder + UnderestDummy +
                 Dataset:UnderestDummy +
                 DatasetOrder:UnderestDummy,
               data = temp.lgclust.nodemo, family = BEINF)

summary(mod2)

mod3 <- stepGAIC(mod1, scope = list(lower = ~1, upper = ~(Dataset + DatasetOrder + UnderestDummy)^2))

# Final
# esponsePct ~ Dataset + DatasetOrder + UnderestDummy + Dataset:UnderestDummy + DatasetOrder:UnderestDummy 

AIC(mod1, mod2, mod3)
# mod3 is best

mod3$anova
# pretty complicated model, though

#gs <- gamlss.scope(model.frame(ResponsePct ~ Dataset + factor(UnderestDummy) + factor(Demo.gender) + factor(Demo.lang) + Demo.expreadnetvis + factor(Stats.OperatingSystemWindows), data = temp))

#gs

#mod4 <- stepGAIC.CH(mod3, scope = gs, k = 2)
# no real point looking for smoothing functions; all of these are factor variables
#mod4$anova
#formula(mod4, "mu")

#op <- par(mfrow = c(3, 2))
# term.plot(mod3, se = T, partial = T)
# par(op)

mod7<-stepGAIC(mod3, what="sigma", scope=~Dataset + DatasetOrder + UnderestDummy)

summary(mod7)
# final sigma: ~UnderestDummy + Dataset 

```

```{r, cache=TRUE, eval=FALSE}

temp.lgclust.all <- layouts_lgclust %>% 
  mutate(ResponsePct = Response/100, 
         StatsNumPixels=scale(StatsNumPixels)) %>%
  dplyr::select(-Demo.educ_TEXT,-Demo.acfieldother,-Attempt,-NodeRank,-MaxNodeRank,-Stats.CompensationCondition, -ClustConf) %>%
  drop_na()


#data(usair)
#mod1 <- gamlss(ResponsePct ~ ., data = temp.lgclust.nodemo, family = BEINF)

#mod1 <- gamlss(ResponsePct ~ Condition +
#Dataset + DatasetOrder +
#DatasetStartTime + TaskOrder + CorrectAnswer + Underestimated +
#Stats.Q_TotalDuration + Stats.OperatingSystem + Demo.age +
#Demo.gender + Demo.lang + Demo.educ + Demo.acfield +
#Demo.dailytech_Computer + Demo.dailytech_Tablet + Demo.dailytech_SmartPhone +
#Demo.weeklygaming + Demo.expdataanal + Demo.expdatavis + Demo.expreadnetvis +
#Demo.expcreatenetvis + StatsNumPixels + AvgDeg + Density + LargeClust1 +
#Modularity + NumClust + NumHighDegree + NumLinks + NumNodes + NumNodesClust1 +
#ConditionPhrasing + Conditionlayouts + ConditionColor + Ctrl_dummy +
#Demo.expreadnetvis.alot + Demo.expcreatenetvis.alot + Stats.OperatingSystemCombined +
#Stats.OperatingSystemCombined2 + Stats.OperatingSystemCombined3 +
#Stats.OperatingSystemCombined4 + Stats.OperatingSystemCombined5 +
#Stats.OperatingSystemWindows + Stats.OperatingSystemMacintosh +
#Stats.OperatingSystemAndroid + Stats.OperatingSystemiPhone +
#Stats.OperatingSystemNumClust + Demo.acfieldGrouped + Demo.acfieldGrouped2 +
#Demo.acfieldGrouped3 + Overestimated + UnderestDummy +
#DatasetDuration,
#data = temp, family = BEINF)

mod1 <- gamlss(ResponsePct ~ DatasetOrder +
CorrectAnswer + 
Stats.OperatingSystem + 
Demo.acfield +
Demo.expdataanal + 
UnderestDummy,
data = temp.lgclust.all, family = BEINF)



#library(MASS)
#dropterm(mod1, test = "Chisq")

dropterm(mod1, test = "Chisq")

#To demonstrate the function addterm consider adding a two way interaction term into the model mod1. Note that the scope argument has to be defined explicitly here.
#addterm(mod1, scope = ~(x1 + x2 + x3 + x4 + x5 + x6)^2, test = "Chisq")

addterm(mod1, scope = ~(DatasetOrder + CorrectAnswer + Stats.OperatingSystem + 
    Demo.acfield + Demo.expdataanal + UnderestDummy)^2, test = "Chisq")

mod2.all <- gamlss(ResponsePct ~ DatasetOrder + CorrectAnswer + Stats.OperatingSystem + 
    Demo.acfield + Demo.expdataanal + UnderestDummy +
                 CorrectAnswer:UnderestDummy +
      Demo.expdataanal:UnderestDummy +
      CorrectAnswer:Demo.expdataanal +
      DatasetOrder:UnderestDummy +
      CorrectAnswer:Demo.acfield +
      CorrectAnswer:Stats.OperatingSystem +
      Stats.OperatingSystem:Demo.acfield,
               data = temp.lgclust.all, family = BEINF)

summary(mod2.all)

mod2.all$anova

AIC(mod7, mod2.all)

mod3.all <- stepGAIC(mod1, scope = list(lower = ~1, 
                                        upper = ~(DatasetOrder + CorrectAnswer + Stats.OperatingSystem +
                                                    Demo.acfield + Demo.expdataanal + UnderestDummy)^2))

# Final
# ResponsePct ~ DatasetOrder + CorrectAnswer + Stats.OperatingSystem +  
#    Demo.acfield + Demo.expdataanal + UnderestDummy + CorrectAnswer:UnderestDummy +  
#    CorrectAnswer:Demo.expdataanal + DatasetOrder:UnderestDummy 

AIC(mod1, mod2.all, mod3.all, mod7)
# mod3.all is best

mod3.all$anova
# pretty complicated model, though

#gs <- gamlss.scope(model.frame(ResponsePct ~ Dataset + factor(UnderestDummy) + factor(Demo.gender) + factor(Demo.lang) + Demo.expreadnetvis + factor(Stats.OperatingSystemWindows), data = temp))

#gs

#mod4 <- stepGAIC.CH(mod3, scope = gs, k = 2)
# no real point looking for smoothing functions; all of these are factor variables
#mod4$anova
#formula(mod4, "mu")

op <- par(mfrow = c(3, 2))
 term.plot(mod3.all, se = T, partial = T)
 par(op)

#mod7.all<-stepGAIC(mod3.all, what="sigma", scope=~DatasetOrder + CorrectAnswer + Stats.OperatingSystem +  
#    Demo.acfield + Demo.expdataanal + UnderestDummy)
mod7.all<-stepGAIC(mod3.all, what="sigma", scope=~DatasetOrder + CorrectAnswer + UnderestDummy)

summary(mod7.all)
# final sigma: ~UnderestDummy + CorrectAnswer
# final model:
# gamlss(formula = ResponsePct ~ DatasetOrder + CorrectAnswer +  
#    Stats.OperatingSystem + Demo.acfield + Demo.expdataanal +  
#    UnderestDummy + CorrectAnswer:UnderestDummy + CorrectAnswer:Demo.expdataanal +  
#    DatasetOrder:UnderestDummy, sigma.formula = ~UnderestDummy +  
#    CorrectAnswer, family = BEINF, data = temp.lgclust.all, trace = FALSE)

alt.mod7.all <- gamlss(formula = ResponsePct ~ Dataset + DatasetOrder +  
    UnderestDummy + Dataset:UnderestDummy + DatasetOrder:UnderestDummy,  
    sigma.formula = ~UnderestDummy + Dataset, family = BEINF,  
    data = temp.lgclust.all, trace = FALSE) 

alt.mod7 <- gamlss(formula = ResponsePct ~ DatasetOrder + CorrectAnswer +  
    Stats.OperatingSystem + 
    UnderestDummy + CorrectAnswer:UnderestDummy + 
    DatasetOrder:UnderestDummy, sigma.formula = ~UnderestDummy +  
    CorrectAnswer, family = BEINF, data = temp.lgclust.nodemo, trace = FALSE)

# mod7 fits very well (lower AIC, lower df) and includes more data (802 records instead of 605)
# mod7.all fits less well on fewer records, but takes into account more variables
# the same parameters for mod7 don't work as well on the dataset limited 
# to people who filled out demographics info, so that subset seems biased or underpowered? 
# or maybe mod7 is overfit? using non-demo parameters from mod7.all on nodemo data works well, 
# but not as well as original mod7


AIC(mod1, mod2.all, mod3.all, mod7.all, mod7, alt.mod7.all, alt.mod7)


```

```{r}

#SAVE THE RESULTS
save(mod7, file = file.path(analysisDataDir,"fits/layout_lgclust_beinf_int.RData"))

```

```{r, cache=TRUE}

mod7$call

mod7.tidy.df <- tidy(mod7)
mod7.tidy.df.mu <- mod7.tidy.df %>% filter(parameter == "mu")

mod7.ci.df <- confint_tidy(mod7)
#mod7.ci.df.nona <- mod7.ci.df %>% drop_na()

#mod7.tidyci.df <- bind_cols(mod7.tidy.df.mu, mod7.ci.df.nona)
mod7.tidyci.df <- bind_cols(mod7.tidy.df.mu, mod7.ci.df)

mod7.aug.df <- augment(mod7,temp.lgclust.nodemo) # augment isn't supposed to work but seems to
#mod7.summ.df <- glance(mod7) #glance doesn't work

mod7.tidyci.df$term <- factor(mod7.tidyci.df$term,
                                          levels=mod7.tidyci.df %>% arrange(estimate) %>%
                                            dplyr::select(term) %>% unlist())

ggplot(mod7.aug.df) + geom_point(aes(ResponsePct,.fitted))

ggplot(layouts_lgclust, aes(Response)) +
geom_histogram(binwidth = 1) +
labs(title="Distribution of Response values for Percentage of Nodes\nin Largest Cluster task, layout conditions")

ggplot(mod7.aug.df, aes(ResponsePct,.fitted)) +
geom_bin2d() +
geom_smooth(method="lm") +
labs(title="Real vs. Predicted Response values for Percentage of Nodes\nin Largest Cluster task, layout conditions",
x="Response as a Percentage")


Rsq(mod7)


#ggplot(mod7.tidyci.df, aes(term, estimate)) + 
#  geom_point() + 
#  coord_flip()

#ggplot(mod7.aug.df %>% group_by(Dataset) %>% summarize(est=mean(.fitted))) +
#  geom_point(aes(Dataset,est)) +
#  #scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
#  coord_flip()

#plot(emmeans(layout.clickhd.nb.full, "Dataset"))

#ggplot(mod7.aug.df) +
#  geom_violin(aes(Dataset,.fitted)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% summarize(est=median(ResponsePct)),aes(Dataset,est)) +
#  #scale_y_continuous(limits = c(-.06,1.2), breaks=c(0,.3,.6,.9,1.2)) +
#  coord_flip()

# could be okay, but not sure of calculation
#ggplot(data = mod7.aug.df) + 
#  geom_errorbar(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(.fitted), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est, ymin=ymin, ymax=ymax, width=.2)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(.fitted), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est))

# no good
#ggplot(data = mod7.aug.df) + 
#  geom_errorbar(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(ResponsePct), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est, ymin=ymin, ymax=ymax, width=.2)) +
#  geom_point(data=mod7.aug.df %>% group_by(Dataset) %>% 
#               summarize(est=mean(ResponsePct), 
#                         ymin=mean(.fitted-1.96*.se.fit), 
#                         ymax=mean(.fitted+1.96*.se.fit)),
#             aes(Dataset,est))
  

```


```{r}

predict.current <- bind_cols(temp.lgclust.nodemo,
                             as.data.frame(predict(mod7,what="mu",type="response",se.fit=TRUE)))
# can also get fitted values with fitted(mod7), just join to temp

ggplot(predict.current) + geom_point(aes(ResponsePct,fit))

# trying to reproduce other M/SE calculations; doesn't seem quite right
#ggplot(predict.current %>% 
#         group_by(Dataset) %>% 
#         summarise(avgFit=mean(fit),avgSE=mean(se.fit)) %>% 
#         mutate(lower.CI=avgFit-avgSE, upper.CI=avgFit+avgSE)) + 
#  geom_pointrange(aes(Dataset,avgFit,ymin=lower.CI,ymax=upper.CI))

#lsmeans(mod7, ~ Dataset)
#Anova(mod7)

ggplot(mod7.aug.df) + geom_point(aes(ResponsePct, .fitted))

# the fitted values from this are different from the fitted values from augment with broom --
# different scale anyway.  why?
# answer: augment is using type="link" rather than type="response"; hard to compare to ResponsePct directly, but
# matches result from term.plot better?

```


```{r}

Rsq(mod7)
Rsq(mod7, type="both")

```

```{r, eval=FALSE}
#a1 <- mod7$anova
#a1 <- anova(mod7)
#a1 <- aov(mod7, what="mu")

#posthoc <- TukeyHSD(x=a1, 'temp$Dataset', conf.level=0.95)
# doesn't work

summary(mod7)

#acfResid(mod7)

#dtop(mod7)

plot(mod7)

plot2way(mod7,c("Dataset","UnderestDummy"))

print(mod7)

rqres.plot(mod7, ylim.all=1)
#rqres.plot(mod7, howmany=40, plot="all")

term.plot(mod7, ask=FALSE)

ggplot(mod7.aug.df %>% group_by(Dataset) %>% summarise(median=median(.fitted))) + geom_boxplot(aes(Dataset,median)) + scale_y_continuous(limits=c(-2,3))

#term.plot(mod7, ask=FALSE, pages=1)
#term.plot(mod7, ask=FALSE, partial.resid = TRUE)
term.plot(mod7, what="mu", ask=FALSE)
term.plot(mod7, what="sigma", ask=FALSE)



temp2 <- temp
temp2$Demo.ResponseID <- factor(temp2$Demo.ResponseID)



hist(temp.lgclust.nodemo$ResponsePct)

pdf.plot(obj=mod7, min=0, max=1, step=.01)

# plotting the distribution
plotBEINF(mu = predict(mod7, what="mu", type="response")[1], 
          sigma = predict(mod7, what="sigma", type="response")[1], 
          nu = predict(mod7, what="nu", type="response")[1], 
          tau = predict(mod7, what="tau", type="response")[1],
          from = 0, 
          to = 1, 
          n = 101)

# trying link instead
#plotBEINF(mu = predict(mod7, what="mu", type="link"), 
#          sigma = predict(mod7, what="sigma", type="link"), 
#          nu = predict(mod7, what="nu", type="link"), 
#          tau = predict(mod7, what="tau", type="link"),
#          from = 0, 
#          to = 1, 
#          n = 101)


# plotting the cdf
plot(function(y) pBEINF(y, mu = predict(mod7, what="mu", type="response")[1], 
          sigma = predict(mod7, what="sigma", type="response")[1], 
          nu = predict(mod7, what="nu", type="response")[1], 
          tau = predict(mod7, what="tau", type="response")[1]), 0, 1)

# plotting the inverse cdf
plot(function(y) qBEINF(y, mu = predict(mod7, what="mu", type="response")[1], 
          sigma = predict(mod7, what="sigma", type="response")[1], 
          nu = predict(mod7, what="nu", type="response")[1], 
          tau = predict(mod7, what="tau", type="response")[1]), 0.01, .99)

# mean
meanBEINF(mod7)[1]



# from http://www.stat.tugraz.at/friedl/GAMLSS/Practical-Graz.pdf
# The worm plot (see Section ??) is a de-trended normal Q-Q plot of the residuals. Modelinadequacy is indicated when many points plotted lie outside the (dotted) point-wise 95% confidence bands. 

wp(mod7, ylim.all=1) # not great

#wp(mod7, resid = resid(mod7), xvar=~temp$Dataset)
# not quite right

#edfAll(mod7)

mod7$call

fittedPlot(mod7, x=temp.lgclust.nodemo$Dataset)
fittedPlot(mod7, x=factor(temp.lgclust.nodemo$DatasetOrder))
fittedPlot(mod7, x=factor(temp.lgclust.nodemo$UnderestDummy))

#Q.stats(mod7,xvar=temp.lgclust.nodemo$Dataset,n.inter=30)


```

```{r, eval=FALSE}


smod7<-summary(mod7, save=TRUE)
smod7$mu.coef.table
smod7$sigma.coef.table
smod7$coef.table
smod7$coef
smod7$object$anova
#to get a list of all the slots in the object
str(smod7)

estimate.pval.mu <- as.data.frame(cbind(term=rownames(smod7$coef.table[c(1:23),]),smod7$coef.table[c(1:23),]), row.names=FALSE, stringsAsFactors = FALSE)


```

```{r, eval=FALSE}

# try https://stats.stackexchange.com/questions/29044/plotting-confidence-intervals-for-the-predicted-probabilities-from-a-logistic-re

# https://stats.stackexchange.com/questions/299792/r-lm-covariance-matrix-manual-calculation-failure

#print(vcov(mod7))

#new.data <- expand.grid(
#  ResponsePct=seq(0,1,by=.001),
#  Dataset=unique(temp$Dataset),
#  UnderestDummy=unique(temp$UnderestDummy),
#  Demo.gender=unique(temp$Demo.gender),
#  Demo.lang=unique(temp$Demo.lang),
#  Demo.expreadnetvis=unique(temp$Demo.expreadnetvis),
#  Stats.OperatingSystemWindows=unique(temp$Stats.OperatingSystemWindows)
#  )

#beta.pred <-bind_cols(as.data.frame(predictAll(mod7, newdata=new.data, type="response")))

pi <- mod7.aug.df$.fitted

w <- pi * (1 - pi)

v <- diag(w, length(w), length(w))

#XtX_inv <- solve(t(as.matrix(new.data)) %*% v %*% as.matrix(new.data))
# still doesn't work

#p0 = nu /(1+nu+tau) & p1 = tau/(1+nu+tau)

vcov.mod7 <- vcov(mod7) # just mu? 23 x 23 (no, mu has 25 coefficients, but 23 df?)
vcov.mod7.2 <- smod7$covmat$vcov # all? 32 x 32
std.err <- sqrt(t(as.matrix(new.data)) %*% vcov.mod7 %*% as.matrix(new.data))

trans <- t(as.matrix(new.data))
new.data.mat <- as.matrix(new.data)

trans %*% new.data.mat

plot(mod7)

sum.pred <- beta.pred %>% group_by(Dataset) %>% summarise(mean=mean(mu),
                                                          sd=sd(mu),
                                                          sample.size=n(),
                                                          df=sample.size-1,
                                                          alpha=.025,
                                                          t.dist=1.96,
                                                          mod=t.dist*(sd/sqrt(sample.size)),
                                                          lower.ci=mean-mod,
                                                          upper.ci=mean+mod
                                                          )

ggplot(beta.pred) + geom_boxplot(aes(Dataset, mu)) + scale_y_continuous(limits=c(0,1)) + coord_flip()
ggplot(sum.pred, aes(Dataset, mean)) + geom_errorbar(aes(ymin=lower.ci,ymax=upper.ci)) + geom_point() + scale_y_continuous(limits=c(0,1)) + coord_flip()



```

```{r, eval=FALSE}
#mod2 <- stepGAIC.VR(mod1) 
#or
#mod2<-stepGAIC(mod1, additive=FALSE)
#mod2$anova
#mod2 <- stepGAIC(mod1, k = log(41))
#mod3 <- stepGAIC(mod1, scope = list(lower = ~1, upper = ~(x1 + x2 + x3 + x4 + x5 + x6)^2))
#mod3$anova
#mod2 <- stepGAIC.VR(mod1)
#mod2$anova
#mod2 <- stepGAIC(mod1, k = log(41))
#mod3 <- stepGAIC(mod1, scope = list(lower = ~1, upper = ~(x1 + x2 + x3 + x4 + x5 + x6)^2))
#gs <- gamlss.scope(model.frame(y ~ x1 + x2 + x3 + x4 + x5 + x6, data = usair))
#gs
#gs1 <- gamlss.scope(model.frame(y ~ x1 + x2 + x3 + x4 + x5 + x6, data = usair), smoother = "lo", arg = "span=.7", form = TRUE)
#gs1
#mod5 <- gamlss(y ~ 1, data = usair, family = GA)
#mod6 <- stepGAIC(mod5, gs, additive = TRUE)
#mod6$anova
#mod6
#mod7<-stepGAIC(mod6, what="sigma", scope=~x1+x2+x3+x4+x5+x6)
#mod7$anova

#We start with a model for mu including all the explanatory variables.
#We shall now use the dropterm to check if model m1 can be simplified by dropping any of the existing terms in mu and the function addterm to check whether two way interactions of the existing terms are needed.
#Based on the Chi square tests no terms can be left out and no two way interaction is needed.
#Since we established that adding or dropping terms in mu is not beneficial there is nopoint using stepGAIC.VR() for modelling the mu parameter with linear terms. Instead we will use (stepGAIC.CH()) trying to establish if smoothing terms are needed in the mu model.
#gs <- gamlss.scope(model.frame(Claims ~ factor(SD) + L_Popdensity + L_KI + L_Accidents + L_Population, data = LGAclaims))
#gs
#m2 <- stepGAIC.CH(m1, scope = gs, k = 2)
#m2$anova
#formula(m2, "mu")
#The best model includes smoothing terms for L_Popdensity, L_Accidents and L_Population but not for L_KI.
#op <- par(mfrow = c(3, 2))
#term.plot(m2, se = T, partial = T)
#par(op)
#Given that we have establish a good model for mu, we proceed to find a good model for sigma. We start first with linear terms but we exclude the factor SD since some of the levels of the factor have very few observations.
#m11 <- stepGAIC.VR(m2, scope = ~L_Popdensity + L_KI + L_Accidents + L_Population, what = "sigma", k = 2)
#m11$anova
#Note that the argument what is used here to determine which distribution parameter is to be modelled. Here variables L_Population, L_KI and L_Accidents were found important in explaining the sigma parameter. The model chosen using AIC appears over complicated. Maybe a higher penalty for GAIC would be more appropriate here.
```

```{r, eval=FALSE}

# https://github.com/mjskay/when-ish-is-my-bus/blob/master/bus-model.Rmd

predictions <- expand.grid(
  ResponsePct=seq(0,1,by=.001),
  Dataset=unique(temp$Dataset),
  UnderestDummy=unique(temp$UnderestDummy),
  Demo.gender=unique(temp$Demo.gender),
  Demo.lang=unique(temp$Demo.lang),
  Demo.expreadnetvis=unique(temp$Demo.expreadnetvis),
  Stats.OperatingSystemWindows=unique(temp$Stats.OperatingSystemWindows)
  ) %>% 
  cbind(predictAll(mod7, newdata = ., data=temp)) %>% 
  mutate(
        upper95 = qBEINF(.975, mu, sigma, nu, tau),
        lower95 = qBEINF(.025, mu, sigma, nu, tau),
        upper80 = qBEINF(.9, mu, sigma, nu, tau),
        lower80 = qBEINF(.1, mu, sigma, nu, tau),
        upper50 = qBEINF(.75, mu, sigma, nu, tau),
        lower50 = qBEINF(.25, mu, sigma, nu, tau),
        upper10 = qBEINF(.55, mu, sigma, nu, tau),
        lower10 = qBEINF(.45, mu, sigma, nu, tau)
    )
  
# What is predictAll adding?  is it really predicting a new value for ResponsePct? maybe need to take a log of mu?

predictions %>%
    ggplot(aes(x = ResponsePct, y=mu)) +
  geom_bin2d() +
  facet_wrap(~Dataset)
```

```{r, eval=FALSE}

mbi1 <- gamlss(ResponsePct ~ 1, data = temp, family = BEINF)
mbi2<-stepGAIC(mbi1,scope=list(upper=~(Condition + Dataset + DatasetOrder)^2))

summary(mbi2)
mbi2$anova

mBB21<-stepGAIC(mbi2,what="sigma",scope=list(upper=~(Condition + Dataset + DatasetOrder)^2))

mBB22<-stepGAIC(mBB21,what="mu")

mBB22$call

mBB23 <- stepGAIC(mBB22,scope=gamlss.scope(model.frame(Response~Dataset, data=temp)),what="mu")

mBB23$anova

term.plot(mBB23)

mBB23$call

```

#### Least Squares

mod7
gamlss(formula = ResponsePct ~ Dataset + DatasetOrder + UnderestDummy + 
    Dataset:UnderestDummy + DatasetOrder:UnderestDummy, sigma.formula = ~UnderestDummy + 
    Dataset, family = BEINF, data = temp.lgclust.nodemo, trace = FALSE)

##### Dataset

###### gamlss

```{r}

term.plot(mod7, ask=FALSE)

```


```{r}

#means_m1 <- lpred(mod7, type='response', what='mu', se.fit=T)

means_m1 <- lpred(mod7, type='terms', terms="Dataset", what='mu', se.fit=T)

#mod.t <- lpred(mod7, type = "terms", terms= "Dataset")
#mod.t

#mod.lp <- lp(mod7)
#mod.lp

df_fit <- data.frame(Dataset = temp.lgclust.nodemo$Dataset, M = means_m1$fit, SE = means_m1$se.fit)
names(df_fit) <- c("Dataset","M","SE")

#ggplot(df_fit, aes(Dataset, M)) + 
#  geom_pointrange(aes(ymin=M-SE, ymax=M+SE)) + 
#  scale_y_continuous(labels=scales::percent)

# not bad, might work
ggplot(df_fit, aes(Dataset, M)) + 
  geom_errorbar(aes(ymin=M-SE, ymax=M+SE), width=.2) + 
  geom_point(size=7) +
  labs(title="Model Fit for Dataset for Percentage of Nodes\nin Largest Cluster task, layout conditions",
       y="Fit")




```

```{r, eval=FALSE}

#df_fit.compare <- df_fit %>% tibble::rowid_to_column(., ".iteration") %>% 
#  mutate(.chain=1,
#         Dataset=as.character(Dataset)) %>% 
#  rename(estimate=M) %>%
#  dplyr::select(-SE)

df_fit.compare <- mod7.aug.df %>% 
  dplyr::select(Dataset,.fitted) %>%
  tibble::rowid_to_column(., ".iteration") %>% 
  mutate(.chain=1, Dataset=as.character(Dataset)) %>% 
  rename(estimate=.fitted) 

mod7.pairs <- df_fit.compare %>% compare_levels(estimate, by=Dataset)

```

```{r, eval=FALSE}

library(modelr)

mod7.aug.df %>%
  data_grid(Dataset) %>%
  add_predicted_samples(mod7) %>%
  ggplot(aes(x = pred, y = Dataset)) +
  stat_pointintervalh(.prob = c(.66, .95))

```


##### DatasetOrder

###### gamlss

```{r}

term.plot(mod7, ask=FALSE)

```


```{r}

#means_m1 <- lpred(mod7, type='response', what='mu', se.fit=T)

means_m1 <- lpred(mod7, type='terms', terms="DatasetOrder", what='mu', se.fit=T)

#mod.t <- lpred(mod7, type = "terms", terms= "Dataset")
#mod.t

#mod.lp <- lp(mod7)
#mod.lp

df_fit <- data.frame(DatasetOrder = factor(temp.lgclust.nodemo$DatasetOrder), M = means_m1$fit, SE = means_m1$se.fit)
names(df_fit) <- c("DatasetOrder","M","SE")

#ggplot(df_fit, aes(Dataset, M)) + 
#  geom_pointrange(aes(ymin=M-SE, ymax=M+SE)) + 
#  scale_y_continuous(labels=scales::percent)

# not bad, might work
ggplot(df_fit, aes(DatasetOrder, M)) + 
  geom_errorbar(aes(ymin=M-SE, ymax=M+SE), width=.2) + 
  geom_point(size=7) +
  labs(title="Model Fit for Dataset Order for Percentage of Nodes\nin Largest Cluster task, layout conditions",
       x="Dataset Order",
       y="Fit")


```



##### UnderestDummy

###### gamlss

```{r}

term.plot(mod7, ask=FALSE)

```


```{r}

#means_m1 <- lpred(mod7, type='response', what='mu', se.fit=T)

means_m1 <- lpred(mod7, type='terms', terms="UnderestDummy", what='mu', se.fit=T)

#mod.t <- lpred(mod7, type = "terms", terms= "Dataset")
#mod.t

#mod.lp <- lp(mod7)
#mod.lp

df_fit <- data.frame(UnderestDummy = temp.lgclust.nodemo$UnderestDummy, M = means_m1$fit, SE = means_m1$se.fit)
names(df_fit) <- c("UnderestDummy","M","SE")

#ggplot(df_fit, aes(Dataset, M)) + 
#  geom_pointrange(aes(ymin=M-SE, ymax=M+SE)) + 
#  scale_y_continuous(labels=scales::percent)

# not bad, might work
ggplot(df_fit, aes(UnderestDummy, M)) + 
  geom_errorbar(aes(ymin=M-SE, ymax=M+SE), width=.2) + 
  geom_point(size=7) +
  scale_x_discrete(labels=c("Underestimated", "Correct or Overestimated"), name="Underestimated") +
labs(title="Model Fit for Underestimated for Percentage of Nodes\nin Largest Cluster task, layout conditions",
y="Fit")


```


##### Dataset:UnderestDummy

###### gamlss

```{r}

plot2way(mod7,c("Dataset","UnderestDummy"))
plot2way(mod7,c("UnderestDummy","Dataset"))

```


```{r, eval=FALSE}

means_m1 <- data.frame(lpred(mod7, type='terms', terms=c("Dataset","UnderestDummy"), what='mu', se.fit=T)) %>%
  unite(data.comb, fit.Dataset, se.fit.Dataset) %>% 
  unite(under.comb, fit.UnderestDummy, se.fit.UnderestDummy) %>%
  bind_cols(temp %>% dplyr::select(Dataset, UnderestDummy),.) %>%
  gather(key=term,value=united, data.comb, under.comb) %>%
  separate(united,into=c("fit","se.fit"), sep="[_]",convert=TRUE) %>%
  mutate(term=case_when(term=="data.comb" ~ "Dataset",
                        term=="under.comb" ~ "UnderestDummy"))

#means_m1

means_m1 <- data.frame(lpred(mod7, type='terms', terms=c("Dataset","UnderestDummy"), what='mu', se.fit=T)) %>%
  unite(data.comb, fit.Dataset, se.fit.Dataset) %>% 
  unite(under.comb, fit.UnderestDummy, se.fit.UnderestDummy) %>%
  bind_cols(temp %>% dplyr::select(Dataset, UnderestDummy),.) %>%
  gather(key=term,value=united, data.comb, under.comb) %>%
  separate(united,into=c("fit","se.fit"), sep="[_]",convert=TRUE) %>%
  mutate(term=case_when(term=="data.comb" ~ "Dataset",
                        term=="under.comb" ~ "UnderestDummy")) %>%
  group_by(Dataset, UnderestDummy,term) %>%
  summarize(meanFit=mean(fit),
            meanSE=mean(se.fit))

ggplot(means_m1, aes(Dataset, meanFit, color=term)) + 
  geom_errorbar(aes(ymin=meanFit-meanSE, ymax=meanFit+meanSE), width=.2) + 
  geom_point(size=7) +
  facet_grid(.~term)

```


##### DatasetOrder:UnderestDummy

###### gamlss

```{r}

plot2way(mod7,c("DatasetOrder","UnderestDummy"))
plot2way(mod7,c("UnderestDummy","DatasetOrder"))

```


```{r, eval=FALSE}

means_m1 <- data.frame(lpred(mod7, type='terms', terms=c("Dataset","UnderestDummy"), what='mu', se.fit=T)) %>%
  unite(data.comb, fit.Dataset, se.fit.Dataset) %>% 
  unite(under.comb, fit.UnderestDummy, se.fit.UnderestDummy) %>%
  bind_cols(temp %>% dplyr::select(Dataset, UnderestDummy),.) %>%
  gather(key=term,value=united, data.comb, under.comb) %>%
  separate(united,into=c("fit","se.fit"), sep="[_]",convert=TRUE) %>%
  mutate(term=case_when(term=="data.comb" ~ "Dataset",
                        term=="under.comb" ~ "UnderestDummy"))

#means_m1

means_m1 <- data.frame(lpred(mod7, type='terms', terms=c("Dataset","UnderestDummy"), what='mu', se.fit=T)) %>%
  unite(data.comb, fit.Dataset, se.fit.Dataset) %>% 
  unite(under.comb, fit.UnderestDummy, se.fit.UnderestDummy) %>%
  bind_cols(temp %>% dplyr::select(Dataset, UnderestDummy),.) %>%
  gather(key=term,value=united, data.comb, under.comb) %>%
  separate(united,into=c("fit","se.fit"), sep="[_]",convert=TRUE) %>%
  mutate(term=case_when(term=="data.comb" ~ "Dataset",
                        term=="under.comb" ~ "UnderestDummy")) %>%
  group_by(Dataset, UnderestDummy,term) %>%
  summarize(meanFit=mean(fit),
            meanSE=mean(se.fit))

ggplot(means_m1, aes(Dataset, meanFit, color=term)) + 
  geom_errorbar(aes(ymin=meanFit-meanSE, ymax=meanFit+meanSE), width=.2) + 
  geom_point(size=7) +
  facet_grid(.~term)

```


