---
title: "Analysis for Number of Links task, Layout conditions"
author: "Angela Zoss"
date: "March 25, 2018"
output: github_document
---

```{r layout-setup-numlinks}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r layout-load-environment-numlinks, message=FALSE}

source('LayoutSetup.R')

```

#### lme4

```{r, cache=TRUE}

# Condition

layout.numlinks.lmer.cond <- lmer(LogError ~ Condition + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.cond) # Size extremely significant

anova(layout.numlinks.lmer.cond)

# Condition is significant (p=2.32e-14); trying Ctrl_dummy

layout.numlinks.lmer.dataset <- lmer(LogError ~ Dataset + (1|Demo.ResponseID), data = layouts_numlinks, REML = T)

lmsum <- summary(layout.numlinks.lmer.dataset)
lmsum 

anova(layout.numlinks.lmer.dataset)

# Dataset is significant (p < 2.2e-16); 

layout.numlinks.lmer <- lmer(LogError ~ DatasetOrder + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# DatasetOrder is not significant; trying DatasetDuration

layout.numlinks.lmer <- lmer(LogError ~ DatasetDuration + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# DatasetDuration is not significant

layout.numlinks.lmer <- lmer(LogError ~ DatasetStartTime + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# DatasetStartTime is not significant; trying TaskOrder

layout.numlinks.lmer <- lmer(LogError ~ TaskOrder + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# TaskOrder is not significant; trying CorrectAnswer

layout.numlinks.lmer.correct <- lmer(LogError ~ CorrectAnswer + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.correct)

anova(layout.numlinks.lmer.correct)

# CorrectAnswer is highly significant (p = 3.997e-15); trying Underestimated

layout.numlinks.lmer.underest <- lmer(LogError ~ Underestimated + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.underest)

anova(layout.numlinks.lmer.underest)

# Underestimated is significant (p = 0.009515)

layout.numlinks.lmer <- lmer(LogError ~ scale(Stats.Q_TotalDuration) + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Stats.Q_TotalDuration is not significant; trying Stats.dataset_count

layout.numlinks.lmer <- lmer(LogError ~ Stats.dataset_count + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Stats.dataset_count is not signficant; trying Stats.OperatingSystem

layout.numlinks.lmer <- lmer(LogError ~ Stats.OperatingSystem + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer) # few categories significant

anova(layout.numlinks.lmer)

# Stats.OperatingSystem is not signficant; skipping combinations

layout.numlinks.lmer <- lmer(LogError ~ scale(StatsNumPixels) + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# StatsNumPixels is not signficant; trying Demo.age

layout.numlinks.lmer <- lmer(LogError ~ Demo.age + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.age))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.age is not signficant; trying Demo.gender

layout.numlinks.lmer <- lmer(LogError ~ Demo.gender + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.gender))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.gender is not signficant

layout.numlinks.lmer <- lmer(LogError ~ Demo.lang + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.lang))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.lang is not signficant; trying Demo.educ

layout.numlinks.lmer <- lmer(LogError ~ Demo.educ + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.educ))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.educ is not signficant; trying Demo.acfield

layout.numlinks.lmer <- lmer(LogError ~ Demo.acfield + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.acfield))), REML = T)

summary(layout.numlinks.lmer) # no categories significant

anova(layout.numlinks.lmer)

# Demo.acfield is not signficant; trying Demo.acfieldGrouped

layout.numlinks.lmer <- lmer(LogError ~ Demo.acfieldGrouped + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.acfieldGrouped))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.acfieldGrouped is not signficant

layout.numlinks.lmer <- lmer(LogError ~ Demo.acfieldGrouped2 + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.acfieldGrouped2))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.acfieldGrouped2 is  not signficant

layout.numlinks.lmer <- lmer(LogError ~ Demo.acfieldGrouped3 + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.acfieldGrouped3))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.acfieldGrouped3 is not signficant

layout.numlinks.lmer <- lmer(LogError ~ Demo.dailytech_Computer + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.dailytech_Computer))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.dailytech_Computer is not significant; trying Demo.dailytech_Tablet

layout.numlinks.lmer <- lmer(LogError ~ Demo.dailytech_Tablet + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.dailytech_Tablet))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.dailytech_Computer is not significant; trying Demo.dailytech_SmartPhone

layout.numlinks.lmer <- lmer(LogError ~ Demo.dailytech_SmartPhone + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.dailytech_SmartPhone))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.dailytech_SmartPhone is barely significant; trying Demo.weeklygaming

layout.numlinks.lmer <- lmer(LogError ~ Demo.weeklygaming + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.weeklygaming))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.weeklygaming is not significant; trying Demo.expdataanal

layout.numlinks.lmer <- lmer(LogError ~ Demo.expdataanal + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expdataanal))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.expdataanal is not significant; trying Demo.expdatavis

layout.numlinks.lmer <- lmer(LogError ~ Demo.expdatavis + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expdatavis))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.expdatavis is not significant; trying Demo.expreadnetvis

layout.numlinks.lmer <- lmer(LogError ~ Demo.expreadnetvis + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expreadnetvis))), REML = T)

summary(layout.numlinks.lmer) 

anova(layout.numlinks.lmer)

# Demo.expreadnetvis is not significant; trying Demo.expreadnetvis.alot

layout.numlinks.lmer <- lmer(LogError ~ Demo.expreadnetvis.alot + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expreadnetvis.alot))), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Demo.expreadnetvis.alot is not significant; trying Demo.expcreatenetvis

layout.numlinks.lmer <- lmer(LogError ~ Demo.expcreatenetvis + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expcreatenetvis))), REML = T)

summary(layout.numlinks.lmer) 

anova(layout.numlinks.lmer)

# Demo.expcreatenetvis is not significant; trying Demo.expcreatenetvis.alot

layout.numlinks.lmer <- lmer(LogError ~ Demo.expcreatenetvis.alot + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(!(is.na(Demo.expcreatenetvis.alot))), REML = T)

summary(layout.numlinks.lmer) 

anova(layout.numlinks.lmer)

# Demo.expcreatenetvis.alot is not significant; trying AvgDeg

layout.numlinks.lmer.avgdeg <- lmer(LogError ~ AvgDeg + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.avgdeg)

anova(layout.numlinks.lmer.avgdeg)

# AvgDeg is significant (p < 2.2e-16); trying Density

layout.numlinks.lmer.dens <- lmer(LogError ~ Density + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.dens)

anova(layout.numlinks.lmer.dens)

# Density is significant (p < 2.2e-16); trying LargeClust1

layout.numlinks.lmer.lgclust <- lmer(LogError ~ LargeClust1 + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.lgclust)

anova(layout.numlinks.lmer.lgclust)

# LargeClust1 is significant (p < 2.2e-16); trying Modularity

layout.numlinks.lmer.mod <- lmer(LogError ~ Modularity + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.mod)

anova(layout.numlinks.lmer.mod)

# Modularity is significant (p<2.2e-16); trying NumClust

layout.numlinks.lmer.numclust <- lmer(LogError ~ NumClust + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.numclust)

anova(layout.numlinks.lmer.numclust)

# NumClust is significant (p<2.2e-16); trying NumHighDegree

layout.numlinks.lmer.numhd <- lmer(LogError ~ NumHighDegree + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.numhd)

anova(layout.numlinks.lmer.numhd)

# NumHighDegree is significant (p=0.004365); trying NumLinks

layout.numlinks.lmer.numlinks <- lmer(LogError ~ NumLinks + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.numlinks)

anova(layout.numlinks.lmer.numlinks)

# NumLinks is significant (p=3.997e-15); trying NumNodes

layout.numlinks.lmer.numnodes <- lmer(LogError ~ NumNodes + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.numnodes)

anova(layout.numlinks.lmer.numnodes)

# NumNodes is significant (p<2.2e-16); trying NumNodesClust1

layout.numlinks.lmer.sizeclust1 <- lmer(LogError ~ NumNodesClust1 + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer.sizeclust1)

anova(layout.numlinks.lmer.sizeclust1)

# NumNodesClust1 is significant (p<2.2e-16); 

layout.numlinks.lmer <- lmer(LogError ~ filename + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# filename is not significant

layout.numlinks.lmer <- lmer(LogError ~ NetVisExperience + (1|Demo.ResponseID), data=layouts_numlinks, REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# NetVisExperience is not significant

layout.numlinks.lmer <- lmer(LogError ~ Stats.CompensationCondition + (1|Demo.ResponseID), data=layouts_numlinks %>% filter(filename=="FacultyGrad"), REML = T)

summary(layout.numlinks.lmer)

anova(layout.numlinks.lmer)

# Stats.CompensationCondition is not significant
```

```{r}

temp.numlinks <- layouts_numlinks %>% 
  dplyr::select(Demo.ResponseID,LogError,Condition,Dataset,CorrectAnswer,Underestimated,
                AvgDeg,Density,LargeClust1,Modularity,NumClust,NumHighDegree,NumLinks,
                NumNodes,NumNodesClust1) %>% drop_na() %>% mutate(CorrectAnswer=scale(CorrectAnswer))

layout.numlinks.lmer.full <- lmer(LogError ~ Condition + 
                                   Dataset +
                                    Underestimated +
                                   (1|Demo.ResponseID), 
                                 data=temp.numlinks, REML = T)

summary(layout.numlinks.lmer.full)

anova(layout.numlinks.lmer.full)

```

```{r}


layout.numlinks.lmer.full.int <- lmer(LogError ~ Condition + 
                                   Dataset +
                                    Underestimated +
                                     Condition:Dataset +
                                   (1|Demo.ResponseID), 
                                 data=temp.numlinks, REML = T)

summary(layout.numlinks.lmer.full.int)

anova(layout.numlinks.lmer.full.int)

anova(layout.numlinks.lmer.full,layout.numlinks.lmer.full.int)
# keep interaction

layout.numlinks.lmer.full.int.2 <- lmer(LogError ~ Condition + 
                                   Dataset +
                                    Underestimated +
                                     Condition:Dataset +
                                     Condition:Underestimated +
                                   (1|Demo.ResponseID), 
                                 data=temp.numlinks, REML = T)

summary(layout.numlinks.lmer.full.int.2)

anova(layout.numlinks.lmer.full.int.2)

anova(layout.numlinks.lmer.full.int.2,layout.numlinks.lmer.full.int)

layout.numlinks.lmer.full.int.3 <- lmer(LogError ~ Condition + 
                                   Dataset +
                                    Underestimated +
                                     Condition:Dataset +
                                     Condition:Underestimated +
                                     Dataset:Underestimated +
                                   (1|Demo.ResponseID), 
                                 data=temp.numlinks, REML = T)

summary(layout.numlinks.lmer.full.int.3)

anova(layout.numlinks.lmer.full.int.3)

anova(layout.numlinks.lmer.full.int.2,layout.numlinks.lmer.full.int.3)

# keep int.3

```

```{r}

#SAVE THE RESULTS
save(layout.numlinks.lmer.full.int.3, 
     file = file.path(analysisDataDir,"fits/layout_numlinks_lmer_int.RData"))

```


```{r, cache=TRUE}

rand(layout.numlinks.lmer.full.int.3)

# result shows that random effects of participant are not significant

anova(layout.numlinks.lmer.full.int.3)

# SmartPhone significant, < 0.01

#ranef(layout.avgdeg.lmer.SP)

# displays the random effects; not that useful

# unlike lme(), lmer() doesn't allow for heterogeneous error variance structures (the "weights")

(r2nsj = r2beta(layout.numlinks.lmer.full.int.3, method = 'nsj', partial = TRUE))[1,'Rsq']

ggplot(layouts_numlinks) + geom_histogram(aes(LogError), binwidth=.005) + labs(title="Distribution of LogError values for Number of Links task,\nlayout conditions")


```

```{r}

plot(layout.numlinks.lmer.full.int.3)

plot(layout.numlinks.lmer.full.int.3, resid(., scaled=TRUE) ~ fitted(.), abline = 0)

plot(layout.numlinks.lmer.full.int.3, resid(.) ~ fitted(.) | Condition, abline = 0)

plot(layout.numlinks.lmer.full.int.3, resid(., scaled=TRUE) ~ fitted(.) | Condition, abline = 0)

plot(layout.numlinks.lmer.full.int.3, LogError ~ fitted(.), abline = c(0,1))



```

```{r}

layout.numlinks.lmer.full.int.3.f <- fortify(layout.numlinks.lmer.full.int.3)

ggplot(layout.numlinks.lmer.full.int.3.f, aes(.fitted,.resid)) + 
  geom_point() +
  #facet_grid(.~Sex) + 
  geom_hline(yintercept=0)

ggplot(layout.numlinks.lmer.full.int.3.f, aes(.fitted,LogError)) + 
  geom_point() +
  geom_abline(aes(slope = 1, intercept = 0))

ggplot(layout.numlinks.lmer.full.int.3.f, aes(LogError,.fitted)) +
geom_point() +
geom_abline(aes(slope = 1, intercept = 0)) +
#scale_y_continuous(limits=c(0,0.3)) +
labs(title="Real vs. Predicted LogError values for Number of Links task,\nlayout conditions")

```

```{r, eval=FALSE}

# TO DO: check out interpretation for these plots??

library(lattice)

prof <-  profile(layout.avgdeg.lmer.SP, optimizer="Nelder_Mead", which="beta_")

prof.CI <- confint(prof)

#CI2 <- confint(layout.avgdeg.lmer.SP, maxpts = 8)

xyplot(prof)

xyplot(prof, absVal = TRUE)

xyplot(prof, conf = c(0.95, 0.99), main = "95% and 99% profile() intervals")

# can also apply logProf() and varianceProf() to profile object

densityplot(prof)

splom(prof)

```

#### Least Squares Means

Do for each categorical predictor. 
Final model (layout.numlinks.lmer.full.int.3): 
LogError ~ Condition + Dataset + Underestimated + Condition:Dataset +  
    Condition:Underestimated + Dataset:Underestimated + (1 | Demo.ResponseID)

##### Condition

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numhighdeg, table(Dataset,Overestimated))
# ref_grid(layout.numhd.lmer.full.int.3) @ grid; .wgt. is number of observations

#grid <- ref_grid(layout.numhd.lmer.full.int.3, at = list(Underestimated = c("over","under")))
#layout.numhd.emm.cond <- emmeans(grid, "Condition")


layout.numlinks.emm.cond <- emmeans(layout.numlinks.lmer.full.int.3, "Condition")
#layout.numhd.emm.condition <- emmeans(layout.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

layout.numlinks.emm.cond

layout.numlinks.emm.cond.df <- dplyr::as_data_frame(layout.numlinks.emm.cond)

layout.numlinks.emm.cond.df

layout.numlinks.emm.cond.cld <- cld(layout.numlinks.emm.cond,
                                   details=TRUE,
                                   #alpha=0.01,
                                   #by="Dataset",
                                   #Letters="|||||||||||||||||||",
                                   sort=TRUE
)

layout.numlinks.emm.cond.cld.df <- layout.numlinks.emm.cond.cld$emmeans

layout.numlinks.emm.cond.cld.df %>% dplyr::select(Condition,.group)

layout.numlinks.emm.cond.cld.df

layout.numlinks.emm.cond.cld.df$Condition <- factor(layout.numlinks.emm.cond.cld.df$Condition, levels=layout.numlinks.emm.cond.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())


#emmip(layout.numhd.lmer.full.int.4, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.cond, ~Condition, CIs = TRUE)
plot(layout.numlinks.emm.cond)
#plot(layout.numlinks.emm.cond, comparisons = TRUE)

layout.numlinks.emm.cond.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.cond.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Condition,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.numlinks.emm.cond.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Condition,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip() +
labs(title="Estimated Marginal Means for Condition for Number of Links task,\nlayout conditions")


#plot(ref_grid(layout.numhd.lmer.full.int.4), by="Condition") 
# try to figure this out? maybe only works on the interaction?

```

```{r}

layout.numlinks.emm.cond.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.cond)) 
layout.numlinks.emm.cond.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

cond.pairs.CI <- confint(pairs(layout.numlinks.emm.cond))

layout.numlinks.emm.cond.pairs <- full_join(layout.numlinks.emm.cond.pairs, cond.pairs.CI)

#layout.numhd.diffemm.condition <- emmeans(layout.numhd.lmer.full.int.4, pairwise ~ Condition)
#layout.numhd.diffemm.condition$contrasts
#contrast(layout.numlinks.emm.condition)
#confint(layout.numlinks.emm.condition)
#pairs(layout.numlinks.emm.condition, details=TRUE)
#confint(contrast(layout.numlinks.emm.condition))
#confint(pairs(layout.numlinks.emm.condition))
#coef(pairs(layout.numlinks.emm.condition))


plot(pairs(layout.numlinks.emm.cond))
plot(pairs(layout.numlinks.emm.cond), comparisons = TRUE)


layout.numlinks.emm.cond.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.cond.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.cond.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.cond.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.cond.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.cond.pairs$sig.levels <- factor(layout.numlinks.emm.cond.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

layout.numlinks.emm.cond.pairs$contrast <- factor(layout.numlinks.emm.cond.pairs$contrast, levels=layout.numlinks.emm.cond.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

layout.numlinks.emm.cond.pairs <- layout.numlinks.emm.cond.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

ggplot(layout.numlinks.emm.cond.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.numlinks.emm.cond.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

cond.copy <- layout.numlinks.emm.cond.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.cond.pairs.compl <- bind_rows(layout.numlinks.emm.cond.pairs, cond.copy)


cond.lev <- c("Ctrl","Cir","Fru","Ord")

layout.numlinks.emm.cond.pairs.compl$From <- factor(layout.numlinks.emm.cond.pairs.compl$From, levels=cond.lev)
layout.numlinks.emm.cond.pairs.compl$To <- factor(layout.numlinks.emm.cond.pairs.compl$To, levels=cond.lev)

#layout.numlinks.emm.cond.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.cond.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.cond.pairs.compl) +
  geom_tile(aes(x=To,y=ordered(From,levels=rev(cond.lev)),fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.cond.pairs.compl) +
  geom_count(aes(x=To,y=ordered(From,levels=rev(cond.lev)),size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.cond.pairs.compl) +
  geom_tile(aes(x=To,y=ordered(From,levels=rev(cond.lev)),fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.cond.pairs.compl) +
  geom_count(aes(x=To,y=ordered(From,levels=rev(cond.lev)),size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

```

##### Dataset

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numhighdeg, table(Dataset,Overestimated))
# ref_grid(layout.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

layout.numlinks.emm.data <- emmeans(layout.numlinks.lmer.full.int.3, "Dataset", nesting = NULL)
#layout.numlinks.emm.condition <- emmeans(layout.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

layout.numlinks.emm.data

layout.numlinks.emm.data.df <- dplyr::as_data_frame(layout.numlinks.emm.data)

layout.numlinks.emm.data.df


# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numlinks.emm.condition)

layout.numlinks.emm.data.cld <- cld(layout.numlinks.emm.data,
                details=TRUE,
                #alpha=0.01,
                #by="Dataset",
                #Letters="|||||||||||||||||||",
                sort=TRUE
)

layout.numlinks.emm.data.cld.df <- layout.numlinks.emm.data.cld$emmeans

layout.numlinks.emm.data.cld.df %>% dplyr::select(Dataset,.group)

layout.numlinks.emm.data.cld.df

layout.numlinks.emm.data.cld.df$Dataset <- factor(layout.numlinks.emm.data.cld.df$Dataset, levels=layout.numlinks.emm.data.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Dataset) %>% unlist())


#emmip(layout.numlinks.lmer.full.int, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.data, ~Dataset, CIs = TRUE)
plot(layout.numlinks.emm.data)
#plot(layout.numlinks.emm.cond, comparisons = TRUE)

layout.numlinks.emm.data.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.data.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Dataset,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.numlinks.emm.data.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Dataset,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip() +
labs(title="Estimated Marginal Means for Dataset for Number of Links task,\nlayout conditions")


#plot(ref_grid(layout.numnodes.lmer.int.3), by="Condition") 
# try to figure this out? maybe only works on the interaction?
```

```{r}

layout.numlinks.emm.data.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.data)) 
layout.numlinks.emm.data.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

pairs.CI <- confint(pairs(layout.numlinks.emm.data))

layout.numlinks.emm.data.pairs <- full_join(layout.numlinks.emm.data.pairs, pairs.CI)

#layout.numhd.diffemm.condition <- emmeans(layout.numhd.lmer.full.int.4, pairwise ~ Condition)
#layout.numhd.diffemm.condition$contrasts
#contrast(layout.numlinks.emm.condition)
#confint(layout.numlinks.emm.condition)
#pairs(layout.numlinks.emm.condition, details=TRUE)
#confint(contrast(layout.numlinks.emm.condition))
#confint(pairs(layout.numlinks.emm.condition))
#coef(pairs(layout.numlinks.emm.condition))


plot(pairs(layout.numlinks.emm.data))
plot(pairs(layout.numlinks.emm.data), comparisons = TRUE)

layout.numlinks.emm.data.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.data.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.data.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.data.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.data.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.data.pairs$sig.levels <- factor(layout.numlinks.emm.data.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)


layout.numlinks.emm.data.pairs$contrast <- factor(layout.numlinks.emm.data.pairs$contrast, levels=layout.numlinks.emm.data.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

layout.numlinks.emm.data.pairs <- layout.numlinks.emm.data.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.numlinks.emm.data.pairs %>% arrange(estimate)

ggplot(layout.numlinks.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.numlinks.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

data.copy <- layout.numlinks.emm.data.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.data.pairs.compl <- bind_rows(layout.numlinks.emm.data.pairs, data.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#layout.numlinks.emm.data.pairs.compl$From <- factor(layout.numlinks.emm.data.pairs.compl$From, levels=cond.lev)
#layout.numlinks.emm.data.pairs.compl$To <- factor(layout.numlinks.emm.data.pairs.compl$To, levels=cond.lev)

layout.numlinks.emm.data.pairs.compl$From <- factor(layout.numlinks.emm.data.pairs.compl$From, levels=rev(unique(layout.numlinks.emm.data.pairs.compl$From)))

#layout.numlinks.emm.data.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.data.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
    scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")


```

##### Underestimated

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numhighdeg, table(Dataset,Overestimated))
# ref_grid(layout.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

layout.numlinks.emm.under <- emmeans(layout.numlinks.lmer.full.int.3, "Underestimated", nesting = NULL)
#layout.numlinks.emm.condition <- emmeans(layout.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

layout.numlinks.emm.under

layout.numlinks.emm.under.df <- dplyr::as_data_frame(layout.numlinks.emm.under)

layout.numlinks.emm.under.df


# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numlinks.emm.condition)

layout.numlinks.emm.under.cld <- cld(layout.numlinks.emm.under,
                details=TRUE,
                #alpha=0.01,
                #by="Dataset",
                #Letters="|||||||||||||||||||",
                sort=TRUE
)

layout.numlinks.emm.under.cld.df <- layout.numlinks.emm.under.cld$emmeans

layout.numlinks.emm.under.cld.df %>% dplyr::select(Underestimated,.group)

layout.numlinks.emm.under.cld.df

layout.numlinks.emm.under.cld.df$Underestimated <- factor(layout.numlinks.emm.under.cld.df$Underestimated, levels=layout.numlinks.emm.under.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Underestimated) %>% unlist())


#emmip(layout.numlinks.lmer.full.int, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.under, ~Underestimated, CIs = TRUE)
plot(layout.numlinks.emm.under)
#plot(layout.numlinks.emm.cond, comparisons = TRUE)

layout.numlinks.emm.under.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.under.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Underestimated,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Underestimated,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()


#plot(ref_grid(layout.numnodes.lmer.int.3), by="Condition") 
# try to figure this out? maybe only works on the interaction?
```

```{r}

layout.numlinks.emm.under.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.under)) 
layout.numlinks.emm.under.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

pairs.CI <- confint(pairs(layout.numlinks.emm.under))

layout.numlinks.emm.under.pairs <- full_join(layout.numlinks.emm.under.pairs, pairs.CI)

#layout.numhd.diffemm.condition <- emmeans(layout.numhd.lmer.full.int.4, pairwise ~ Condition)
#layout.numhd.diffemm.condition$contrasts
#contrast(layout.numlinks.emm.condition)
#confint(layout.numlinks.emm.condition)
#pairs(layout.numlinks.emm.condition, details=TRUE)
#confint(contrast(layout.numlinks.emm.condition))
#confint(pairs(layout.numlinks.emm.condition))
#coef(pairs(layout.numlinks.emm.condition))


plot(pairs(layout.numlinks.emm.under))
plot(pairs(layout.numlinks.emm.under), comparisons = TRUE)

layout.numlinks.emm.under.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.under.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.under.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.under.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.under.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.under.pairs$sig.levels <- factor(layout.numlinks.emm.under.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)


layout.numlinks.emm.under.pairs$contrast <- factor(layout.numlinks.emm.under.pairs$contrast, levels=layout.numlinks.emm.under.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

layout.numlinks.emm.under.pairs <- layout.numlinks.emm.under.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.numlinks.emm.under.pairs %>% arrange(estimate)

ggplot(layout.numlinks.emm.under.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.numlinks.emm.under.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

data.copy <- layout.numlinks.emm.under.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.under.pairs.compl <- bind_rows(layout.numlinks.emm.under.pairs, data.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#layout.numlinks.emm.data.pairs.compl$From <- factor(layout.numlinks.emm.data.pairs.compl$From, levels=cond.lev)
#layout.numlinks.emm.data.pairs.compl$To <- factor(layout.numlinks.emm.data.pairs.compl$To, levels=cond.lev)

layout.numlinks.emm.under.pairs.compl$From <- factor(layout.numlinks.emm.under.pairs.compl$From, levels=rev(unique(layout.numlinks.emm.under.pairs.compl$From)))

#layout.numlinks.emm.data.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.under.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.under.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.under.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.under.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
    scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.numlinks.emm.under.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")


```

##### Condition:Dataset

###### emmeans

```{r}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numnodes, table(Dataset,Underestimated))
# ref_grid(layout.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#layout.numnodes.emm.cond <- emmeans(layout.numnodes.lmer.int.3, "Condition", nesting = NULL)
layout.numlinks.emm.conddata <- emmeans(layout.numlinks.lmer.full.int.3, ~ Dataset | Condition, nesting = NULL)
layout.numlinks.emm.conddata.2 <- emmeans(layout.numlinks.lmer.full.int.3, ~ Condition | Dataset, nesting = NULL)

layout.numlinks.emm.conddata

#layout.numnodes.diffemm.conddata <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#layout.numnodes.diffemm.conddata

layout.numlinks.emm.conddata.df <- dplyr::as_data_frame(layout.numlinks.emm.conddata)

layout.numlinks.emm.conddata.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numlinks.emm.condition)

layout.numlinks.emm.conddata.cld <- cld(layout.numlinks.emm.conddata,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

layout.numlinks.emm.conddata.cld[["emmeans"]]


layout.numlinks.emm.conddata.cld.df <- layout.numlinks.emm.conddata.cld[["emmeans"]]

layout.numlinks.emm.conddata.cld.df %>% dplyr::select(Dataset,Condition,.group) %>% print()

cld(layout.numlinks.emm.conddata.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(Dataset,Condition,.group) %>% print()

# TO DO : get this to print as single table

#layout.numnodes.emm.conddata.cld.df$Condition <- factor(layout.numnodes.emm.conddata.cld.df$Condition, levels=layout.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(layout.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.conddata, ~Condition|Dataset, CIs = TRUE)
plot(layout.numlinks.emm.conddata)
#plot(layout.numnodes.emm.conddata, comparisons = TRUE)

layout.numlinks.emm.conddata.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.conddata.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=Condition,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Dataset) + 
  coord_flip()

ggplot(layout.numlinks.emm.conddata.cld.df) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL, color=Condition), width=.2, position=position_dodge(width=0.2)) +
  geom_point(aes(x=Dataset,y=emmean, color=Condition), position=position_dodge(width=0.2)) +
  geom_line(aes(x=Dataset,y=emmean, color=Condition, group=Condition), position=position_dodge(width=0.2)) +
  #scale_color_manual(labels=c("Blue","Black"),values=c("steelblue","black"), name="Node Color") +
  #scale_color_discrete(labels=c("Control","Color","Phrasing","Size")) +
  labs(title="Estimated Marginal Means for Condition vs. Dataset for\nNumber of Links task, layout conditions")


```

```{r}

layout.numlinks.emm.conddata.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.conddata)) 
layout.numlinks.emm.conddata.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

conddata.pairs.CI <- confint(pairs(layout.numlinks.emm.conddata))

layout.numlinks.emm.conddata.pairs <- full_join(layout.numlinks.emm.conddata.pairs, conddata.pairs.CI)

#layout.numnodes.diffemm.cond <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Condition)
#layout.numnodes.diffemm.cond$contrasts
#contrast(layout.numnodes.emm.cond)
#confint(layout.numnodes.emm.cond)
#pairs(layout.numnodes.emm.cond, details=TRUE)
#confint(contrast(layout.numnodes.emm.cond))
#confint(pairs(layout.numnodes.emm.cond))
#coef(pairs(layout.numnodes.emm.cond))

plot(pairs(layout.numlinks.emm.conddata))
plot(pairs(layout.numlinks.emm.conddata), comparisons = TRUE)

layout.numlinks.emm.conddata.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.conddata.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.conddata.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.conddata.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.conddata.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.conddata.pairs$sig.levels <- factor(layout.numlinks.emm.conddata.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

layout.numlinks.emm.conddata.pairs$contrast.cond <- paste0(layout.numlinks.emm.conddata.pairs$contrast,layout.numlinks.emm.conddata.pairs$Condition)

layout.numlinks.emm.conddata.pairs$contrast.cond <- factor(layout.numlinks.emm.conddata.pairs$contrast.cond, levels=layout.numlinks.emm.conddata.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.cond) %>% distinct() %>% unlist())

#layout.numlinks.emm.conddata.pairs %>% View()

layout.numlinks.emm.conddata.pairs$contrast <- 
  factor(as.character(layout.numlinks.emm.conddata.pairs$contrast), 
         levels=layout.numlinks.emm.conddata.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


layout.numlinks.emm.conddata.pairs <- layout.numlinks.emm.conddata.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.numlinks.emm.conddata.pairs %>% arrange(estimate)
#layout.numlinks.emm.conddata.pairs %>% View()

ggplot(layout.numlinks.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast.cond,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast.cond,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()


ggplot(layout.numlinks.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.conddata.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Condition, scales="free_y") +
  coord_flip()

```

```{r}

conddata.copy <- layout.numlinks.emm.conddata.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.conddata.pairs.compl <- bind_rows(layout.numlinks.emm.conddata.pairs, conddata.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#layout.numnodes.emm.conddata.pairs.compl$From <- factor(layout.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#layout.numnodes.emm.conddata.pairs.compl$To <- factor(layout.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

layout.numlinks.emm.conddata.pairs.compl$From <- factor(layout.numlinks.emm.conddata.pairs.compl$From, levels=c(9,7,1))


#layout.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.conddata.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.conddata.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(layout.numlinks.emm.conddata.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(layout.numlinks.emm.conddata.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)

ggplot(layout.numlinks.emm.conddata.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Condition)


```

##### Condition:Underestimated

###### emmeans


```{r}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numnodes, table(Dataset,Underestimated))
# ref_grid(layout.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#layout.numnodes.emm.cond <- emmeans(layout.numnodes.lmer.int.3, "Condition", nesting = NULL)
layout.numlinks.emm.condunder <- emmeans(layout.numlinks.lmer.full.int.3, ~ Condition | Underestimated, nesting = NULL)
layout.numlinks.emm.condunder.2 <- emmeans(layout.numlinks.lmer.full.int.3, ~ Underestimated | Condition, nesting = NULL)


layout.numlinks.emm.condunder

#layout.numnodes.diffemm.conddata <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#layout.numnodes.diffemm.conddata

layout.numlinks.emm.condunder.df <- dplyr::as_data_frame(layout.numlinks.emm.condunder)

layout.numlinks.emm.condunder.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numlinks.emm.condition)

layout.numlinks.emm.condunder.cld <- cld(layout.numlinks.emm.condunder,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

layout.numlinks.emm.condunder.cld[["emmeans"]]


layout.numlinks.emm.condunder.cld.df <- layout.numlinks.emm.condunder.cld[["emmeans"]]

layout.numlinks.emm.condunder.cld.df %>% dplyr::select(Condition,Underestimated,.group) %>% print()
cld(layout.numlinks.emm.condunder.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(Condition,Underestimated,.group) %>% print()


# TO DO : get this to print as single table

#layout.numnodes.emm.conddata.cld.df$Condition <- factor(layout.numnodes.emm.conddata.cld.df$Condition, levels=layout.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(layout.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.condunder, ~Condition|Underestimated, CIs = TRUE)
plot(layout.numlinks.emm.condunder)
#plot(layout.numnodes.emm.conddata, comparisons = TRUE)

layout.numlinks.emm.condunder.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.condunder.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=Condition,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated) + 
  coord_flip()

ggplot(layout.numlinks.emm.condunder.cld.df) +
  geom_errorbar(aes(x=Condition,ymax=upper.CL,ymin=lower.CL, color=Underestimated), width=.2, position="dodge") +
  geom_point(aes(x=Condition,y=emmean,color=Underestimated),position=position_dodge(width=0.2)) +
  scale_color_discrete(labels=c("Overestimated","Underestimated")) +
  labs(title="Estimated Marginal Means for Condition vs. Underestimated for\nNumber of Links task, layout conditions")



```

```{r}

layout.numlinks.emm.condunder.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.condunder)) 
layout.numlinks.emm.condunder.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

condunder.pairs.CI <- confint(pairs(layout.numlinks.emm.condunder))

layout.numlinks.emm.condunder.pairs <- full_join(layout.numlinks.emm.condunder.pairs, condunder.pairs.CI)

#layout.numnodes.diffemm.cond <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Condition)
#layout.numnodes.diffemm.cond$contrasts
#contrast(layout.numnodes.emm.cond)
#confint(layout.numnodes.emm.cond)
#pairs(layout.numnodes.emm.cond, details=TRUE)
#confint(contrast(layout.numnodes.emm.cond))
#confint(pairs(layout.numnodes.emm.cond))
#coef(pairs(layout.numnodes.emm.cond))

plot(pairs(layout.numlinks.emm.condunder))
plot(pairs(layout.numlinks.emm.condunder), comparisons = TRUE)

layout.numlinks.emm.condunder.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.condunder.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.condunder.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.condunder.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.condunder.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.condunder.pairs$sig.levels <- factor(layout.numlinks.emm.condunder.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

layout.numlinks.emm.condunder.pairs$contrast.all <- paste0(layout.numlinks.emm.condunder.pairs$contrast,layout.numlinks.emm.condunder.pairs$Underestimated)

layout.numlinks.emm.condunder.pairs$contrast.all <- factor(layout.numlinks.emm.condunder.pairs$contrast.all, levels=layout.numlinks.emm.condunder.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.all) %>% distinct() %>% unlist())

#layout.numlinks.emm.conddata.pairs %>% View()

layout.numlinks.emm.condunder.pairs$contrast <- 
  factor(as.character(layout.numlinks.emm.condunder.pairs$contrast), 
         levels=layout.numlinks.emm.condunder.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


layout.numlinks.emm.condunder.pairs <- layout.numlinks.emm.condunder.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.numlinks.emm.condunder.pairs %>% arrange(estimate)
#layout.numlinks.emm.conddata.pairs %>% View()

ggplot(layout.numlinks.emm.condunder.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.condunder.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()


ggplot(layout.numlinks.emm.condunder.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.condunder.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

```

```{r}

condunder.copy <- layout.numlinks.emm.condunder.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.condunder.pairs.compl <- bind_rows(layout.numlinks.emm.condunder.pairs, condunder.copy)


cond.lev <- c("Ctrl","Cir","Fru","Ord")

layout.numlinks.emm.condunder.pairs.compl$From <- factor(layout.numlinks.emm.condunder.pairs.compl$From, levels=rev(cond.lev))
layout.numlinks.emm.condunder.pairs.compl$To <- factor(layout.numlinks.emm.condunder.pairs.compl$To, levels=cond.lev)



#layout.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.condunder.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.condunder.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.condunder.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.condunder.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.condunder.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)


```


##### Dataset:Underestimated

###### emmeans

```{r, eval=FALSE}

# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numnodes, table(Dataset,Underestimated))
# ref_grid(layout.numnodes.lmer.int.5) @ grid; .wgt. is number of observations

# See also: https://cran.r-project.org/web/packages/emmeans/vignettes/interactions.html

#layout.numnodes.emm.cond <- emmeans(layout.numnodes.lmer.int.3, "Condition", nesting = NULL)
layout.numlinks.emm.dataunder <- emmeans(layout.numlinks.lmer.full.int.3, ~ Dataset | Underestimated, nesting = NULL)
layout.numlinks.emm.dataunder.2 <- emmeans(layout.numlinks.lmer.full.int.3, ~ Underestimated | Dataset, nesting = NULL)

layout.numlinks.emm.dataunder

#layout.numnodes.diffemm.conddata <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Dataset | Condition, nesting = NULL)

#layout.numnodes.diffemm.conddata

layout.numlinks.emm.dataunder.df <- dplyr::as_data_frame(layout.numlinks.emm.dataunder)

layout.numlinks.emm.dataunder.df #%>% View()

# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numlinks.emm.condition)

layout.numlinks.emm.dataunder.cld <- cld(layout.numlinks.emm.dataunder,
                                       details=TRUE,
                                       #alpha=0.01,
                                       #by="Dataset",
                                       #Letters="|||||||||||||||||||",
                                       sort=TRUE
)

layout.numlinks.emm.dataunder.cld[["emmeans"]]


layout.numlinks.emm.dataunder.cld.df <- layout.numlinks.emm.dataunder.cld[["emmeans"]]

layout.numlinks.emm.dataunder.cld.df %>% dplyr::select(Dataset,Underestimated,.group) %>% print()

cld(layout.numlinks.emm.dataunder.2, details=TRUE, sort=TRUE)[["emmeans"]] %>% dplyr::select(Dataset,Underestimated,.group) %>% print()


# TO DO : get this to print as single table

#layout.numnodes.emm.conddata.cld.df$Condition <- factor(layout.numnodes.emm.conddata.cld.df$Condition, levels=layout.numnodes.emm.conddata.cld %>% arrange(desc(emmean)) %>% dplyr::select(Condition) %>% unlist())

#emmip(layout.numnodes.lmer.int.3, ~Condition, CIs = TRUE)
emmip(layout.numlinks.emm.dataunder, ~Dataset|Underestimated, CIs = TRUE)
plot(layout.numlinks.emm.dataunder)
#plot(layout.numnodes.emm.conddata, comparisons = TRUE)

layout.numlinks.emm.dataunder.cld.df %>% arrange(desc(emmean))

ggplot(layout.numlinks.emm.dataunder.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  #geom_point(aes(x=Condition,y=emmean), size=7) +
  geom_point(aes(x=Dataset,y=emmean)) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated) + 
  coord_flip()

ggplot(layout.numlinks.emm.dataunder.cld.df) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL, color=Underestimated), width=.2, position="dodge") +
  geom_point(aes(x=Dataset,y=emmean, color=Underestimated), position=position_dodge(width=0.2)) +
  geom_line(aes(x=Dataset,y=emmean, color=Underestimated, group=Underestimated), position=position_dodge(width=0.2)) +
  scale_color_discrete(labels=c("Overestimated","Underestimated")) +
  labs(title="Estimated Marginal Means for Dataset vs. Underestimated for\nNumber of Links task, layout conditions")


```

```{r, eval=FALSE}

layout.numlinks.emm.dataunder.pairs <- dplyr::as_data_frame(pairs(layout.numlinks.emm.dataunder)) 
layout.numlinks.emm.dataunder.pairs #%>% View()
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numlinks.emm.condition) has both negative and positive estimates
# and joins better to confint()

dataunder.pairs.CI <- confint(pairs(layout.numlinks.emm.dataunder))

layout.numlinks.emm.dataunder.pairs <- full_join(layout.numlinks.emm.dataunder.pairs, dataunder.pairs.CI)

#layout.numnodes.diffemm.cond <- emmeans(layout.numnodes.lmer.int.3, pairwise ~ Condition)
#layout.numnodes.diffemm.cond$contrasts
#contrast(layout.numnodes.emm.cond)
#confint(layout.numnodes.emm.cond)
#pairs(layout.numnodes.emm.cond, details=TRUE)
#confint(contrast(layout.numnodes.emm.cond))
#confint(pairs(layout.numnodes.emm.cond))
#coef(pairs(layout.numnodes.emm.cond))

plot(pairs(layout.numlinks.emm.dataunder))
plot(pairs(layout.numlinks.emm.dataunder), comparisons = TRUE)

layout.numlinks.emm.dataunder.pairs$sig.levels <- 
  case_when(layout.numlinks.emm.dataunder.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.numlinks.emm.dataunder.pairs$p.value < .001 ~ sig.level.names[2],
            layout.numlinks.emm.dataunder.pairs$p.value < .01 ~ sig.level.names[3],
            layout.numlinks.emm.dataunder.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.numlinks.emm.dataunder.pairs$sig.levels <- factor(layout.numlinks.emm.dataunder.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)

layout.numlinks.emm.dataunder.pairs$contrast.all <- paste0(layout.numlinks.emm.dataunder.pairs$contrast,layout.numlinks.emm.dataunder.pairs$Underestimated)

layout.numlinks.emm.dataunder.pairs$contrast.all <- factor(layout.numlinks.emm.dataunder.pairs$contrast.all, levels=layout.numlinks.emm.dataunder.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast.all) %>% distinct() %>% unlist())

#layout.numlinks.emm.conddata.pairs %>% View()

layout.numlinks.emm.dataunder.pairs$contrast <- 
  factor(as.character(layout.numlinks.emm.dataunder.pairs$contrast), 
         levels=layout.numlinks.emm.dataunder.pairs %>% group_by(contrast) %>% summarise(avgEst = mean(estimate)) %>% arrange(desc(avgEst)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())


layout.numlinks.emm.dataunder.pairs <- layout.numlinks.emm.dataunder.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.numlinks.emm.dataunder.pairs %>% arrange(estimate)
#layout.numlinks.emm.conddata.pairs %>% View()

ggplot(layout.numlinks.emm.dataunder.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.dataunder.pairs) +
  geom_errorbar(aes(x=contrast.all,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast.cond,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast.all,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()


ggplot(layout.numlinks.emm.dataunder.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

ggplot(layout.numlinks.emm.dataunder.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  #geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  facet_wrap(~Underestimated, scales="free_y") +
  coord_flip()

```

```{r, eval=FALSE}

dataunder.copy <- layout.numlinks.emm.dataunder.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.numlinks.emm.dataunder.pairs.compl <- bind_rows(layout.numlinks.emm.dataunder.pairs, dataunder.copy)


#cond.lev <- c("Ctrl","Phr","Col","Siz")

#layout.numnodes.emm.conddata.pairs.compl$From <- factor(layout.numnodes.emm.conddata.pairs.compl$From, levels=cond.lev)
#layout.numnodes.emm.conddata.pairs.compl$To <- factor(layout.numnodes.emm.conddata.pairs.compl$To, levels=cond.lev)

layout.numlinks.emm.dataunder.pairs.compl$From <- factor(layout.numlinks.emm.dataunder.pairs.compl$From, levels=c(9,7,1))


#layout.numlinks.emm.conddata.pairs.compl %>% arrange(desc(estimate))
layout.numlinks.emm.dataunder.pairs.compl %>% arrange(estimate)

ggplot(layout.numlinks.emm.dataunder.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.dataunder.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.dataunder.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
  scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)

ggplot(layout.numlinks.emm.dataunder.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From") +
  facet_wrap(~Underestimated)


```


