---
title: "Analysis for Average Degree task, Layout conditions"
author: "Angela Zoss"
date: "March 25, 2018"
output: github_document
---

```{r layout-setup-avgdeg}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r layout-load-environment-avgdeg, message=FALSE}

source('LayoutSetup.R')

```

#### lme4

```{r, cache=TRUE, eval=FALSE}

# Condition

layout.avgdeg.lmer <- lmer(LogError ~ Condition + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Condition is not significant; trying Ctrl_dummy

layout.avgdeg.lmer <- lmer(LogError ~ Ctrl_dummy + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Ctrl_dummy is not significant; trying Dataset

layout.avgdeg.lmer.data <- lmer(LogError ~ Dataset + (1|Demo.ResponseID), data = layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.data)

anova(layout.avgdeg.lmer.data)

# Dataset is barely significant (p=0.02879)

#layout.avgdeg.lmer <- lmer(LogError ~ QuestionOrder + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

layouts_avgdeg.CS <- layouts_avgdeg %>% mutate(QuestionOrder=scale(QuestionOrder))

layout.avgdeg.lmer <- lmer(LogError ~ QuestionOrder + (1|Demo.ResponseID), data=layouts_avgdeg.CS, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# QuestionOrder is not significant

layout.avgdeg.lmer <- lmer(LogError ~ DatasetOrder + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# DatasetOrder is not significant

layout.avgdeg.lmer <- lmer(LogError ~ DatasetDuration + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# DatasetDuration is not significant

layout.avgdeg.lmer <- lmer(LogError ~ DatasetStartTime + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# DatasetStartTime is not significant; trying TaskOrder

layout.avgdeg.lmer <- lmer(LogError ~ TaskOrder + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# TaskOrder is not significant; trying CorrectAnswer

layout.avgdeg.lmer.correct <- lmer(LogError ~ CorrectAnswer + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.correct)

anova(layout.avgdeg.lmer.correct)

# CorrectAnswer is barely significant (p=0.03933)

layout.avgdeg.lmer.underest <- lmer(LogError ~ Underestimated + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.underest)

anova(layout.avgdeg.lmer.underest)

# Underestimated is highly significant (p = 1.432e-12)

layout.avgdeg.lmer <- lmer(LogError ~ Stats.Q_TotalDuration + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Stats.Q_TotalDuration is not significant; trying Stats.dataset_count

layout.avgdeg.lmer <- lmer(LogError ~ Stats.dataset_count + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Stats.dataset_count is not significant; trying Stats.OperatingSystem

layout.avgdeg.lmer <- lmer(LogError ~ Stats.OperatingSystem + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Stats.OperatingSystem is not significant

layout.avgdeg.lmer <- lmer(LogError ~ Stats.OperatingSystemCombined + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Stats.OperatingSystemCombined is not significant

layouts_avgdeg.CS <- layouts_avgdeg %>% mutate(StatsNumPixels=scale(StatsNumPixels))

layout.avgdeg.lmer <- lmer(LogError ~ StatsNumPixels + (1|Demo.ResponseID), data=layouts_avgdeg.CS, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# StatsNumPixels is not significant; trying Demo.age

layout.avgdeg.lmer <- lmer(LogError ~ Demo.age + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.age))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.age is not significant; trying Demo.gender

layout.avgdeg.lmer <- lmer(LogError ~ Demo.gender + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.gender))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.gender is not signficant; trying Demo.lang

layout.avgdeg.lmer <- lmer(LogError ~ Demo.lang + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.lang))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.lang is not signficant; trying Demo.educ

layout.avgdeg.lmer <- lmer(LogError ~ Demo.educ + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.educ))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.educ is not signficant; trying Demo.acfield

layout.avgdeg.lmer <- lmer(LogError ~ Demo.acfield + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.acfield))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.acfield is not signficant overall; trying Demo.acfieldGrouped

layout.avgdeg.lmer <- lmer(LogError ~ Demo.acfieldGrouped + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.acfieldGrouped))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.acfieldGrouped is not significant

layout.avgdeg.lmer <- lmer(LogError ~ Demo.acfieldGrouped2 + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.acfieldGrouped2))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.acfieldGrouped2 is not significant

layout.avgdeg.lmer <- lmer(LogError ~ Demo.acfieldGrouped3 + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.acfieldGrouped3))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.acfieldGrouped3 is not significant

layout.avgdeg.lmer.comp <- lmer(LogError ~ Demo.dailytech_Computer + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.dailytech_Computer))), REML = T)

summary(layout.avgdeg.lmer.comp)

anova(layout.avgdeg.lmer.comp)

# Demo.dailytech_Computer is significant (p=0.006587); trying Demo.dailytech_Tablet

layout.avgdeg.lmer <- lmer(LogError ~ Demo.dailytech_Tablet + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.dailytech_Tablet))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.dailytech_Computer is not significant

layout.avgdeg.lmer.SP <- lmer(LogError ~ Demo.dailytech_SmartPhone + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.dailytech_SmartPhone))), REML = T)

summary(layout.avgdeg.lmer.SP)

anova(layout.avgdeg.lmer.SP)

# Demo.dailytech_SmartPhone is barely significant (p=0.03045)

layout.avgdeg.lmer <- lmer(LogError ~ Demo.weeklygaming + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.weeklygaming))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.weeklygaming is not significant; trying Demo.expdataanal

layout.avgdeg.lmer <- lmer(LogError ~ Demo.expdataanal + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.expdataanal))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.expdataanal is not significant; trying Demo.expdatavis

layout.avgdeg.lmer <- lmer(LogError ~ Demo.expdatavis + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.expdatavis))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.expdatavis is not significant; trying Demo.expreadnetvis

layout.avgdeg.lmer <- lmer(LogError ~ Demo.expreadnetvis + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.expreadnetvis))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.expreadnetvis is not significant

layout.avgdeg.lmer <- lmer(LogError ~ Demo.expcreatenetvis + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(!(is.na(Demo.expcreatenetvis))), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Demo.expcreatenetvis is not significant; trying AvgDeg

layout.avgdeg.lmer.avgdeg <- lmer(LogError ~ AvgDeg + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.avgdeg)

anova(layout.avgdeg.lmer.avgdeg)

# AvgDeg is significant (p=0.03933)

layout.avgdeg.lmer <- lmer(LogError ~ Density + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Density is barely not significant (p=0.05856)

layout.avgdeg.lmer.lgclust <- lmer(LogError ~ LargeClust1 + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.lgclust)

anova(layout.avgdeg.lmer.lgclust)

# LargeClust1 is barely significant (p=0.04142)

layout.avgdeg.lmer.mod <- lmer(LogError ~ Modularity + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.mod)

anova(layout.avgdeg.lmer.mod)

# Modularity is barely significant (p=0.03925)

layout.avgdeg.lmer.nclust <- lmer(LogError ~ NumClust + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.nclust)

anova(layout.avgdeg.lmer.nclust)

# NumClust is significant (p=0.00886)

layout.avgdeg.lmer <- lmer(LogError ~ NumHighDegree + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# NumHighDegree is not significant

layout.avgdeg.lmer <- lmer(LogError ~ NumLinks + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# NumLinks is barely not significant

layout.avgdeg.lmer.numnodes <- lmer(LogError ~ NumNodes + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.numnodes)

anova(layout.avgdeg.lmer.numnodes)

# NumNodes is barely significant (p=0.01815)

layout.avgdeg.lmer.numnodesclust1 <- lmer(LogError ~ NumNodesClust1 + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer.numnodesclust1)

anova(layout.avgdeg.lmer.numnodesclust1)

# NumNodesClust1 is barely significant (p=0.04227)

layout.avgdeg.lmer <- lmer(LogError ~ filename + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# filename is not significant

layout.avgdeg.lmer <- lmer(LogError ~ NetVisExperience + (1|Demo.ResponseID), data=layouts_avgdeg, REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# NetVisExperience is not significant

layout.avgdeg.lmer <- lmer(LogError ~ Stats.CompensationCondition + (1|Demo.ResponseID), data=layouts_avgdeg %>% filter(filename=="FacultyGrad"), REML = T)

summary(layout.avgdeg.lmer)

anova(layout.avgdeg.lmer)

# Stats.CompensationCondition is not significant


```


```{r}

temp.avgdeg <- layouts_avgdeg %>% dplyr::select(Demo.ResponseID, LogError, Dataset, CorrectAnswer, Underestimated, Demo.dailytech_Computer, Demo.dailytech_SmartPhone, AvgDeg, LargeClust1, Modularity, NumClust, NumNodes, NumNodesClust1) %>% drop_na()

layout.avgdeg.lmer.full <- lmer(LogError ~ Dataset + Underestimated + Demo.dailytech_Computer + (1|Demo.ResponseID), data=temp.avgdeg, REML = T)

summary(layout.avgdeg.lmer.full)

anova(layout.avgdeg.lmer.full)

layout.avgdeg.lmer.underest <- lmer(LogError ~ Underestimated + (1|Demo.ResponseID), data=temp.avgdeg, REML = T)

anova(layout.avgdeg.lmer.full, layout.avgdeg.lmer.underest)
# keep full
```

```{r}
layout.avgdeg.lmer.int <- lmer(LogError ~ Dataset + 
                                 Underestimated + 
                                 Demo.dailytech_Computer + 
                                 Dataset:Demo.dailytech_Computer +
                                 (1|Demo.ResponseID), data=temp.avgdeg, REML = T)

summary(layout.avgdeg.lmer.int)

anova(layout.avgdeg.lmer.int)

anova(layout.avgdeg.lmer.full, layout.avgdeg.lmer.int)
# interaction barely significantly better

layout.avgdeg.lmer.int.2 <- lmer(LogError ~ Dataset + 
                                 Underestimated + 
                                 Demo.dailytech_Computer + 
                                 Dataset:Demo.dailytech_Computer +
                                   Underestimated:Demo.dailytech_Computer +
                                 (1|Demo.ResponseID), data=temp.avgdeg, REML = T)

summary(layout.avgdeg.lmer.int.2)

anova(layout.avgdeg.lmer.int.2)

anova(layout.avgdeg.lmer.full, layout.avgdeg.lmer.int.2) # definitely better than full
anova(layout.avgdeg.lmer.int, layout.avgdeg.lmer.int.2) # also better than previous interaction

#keep 2

```

```{r}

#SAVE THE RESULTS
save(layout.avgdeg.lmer.int.2, file = file.path(analysisDataDir,"fits/layout_avgdeg_lmer_int.RData"))

```

```{r, cache=TRUE}

rand(layout.avgdeg.lmer.int.2)

# result shows that random effects of participant are significant (p=2e-10)

anova(layout.avgdeg.lmer.int.2)

#ranef(layout.avgdeg.lmer.full)

# displays the random effects; not that useful

# unlike lme(), lmer() doesn't allow for heterogeneous error variance structures (the "weights")

ggplot(layouts_avgdeg) + geom_histogram(aes(LogError), binwidth=.005) + labs(title="Distribution of LogError values for Average Degree task,\nlayout conditions")

(r2nsj = r2beta(layout.avgdeg.lmer.int.2, method = 'nsj', partial = TRUE))
(r2nsj = r2beta(layout.avgdeg.lmer.int.2, method = 'nsj', partial = TRUE))[1,'Rsq']



```

```{r, eval=FALSE}

plot(layout.avgdeg.lmer.int.2)

plot(layout.avgdeg.lmer.int.2, resid(., scaled=TRUE) ~ fitted(.), abline = 0)

plot(layout.avgdeg.lmer.int.2, resid(.) ~ fitted(.) | Underestimated, abline = 0)

plot(layout.avgdeg.lmer.int.2, resid(., scaled=TRUE) ~ fitted(.) | Underestimated, abline = 0)

plot(layout.avgdeg.lmer.int.2, LogError ~ fitted(.), abline = c(0,1))



```

```{r}

layout.avgdeg.lmer.int.2.f <- fortify(layout.avgdeg.lmer.int.2)

ggplot(layout.avgdeg.lmer.int.2.f, aes(.fitted,.resid)) + 
  geom_point() +
  #facet_grid(.~Sex) + 
  geom_hline(yintercept=0)

ggplot(layout.avgdeg.lmer.int.2.f, aes(.fitted,LogError)) + 
  geom_point() +
  geom_abline(aes(slope = 1, intercept = 0))

ggplot(layout.avgdeg.lmer.int.2.f, aes(LogError,.fitted)) + 
  geom_point() +
  geom_abline(aes(slope = 1, intercept = 0)) +
  #scale_y_continuous(limits=c(0,0.3)) +
  labs(title="Real vs. Predicted LogError values for Average Degree task,\nlayout conditions")



```


#### Least Squares Means

Do for each categorical predictor. 
Final model: 
layout.avgdeg.lmer.int.2 <- lmer(LogError ~ Dataset + 
                                 Underestimated + 
                                 Demo.dailytech_Computer + 
                                 Dataset:Demo.dailytech_Computer +
                                 Underestimated:Demo.dailytech_Computer +
                                 (1|Demo.ResponseID), data=temp.avgdeg, REML = T)

##### Dataset

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numhighdeg, table(Dataset,Overestimated))
# ref_grid(layout.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

layout.avgdeg.emm.data <- emmeans(layout.avgdeg.lmer.int.2, "Dataset", nesting = NULL)
#layout.numhd.emm.condition <- emmeans(layout.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

layout.avgdeg.emm.data

layout.avgdeg.emm.data.df <- dplyr::as_data_frame(layout.avgdeg.emm.data)

layout.avgdeg.emm.data.df


# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numhd.emm.condition)

layout.avgdeg.emm.data.cld <- cld(layout.avgdeg.emm.data,
                details=TRUE,
                #alpha=0.01,
                #by="Dataset",
                #Letters="|||||||||||||||||||",
                sort=TRUE
)

layout.avgdeg.emm.data.cld.df <- layout.avgdeg.emm.data.cld$emmeans

layout.avgdeg.emm.data.cld.df %>% dplyr::select(Dataset,.group)

layout.avgdeg.emm.data.cld.df

layout.avgdeg.emm.data.cld.df$Dataset <- factor(layout.avgdeg.emm.data.cld.df$Dataset, levels=layout.avgdeg.emm.data.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Dataset) %>% unlist())


#emmip(layout.numlinks.lmer.full.int, ~Condition, CIs = TRUE)
emmip(layout.avgdeg.emm.data, ~Dataset, CIs = TRUE)
plot(layout.avgdeg.emm.data)
#plot(layout.numlinks.emm.cond, comparisons = TRUE)

layout.avgdeg.emm.data.cld.df %>% arrange(desc(emmean))

ggplot(layout.avgdeg.emm.data.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Dataset,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Dataset,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()


#plot(ref_grid(layout.numnodes.lmer.int.3), by="Condition") 
# try to figure this out? maybe only works on the interaction?
```

```{r}

layout.avgdeg.emm.data.pairs <- dplyr::as_data_frame(pairs(layout.avgdeg.emm.data)) 
layout.avgdeg.emm.data.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

pairs.CI <- confint(pairs(layout.avgdeg.emm.data))

layout.avgdeg.emm.data.pairs <- full_join(layout.avgdeg.emm.data.pairs, pairs.CI)

#layout.numhd.diffemm.condition <- emmeans(layout.numhd.lmer.full.int.4, pairwise ~ Condition)
#layout.numhd.diffemm.condition$contrasts
#contrast(layout.numhd.emm.condition)
#confint(layout.numhd.emm.condition)
#pairs(layout.numhd.emm.condition, details=TRUE)
#confint(contrast(layout.numhd.emm.condition))
#confint(pairs(layout.numhd.emm.condition))
#coef(pairs(layout.numhd.emm.condition))


plot(pairs(layout.avgdeg.emm.data))
plot(pairs(layout.avgdeg.emm.data), comparisons = TRUE)

layout.avgdeg.emm.data.pairs$sig.levels <- 
  case_when(layout.avgdeg.emm.data.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.avgdeg.emm.data.pairs$p.value < .001 ~ sig.level.names[2],
            layout.avgdeg.emm.data.pairs$p.value < .01 ~ sig.level.names[3],
            layout.avgdeg.emm.data.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.avgdeg.emm.data.pairs$sig.levels <- factor(layout.avgdeg.emm.data.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)


layout.avgdeg.emm.data.pairs$contrast <- factor(layout.avgdeg.emm.data.pairs$contrast, levels=layout.avgdeg.emm.data.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

layout.avgdeg.emm.data.pairs <- layout.avgdeg.emm.data.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.avgdeg.emm.data.pairs %>% arrange(estimate)

ggplot(layout.avgdeg.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.avgdeg.emm.data.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

copy <- layout.avgdeg.emm.data.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.avgdeg.emm.data.pairs.compl <- bind_rows(layout.avgdeg.emm.data.pairs, copy)

#cond.lev <- c("Ctrl","Phr","Col","Siz")

layout.avgdeg.emm.data.pairs.compl$From <- factor(layout.avgdeg.emm.data.pairs.compl$From, levels=rev(unique(layout.avgdeg.emm.data.pairs.compl$From)))
#layout.avgdeg.emm.under.pairs.compl$To <- factor(layout.avgdeg.emm.under.pairs.compl$To, levels=cond.lev)

#layout.numlinks.emm.cond.pairs.compl %>% arrange(desc(estimate))
layout.avgdeg.emm.data.pairs.compl %>% arrange(estimate)

ggplot(layout.avgdeg.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.data.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
    scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.data.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")


```

##### Underestimated

###### emmeans

```{r}
# trying to use emmeans package for lsmeans table

# can use ref_grid to see if emmeans is finding nestings within variables, which can cause problems(?)
# ref_grid(layout.numhd.lmer.full.int.4)
# unfortunately, considers Overestimated nested in Dataset because I didn't include 
# Overestimated as a fixed effect; can use nesting = NULL to ignore this auto-detection of nesting

# also want to check if any combination of two factors has zeroes in the cells
# with(layouts_numhighdeg, table(Dataset,Overestimated))
# ref_grid(layout.numhd.lmer.full.int.4) @ grid; .wgt. is number of observations

layout.avgdeg.emm.under <- emmeans(layout.avgdeg.lmer.int.2, "Underestimated", nesting = NULL)
#layout.numhd.emm.condition <- emmeans(layout.numhd.lmer.full.int.4, "Condition", lmer.df = "satterthwaite")

layout.avgdeg.emm.under

layout.avgdeg.emm.under.df <- dplyr::as_data_frame(layout.avgdeg.emm.under)

layout.avgdeg.emm.under.df


# From: https://cran.r-project.org/web/packages/emmeans/vignettes/comparisons.html
# The blue bars are confidence intervals for the EMMs, and the red arrows are for the comparisons among them. If an arrow from one mean overlaps an arrow from another group, the difference is not significant, based on the adjust setting (which defaults to "tukey"). (Note: Don’t ever use confidence intervals for EMMs to perform comparisons; they can be very misleading.)

# TO DO : can't figure out how to extract data about the arrows in order to reproduce the layout

#xtable::xtable(layout.numhd.emm.condition)

layout.avgdeg.emm.under.cld <- cld(layout.avgdeg.emm.under,
                details=TRUE,
                #alpha=0.01,
                #by="Dataset",
                #Letters="|||||||||||||||||||",
                sort=TRUE
)

layout.avgdeg.emm.under.cld.df <- layout.avgdeg.emm.under.cld$emmeans

layout.avgdeg.emm.under.cld.df %>% dplyr::select(Underestimated,.group)

layout.avgdeg.emm.under.cld.df

layout.avgdeg.emm.under.cld.df$Underestimated <- factor(layout.avgdeg.emm.under.cld.df$Underestimated, levels=layout.avgdeg.emm.under.cld.df %>% arrange(desc(emmean)) %>% dplyr::select(Underestimated) %>% unlist())


#emmip(layout.numlinks.lmer.full.int, ~Condition, CIs = TRUE)
emmip(layout.avgdeg.emm.under, ~Underestimated, CIs = TRUE)
plot(layout.avgdeg.emm.under)
#plot(layout.numlinks.emm.cond, comparisons = TRUE)

layout.avgdeg.emm.under.cld.df %>% arrange(desc(emmean))

ggplot(layout.avgdeg.emm.under.cld.df) +
  #geom_point(aes(x=Condition,y=emmean), shape=21, size=7) +
  geom_errorbar(aes(x=Underestimated,ymax=upper.CL,ymin=lower.CL), width=.2) +
  geom_point(aes(x=Underestimated,y=emmean), size=7) +
  #scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()


#plot(ref_grid(layout.numnodes.lmer.int.3), by="Condition") 
# try to figure this out? maybe only works on the interaction?
```

```{r}

layout.avgdeg.emm.under.pairs <- dplyr::as_data_frame(pairs(layout.avgdeg.emm.under)) 
layout.avgdeg.emm.under.pairs
# for some reason, full.cld$comparisons returns estimates that are all positive; 
# pairs(layout.numhd.emm.condition) has both negative and positive estimates
# and joins better to confint()

pairs.CI <- confint(pairs(layout.avgdeg.emm.under))

layout.avgdeg.emm.under.pairs <- full_join(layout.avgdeg.emm.under.pairs, pairs.CI)

#layout.numhd.diffemm.condition <- emmeans(layout.numhd.lmer.full.int.4, pairwise ~ Condition)
#layout.numhd.diffemm.condition$contrasts
#contrast(layout.numhd.emm.condition)
#confint(layout.numhd.emm.condition)
#pairs(layout.numhd.emm.condition, details=TRUE)
#confint(contrast(layout.numhd.emm.condition))
#confint(pairs(layout.numhd.emm.condition))
#coef(pairs(layout.numhd.emm.condition))


plot(pairs(layout.avgdeg.emm.under))
plot(pairs(layout.avgdeg.emm.under), comparisons = TRUE)

layout.avgdeg.emm.under.pairs$sig.levels <- 
  case_when(layout.avgdeg.emm.under.pairs$p.value < .0001 ~ sig.level.names[1],
            layout.avgdeg.emm.under.pairs$p.value < .001 ~ sig.level.names[2],
            layout.avgdeg.emm.under.pairs$p.value < .01 ~ sig.level.names[3],
            layout.avgdeg.emm.under.pairs$p.value < .05 ~ sig.level.names[4],
            TRUE ~ sig.level.names[5])

layout.avgdeg.emm.under.pairs$sig.levels <- factor(layout.avgdeg.emm.under.pairs$sig.levels, levels=sig.level.names,ordered=TRUE)


layout.avgdeg.emm.under.pairs$contrast <- factor(layout.avgdeg.emm.under.pairs$contrast, levels=layout.avgdeg.emm.under.pairs %>% arrange(desc(estimate)) %>% dplyr::select(contrast) %>% distinct() %>% unlist())

layout.avgdeg.emm.under.pairs <- layout.avgdeg.emm.under.pairs %>% separate(contrast, c("From", "del", "To"), sep="[ ]", remove=FALSE) %>% dplyr::select(-del)

layout.avgdeg.emm.under.pairs %>% arrange(estimate)

ggplot(layout.avgdeg.emm.under.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

ggplot(layout.avgdeg.emm.under.pairs) +
  geom_errorbar(aes(x=contrast,ymax=upper.CL,ymin=lower.CL), width=.5) +
  geom_point(aes(x=contrast,y=estimate, fill=sig.levels), shape=21, size=7) +
  geom_hline(aes(yintercept=0)) +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  coord_flip()

```

```{r}

copy <- layout.avgdeg.emm.under.pairs %>% rename(From=To,To=From) %>% 
  mutate(estimate=-estimate,
         t.ratio=-t.ratio,
         lower.CL=-lower.CL,
         upper.CL=-upper.CL)

layout.avgdeg.emm.under.pairs.compl <- bind_rows(layout.avgdeg.emm.under.pairs, copy)

#cond.lev <- c("Ctrl","Phr","Col","Siz")

layout.avgdeg.emm.under.pairs.compl$From <- factor(layout.avgdeg.emm.under.pairs.compl$From, levels=rev(unique(layout.avgdeg.emm.under.pairs.compl$From)))
#layout.avgdeg.emm.under.pairs.compl$To <- factor(layout.avgdeg.emm.under.pairs.compl$To, levels=cond.lev)

#layout.numlinks.emm.cond.pairs.compl %>% arrange(desc(estimate))
layout.avgdeg.emm.under.pairs.compl %>% arrange(estimate)

ggplot(layout.avgdeg.emm.under.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=sig.levels), color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.under.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=sig.levels), shape=21, color="black") +
  scale_fill_manual("Significance Levels", values=sig.colors) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.under.pairs.compl) +
  geom_tile(aes(x=To,y=From,fill=estimate)) +
    scale_fill_distiller(type="div", palette=4) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")

ggplot(layout.avgdeg.emm.under.pairs.compl) +
  geom_count(aes(x=To,y=From,size=abs(estimate),fill=estimate, color=p.value<.01), shape=21) +
  scale_fill_distiller(type="div", palette=4) +
  scale_color_manual(values=c("grey90","black")) +
  scale_x_discrete(drop=FALSE, position = "top") +
  scale_y_discrete(drop=FALSE, name="From")


```


##### Demo.dailytech_Computer - not a factor

```{r}

ggplot(temp.avgdeg) +
  geom_point(aes(Demo.dailytech_Computer,LogError)) +
  geom_smooth(aes(Demo.dailytech_Computer,LogError), method="lm")

```

##### Dataset:Demo.dailytech_Computer


```{r}

ggplot(temp.avgdeg) +
  geom_point(aes(Demo.dailytech_Computer,LogError)) +
  geom_smooth(aes(Demo.dailytech_Computer,LogError), method="lm") +
  facet_grid(.~Dataset)

```

##### Underestimated:Demo.dailytech_Computer

```{r}

ggplot(temp.avgdeg) +
  geom_point(aes(Demo.dailytech_Computer,LogError)) +
  geom_smooth(aes(Demo.dailytech_Computer,LogError), method="lm") +
  facet_grid(.~Underestimated)

```

