---
title: "Processing Combined NetVisLit Data"
author: "Angela Zoss"
date: "June 23, 2017"
output: github_document
---

Possible data processing steps:

* Having your software open your importable data files.
* Cleaning the data to resolve any errors or discrepancies.
* Removing variables or cases that you do not need. 
* Combining data from different importable data files.
* Transposing a data table so that columns become rows and rows become columns.
* Generating new variables
* Saving intermediate and analysis data files.

## Load packages

```{r}

require(tidyverse)
require(readxl)

```


## Environmental Variables

```{r}

originalDataDir <- "../../Original Data"
analysisDataDir <- "../../Analysis Data"

generatedDataDir <- file.path(originalDataDir, "Generated data")
path_to_qualtrics <- file.path(originalDataDir,"Raw data/Qualtrics data")
path_to_responses <- file.path(path_to_qualtrics,"responses")

```

## Loading raw data files

```{r, echo=FALSE}

# Make sure none of the files are open, or Excel will have a temp file in the same directory that messes this up

# names and rawdata files need the same basename to be matched up together

new_names <- dir(path = path_to_responses, pattern = "*.xlsx", full.names = TRUE) %>% 
  set_names(., sub("-new-names.xlsx","",basename(.))) %>%
  map(read_excel) %>% lapply(function(x){select(x, NewName)})
  #map_df(read_excel, .id="filename")

all_responses <- dir(path = path_to_responses, pattern = "*.csv", full.names = TRUE) %>% 
  set_names(., sub("-rawdata.csv","",basename(.))) %>%
  map(read_csv, skip=2, col_names=FALSE, col_types = cols(.default = "c"))

# hate using for loop, but can't figure out any other way to automate

for (file in names(all_responses)){
  nm <- unlist(new_names[[file]])
  all_responses[[file]] <- setNames(all_responses[[file]],nm)
}

raw_responses_full <- type_convert(bind_rows(all_responses, .id="filename"))


num_ans_lookup <- read_csv(file.path(generatedDataDir, "numerical_answer_lookup.csv"))

node_lookup <- read_csv(file.path(generatedDataDir, "node_lookup.csv"), col_types = cols(MaxValue = col_double(),NodeValue = col_double()))

all_nodes <- read_csv(file.path(generatedDataDir, "all_nodes.csv"))


block_ids <- read_tsv(file.path(path_to_qualtrics, "blockIDs.csv"))

population_experience <- read_csv(file.path(path_to_qualtrics,"population_experience.csv"))

training_task_order <- read_csv(file.path(path_to_qualtrics, "training_task_order.csv"))


```

## Process raw data

```{r}

# Remove bizarre R0 version of the ClickHighDeg question; 
# I must have defined a region of interest, but have no need for it

#raw_responses_full <- raw_responses_full %>% select(-contains("R0"),-contains("R1"))

raw_responses <- raw_responses_full %>% select(-contains("R0"),-contains("R1"))

# remove responses where the "Finished" flag is false

# TO DO: don't do this?  for faculty, may want to keep more data than this
# TO DO: figure out how to remove people not taking it seriously; look for error patterns?  
# short times? unreasonable clicks?

#raw_responses <- raw_responses %>% filter(`Extra-Finished`==1)

```


## Subset the experimental and training columns

```{r}

exp_responses <- dplyr::select(raw_responses, "Demo-ResponseID", starts_with("Exp"), starts_with("Training"))

exp_responses_tall <- gather(exp_responses, "Question", "Response", -1)

exp_responses_split <- separate(exp_responses_tall,Question,c("QType","Condition","Dataset","Task"),sep="[-]", convert=TRUE)

# remove unfortunate underscore in one of the tasks

exp_responses_split$Task <- sub("LargeClust_1","LargeClust1",exp_responses_split$Task)

#also separating click questions from coords, so the join with QuestionOrder data works better

exp_responses_split <- separate(exp_responses_split,Task,c("Task","Coord"),sep="[_]", convert=TRUE)

#exp_responses_split$Dataset <- as.numeric(exp_responses_split$Dataset)

# change skipped responses to NA

exp_responses_split$Response <- sub("-99",NA,exp_responses_split$Response)

# remove all NA responses

exp_responses_split <- exp_responses_split[!is.na(exp_responses_split$Response),]

# Save file out?

#write_csv(exp_responses_split, file.path(analysisDataDir,"ExperimentalResponses.csv"))

```

```{r}

# Omit anyone?

# 
#omit_IDs <- raw_responses_full %>% filter(`Stats-dataset_count` != 3) %>% select(`Demo-ResponseID`)

# testing for how many experimental tasks they *did* answer, because someone who answers none won't even show up in this query; picking 5 tasks as a somewhat arbitrary cutoff (it's at least half)

keep_IDs <- exp_responses_split %>% filter(QType == "Exp") %>% group_by(`Demo-ResponseID`) %>% summarise(num_tasks = n_distinct(Task)) %>% filter(num_tasks >= 5) %>% select(`Demo-ResponseID`)

#answers_per_dataset <- exp_responses_split %>% group_by(`Demo-ResponseID`,Dataset) %>% summarise(num_tasks = n_distinct(Task)) %>% mutate(include = num_tasks>4) 

raw_responses <- raw_responses %>% filter(`Demo-ResponseID` %in% keep_IDs$`Demo-ResponseID`)

exp_responses_split <- exp_responses_split %>% filter(`Demo-ResponseID` %in% keep_IDs$`Demo-ResponseID`)

```

## Process the demographic/stats columns

```{r}

# Join demo data to exp response data?  What files need this data?  All graded files?

demo <- dplyr::select(raw_responses, "Demo-ResponseID", starts_with("Demo"))

stats <- dplyr::select(raw_responses, "filename", "Demo-ResponseID", starts_with("Stats"), -contains("training"), -contains("dataset-"))

stats$`Stats-CompensationCondition` <- sub(" ","",stats$`Stats-CompensationCondition`)

# When joining demo/stats to graded answers, can join stats_demo as is, but want to make sure stats_datasets_tall joins by both ID and Dataset

stats_demo <- full_join(stats,demo)

stats_demo <- left_join(stats_demo, population_experience)

write_csv(stats_demo, file.path(analysisDataDir,"Stats_Demo.csv"))


```


## Process the order columns

```{r}

# Extract dataset order questions to new table, including RespondentID!

dataset_order <- dplyr::select(raw_responses, "Demo-ResponseID", starts_with("OrderDatasets"), -`OrderDatasetsWithinBlock-Training`)

# Transpose 5 order questions from wide to tall into two columns - column labels and values

dataset_order <- dataset_order %>% gather("Condition","Order",-1)

# Remove NAs?

dataset_order <- dataset_order %>% filter(!is.na(Order))


# Split column labels to get block in its own column

dataset_order$Condition <- sub("OrderDatasetsWithinBlock-","",dataset_order$Condition)

# Split Values to get the ordered datasets in separate columns

dataset_order <- dataset_order %>% separate(Order, c("1","2","3"), sep="[|]")

#dataset_order <- dataset_order %>% separate(Order, c("1"), sep="[|]")

# Transpose dataset columns into one column for dataset number and another for dataset order

dataset_order <- dataset_order %>% gather("DatasetOrder","BlockID",-c(1:2), convert=TRUE)

dataset_order <- dataset_order %>% filter(!is.na(BlockID))

# Rename datasets using prepared dictionary

dataset_order <- left_join(dataset_order, block_ids, by=c("BlockID", "Condition"))

dataset_order <- dataset_order %>% select(-BlockID)

```


```{r}

stats_datasets <- dplyr::select(raw_responses, "filename", "Demo-ResponseID", starts_with("Stats-training"), starts_with("Stats-dataset-"))

stats_datasets_tall <- stats_datasets %>% gather("ColName","Value",-c(1,2)) %>% separate(ColName, c("Group","Subgroup","Dataset","Measurement"), sep="[-]", convert=TRUE) %>% select(-Group, -Subgroup) %>% filter(!(Measurement %in% c("order","yn"))) %>% spread(Measurement, Value)

names(stats_datasets_tall)[names(stats_datasets_tall) == "start"] <- "DatasetStartTime"

names(stats_datasets_tall)[names(stats_datasets_tall) == "duration"] <- "DatasetDuration"

stats_datasets_tall <- stats_datasets_tall %>% filter(!is.na(DatasetStartTime), !is.na(DatasetDuration))

#write_csv(stats_datasets_tall, file.path(analysisDataDir,"Stats_Datasets_Tall.csv"))
```

```{r}

# Join dataset order to stats_dataset_tall

conditions <- stats_demo %>% select(`Demo-ResponseID`,`Stats-Group`)

stats_datasets_tall <- left_join(stats_datasets_tall, conditions)

stats_datasets_tall <- left_join(stats_datasets_tall, dataset_order, by=c("Demo-ResponseID","Dataset")) %>% select(-Condition)

stats_datasets_tall$DatasetOrder[stats_datasets_tall$Dataset==0] <- 0

stats_datasets_tall <- full_join(stats_datasets_tall, population_experience)

write_csv(stats_datasets_tall, file.path(analysisDataDir,"Stats_Datasets_Tall.csv"))

```

```{r}
# Join dataset order to exp response data

exp_responses_with_order <- left_join(exp_responses_split, dataset_order, by=c("Demo-ResponseID","Condition","Dataset"))

exp_responses_with_order$DatasetOrder <- ifelse(exp_responses_with_order$QType == "Training", 0, exp_responses_with_order$DatasetOrder)

```

```{r}

# Extract question order questions to new table, including RespondentID!

question_order <- dplyr::select(raw_responses, "Demo-ResponseID", starts_with("OrderQuestions"))

# Transpose 12 order questions from wide to tall into two columns - column labels and values

question_order <- question_order %>% gather("Column","Order",-1)

# Remove NAs?

question_order <- question_order %>% filter(!is.na(Order))

# Split column labels to get block and dataset in their own columns

question_order$Column <- sub("OrderQuestionsWithinDataset-","",question_order$Column)

question_order <- question_order %>% separate(Column,c("Condition","Dataset"),sep="[-]", convert=TRUE)

# Split values to get the ordered questions in separate columns

question_order <- question_order %>% separate(Order, c("1","2","3","4","5","6","7","8","9"), sep="[|]")

# Transpose question columns into one column for question name and another for question order

question_order <- question_order %>% gather("TaskOrder","Task",-c(1:3), convert=TRUE)

question_order$Task <- sub("—","-",question_order$Task)

question_order <- question_order %>% 
  separate(Task,c("ConditionCopy","DatasetCopy","Task"),sep="[-]") %>%
  select(-ConditionCopy,-DatasetCopy)

# Change LargeClust to LargeClust1

question_order$Task <- sub("LargeClust","LargeClust1",question_order$Task)

# Join question order to exp response data

exp_responses_with_order <- left_join(exp_responses_with_order, question_order, by=c("Demo-ResponseID","Condition","Dataset","Task"))

```


```{r}

new_training_rows <- exp_responses_with_order %>% filter(QType == "Training") %>% select(-TaskOrder) %>% left_join(training_task_order)

exp_responses_with_order <- exp_responses_with_order %>% filter(QType != "Training") %>% bind_rows(new_training_rows)

```

```{r}

# for people in Col, Phr, and Size condition, change the Condition in the Training tasks to match their group; it's confusing when trying to compare their experimental tasks to their training tasks

exp_responses_with_order <- select(raw_responses, `Demo-ResponseID`, `Stats-Group`) %>% right_join(exp_responses_with_order) %>% mutate(Condition = ifelse(`Stats-Group` == "color","Col",ifelse(`Stats-Group` == "phrasing", "Phr", ifelse(`Stats-Group` == "size", "Siz",Condition)))) %>% select(-`Stats-Group`)

```

```{r}
# Save file out?

write_csv(exp_responses_with_order, file.path(analysisDataDir,"CombinedResponsesWithOrder.csv"))

```

## Join response data to answer data

```{r}

# Note: these answers should be the same regardless of condition, as should clusters.  Anything related to clicking (degree and betweenness) will depend on condition.

joined_num_ans <- inner_join(exp_responses_with_order, num_ans_lookup, by=c("Dataset","Task"))

joined_num_ans$Response <- type.convert(joined_num_ans$Response)

joined_num_ans <- joined_num_ans %>% select(-Coord)

# Need to match up x and y from click data

exp_responses_degree <- filter(exp_responses_with_order, Task == "ClickHighDeg")

exp_responses_degree$Task <- "Click"
  
exp_responses_degree <- exp_responses_degree %>% unite("Task", c("Task","Coord"))

exp_responses_degree$Response <- type.convert(exp_responses_degree$Response)

exp_responses_degree <- separate(exp_responses_degree, Task, c("Task","Attempt"), sep=7, convert=TRUE)

exp_responses_degree_wide <- spread(exp_responses_degree, Task, Response)

joined_degree <- left_join(exp_responses_degree_wide, node_lookup[node_lookup$Task == "ClickHighDeg",], by=c("Condition", "Dataset"))

#joined_degree$Attempt <- 1

#exp_responses_bc <- filter(exp_responses_split, Task %in% c("BC_X1","BC_Y1","BC_X2","BC_Y2","BC_X3","BC_Y3","BC_X4","BC_Y4","BC_X5","BC_Y5"))

exp_responses_bc <- filter(exp_responses_with_order, Task == "BC")

exp_responses_bc$Task <- "Click"

exp_responses_bc <- exp_responses_bc %>% unite("Task", c("Task","Coord"))

exp_responses_bc$Response <- type.convert(exp_responses_bc$Response)

exp_responses_bc <- separate(exp_responses_bc, Task, c("Task","Attempt"), sep=7, convert=TRUE)

exp_responses_bc_wide <- spread(exp_responses_bc, Task, Response)

#joined_bc <- inner_join(exp_responses_bc_wide, bc_lookup, by=c("Condition","Dataset"))

joined_bc <- left_join(exp_responses_bc_wide, node_lookup[node_lookup$Task == "BC",], by=c("Condition","Dataset"))

joined_nodes <- bind_rows(joined_degree, joined_bc)


```


## Grade the questions

```{r}

# TO DO: change percentage to correct calculation

#graded_clusters <- dplyr::mutate(joined_clusters,
#                                 AvgCorrectValue = (MinCorrectValue + MaxCorrectValue)/2,
#                                 Difference = abs(AvgCorrectValue - Response),
#                                 Percentage = Difference/AvgCorrectValue)

#graded_degree <- dplyr::mutate(joined_degree, Distance = sqrt((ClickHighDeg_X1-NodeXAdjusted)^2 + (ClickHighDeg_Y1-NodeYAdjusted)^2))

#graded_bc <- dplyr::mutate(joined_bc, Distance = sqrt((BC_X-NodeXAdjusted)^2 + (BC_Y-NodeYAdjusted)^2))

# find distance between click responses and all node positions

graded_nodes <- mutate(joined_nodes, Distance = sqrt((Click_X-NodeXAdjusted)^2 + (Click_Y-NodeYAdjusted)^2))

#graded_degree_top <- group_by(graded_degree, `Demo-ResponseID`, Condition, Dataset) %>% top_n(-1, Distance)

#graded_bc_top <- group_by(graded_bc, `Demo-ResponseID`, Condition, Dataset, Attempt) %>% top_n(-1, Distance)

# pick the closest node (node where distance is smallest)

# TO DO: keep some measure of whether other nodes were close? distribution?
# TO DO: pick best of nearest 5 nodes, rather than keeping the top 1?  Would need to calculate
# accuracy before making final selection
# TO DO: calculate LogError on click data, too?  decide on best node, calculate its BC value
# (or rank?) and compute log error between that and the value for the best answer?

graded_nodes_top <- group_by(graded_nodes, `Demo-ResponseID`, Condition, Dataset, Task, Attempt) %>% top_n(-1, Distance)

#graded_nodes_top <- left_join(graded_nodes_top, stats_demo)

#graded_nodes_top <- left_join(graded_nodes_top, stats_datasets_tall)


# Calculate LogError, a la Heer & Bostock 2010
# Note: Heer & Bostock add 1/8 to the calculation, but that means that perfectly correct answers
# become -3.  Seems strange.  Changing to add 1, so perfectly correct answers have LogError of 0.


graded_num_ans <- dplyr::mutate(joined_num_ans, 
                                RawDifference = Response - CorrectAnswer, 
                                AbsDifference = abs(Response - CorrectAnswer), 
                                Percentage = abs(CorrectAnswer - Response)/CorrectAnswer,
                                LogError = log2(abs(Response - CorrectAnswer) + 1))

clust_conf <- filter(exp_responses_split, Task == "ClustConf") %>% select(-Coord)

graded_num_ans <- left_join(graded_num_ans, clust_conf, by = c("Demo-ResponseID", "QType", "Condition", "Dataset")) %>% select(-Task.y)

names(graded_num_ans)[names(graded_num_ans) == 'Response.y'] <- 'ClustConf'

names(graded_num_ans)[names(graded_num_ans) == 'Task.x'] <- 'Task'

names(graded_num_ans)[names(graded_num_ans) == 'Response.x'] <- 'Response'

graded_num_ans[graded_num_ans$Task != "NumClust","ClustConf"] <- NA

#graded_num_ans <- left_join(graded_num_ans, stats_demo)

#graded_num_ans <- left_join(graded_num_ans, stats_datasets_tall)


```

## Write analysis files

```{r}

write_csv(graded_num_ans, file.path(analysisDataDir,"GradedNumAnswers.csv"))

#write_csv(graded_degree_top, file.path(analysisDataDir,"GradedDegree.csv")s)

#write_csv(graded_bc_top, file.path(analysisDataDir,"GradedBC.csv"))

write_csv(graded_nodes_top, file.path(analysisDataDir,"GradedNodes.csv"))

```


